### 2022-11-26 submission.tex
first commit

\documentclass[12pt]{article}
\usepackage[paper=letterpaper,margin=2cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{newtxtext, newtxmath}
\usepackage{enumitem}
\usepackage{titling}
\usepackage[colorlinks=true]{hyperref}
\usepackage{graphicx}
\usepackage{csvsimple}
\usepackage{luacode}
\setlength{\droptitle}{-6em}

% Enter the specific assignment number and topic of that assignment below, and replace "Your Name" with your actual name.

\title{\textbf{COMP0078 Assignment 2}}
\author{Student Numbers: 21168615 \& 19004608 \\ }
\date{Dec 14, 2022}

\begin{document}
    \maketitle
\section{PART I}
\subsection{Kerenl Perceptron}
\newpage
\section{PART II}
\subsection{Semi-supervised Leanrning via Laplacian Interpolation}
\newpage
\section{PART III}
\subsection{Questions}
\begin{itemize}
    \item[1.]
    \item[2.]
    \item[3.]
\end{itemize}
\end{document}

### 2022-11-26 main.py

@@ -1,0 +1,24 @@
+import os
+
+import jax
+import numpy as np
+import pandas as pd
+
+from src.constants import DATA_FOLDER, DEFAULT_SEED, OUTPUTS_FOLDER
+
+if __name__ == "__main__":
+    jax.config.update("jax_platform_name", "cpu")
+    jax.config.update("jax_enable_x64", True)
+
+    if not os.path.exists(OUTPUTS_FOLDER):
+        os.makedirs(OUTPUTS_FOLDER)
+
+    # Question 1
+    PART_1_OUTPUT_FOLDER = os.path.join(OUTPUTS_FOLDER, "part1")
+    if not os.path.exists(PART_1_OUTPUT_FOLDER):
+        os.makedirs(PART_1_OUTPUT_FOLDER)
+
+    # Question 2
+    PART_2_OUTPUT_FOLDER = os.path.join(OUTPUTS_FOLDER, "part2")
+    if not os.path.exists(PART_2_OUTPUT_FOLDER):
+        os.makedirs(PART_2_OUTPUT_FOLDER)

### 2022-11-26 src/constants.py

@@ -1,0 +1,4 @@
+OUTPUTS_FOLDER = "outputs"
+DATA_FOLDER = "data"
+
+DEFAULT_SEED = 42

### 2022-11-30 src/models/SSL.py
question 2 completed

@@ -1,32 +1,36 @@
 import numpy as np
-from sklearn.neighbors import KDTree
-
-def _make_graph_matrix(X):
-    tree = KDTree(X)
-    n = X.shape[0]
-    graph = tree.query(X, k = 4)[1][:,1:]
-    W = np.zeros((n,n))
-    for i in range(n):
-        W[i,graph[i,:]] = 1
-        W[graph[i,:],i] = 1
-    return W
 
 
-def laplacian_interpolation(X: np.ndarray, y: int) -> np.ndarray:
-    """ 
-    Inputs:
-     
-    D: graph degree matrix
-    w: graph adjacency matrix (both nxn)
+class LaplacianInterpolation():
+    def __init__(self):
+        self.W = None
 
-    Note: we have ordered our graph nodes so the first l datapoints are the 
-    labelled datapoints.
+    def predict(self, W, y):
+        """ 
+        Inputs:
+        
+        X : design matrix of input variables
+        y : set of labels for x_1, ..., x_l
 
-    The following expression was given in the paper provided, and hence used in
-    this example for a closed-form solution.
+        Note: we have ordered our graph nodes so the first l datapoints are the 
+        labelled datapoints.
 
-    """
-    W = _make_graph_matrix(X)
-    s = y.shape[0]
-    D = np.diag(W.sum(0))
-    return np.sign(np.linalg.solve(D[s:,s:] - W[s:,s:], W[s:,:s] @ y))
+        The following expression was given in the paper provided, and hence used in
+        this example for a closed-form solution.
+
+        """
+        s = y.shape[0]
+        D = np.diag(W.sum(0))
+        return np.sign(np.linalg.lstsq(D[s:,s:] - W[s:,s:], W[s:,:s] @ y, rcond = None)[0])
+
+
+class LaplacianKernelInterpolation():
+    def __init__(self):
+        pass
+
+    def predict(self, W, y):        
+        L = np.diag(W.sum(0)) - W
+        m = y.shape[0]
+        L_pinv = np.linalg.pinv(L)
+        alpha = np.linalg.pinv(L_pinv[:m,:m]) @ y
+        return np.sign(L_pinv[:m,:].T @ alpha)[m:]

### 2022-11-30 src/models/helpers.py

@@ -57,10 +57,19 @@ def one_hot_encode(shifted_labels: np.ndarray) -> np.ndarray:
     return 2 * one_hot_encoding - 1
 
 
+def ssl_data_sample(y, sample_size):
+    idxs = np.random.choice(list(np.where(y == -1.)[0]), size = sample_size, replace = False).tolist()
+    idxs += np.random.choice(list(np.where(y == 1.)[0]), size = sample_size, replace = False).tolist()
+    idxs += [i for i in range(y.shape[0]) if i not in idxs]
+    return idxs
 
-def ssl_data_sample(data, sample_size):
-    idxs = np.random.choice(list(np.where(data[:,0] == -1.)[0]), size = sample_size, replace = False).tolist()
-    idxs += np.random.choice(list(np.where(data[:,0] == 1.)[0]), size = sample_size, replace = False).tolist()
-    temp = np.concatenate((data[idxs], np.delete(data, idxs, axis = 0)))
-    X,y_train, y_test = temp[:,1:], temp[:2*sample_size,0], temp[2*sample_size:,0]
-    return X, y_train, y_test
+
+def KNN_adjacency_matrix(X,k):
+    tree = KDTree(X)
+    n = X.shape[0]
+    graph = tree.query(X, k)[1][:,1:]
+    W = np.zeros((n,n))
+    for i in range(n):
+        W[i,graph[i,:]] = 1
+        W[graph[i,:],i] = 1
+    return W

### 2022-11-30 src/solutions/q2.py

@@ -1,32 +1,39 @@
-from src.models.helpers import ssl_data_sample
-from src.models.SSL import laplacian_interpolation
+from src.models.helpers import ssl_data_sample, KNN_adjacency_matrix
+from src.models.SSL import LaplacianInterpolation, LaplacianKernelInterpolation
 import os
 import numpy as np
 import pandas as pd
 
+outpath =  os.path.join('outputs', 'part2')
 DATAPATH50 = os.path.join('data','dtrain13_50.dat')
 DATAPATH100 = os.path.join('data','dtrain13_100.dat')
 DATAPATH200 = os.path.join('data','dtrain13_200.dat')
 DATAPATH400 = os.path.join('data','dtrain13_400.dat')
-REPORT_LAPLACIAN_OUTPATH = os.path.join('outputs', 'laplacian_interpolation_report')
+REPORT_LAPLACIAN_OUTPATH = os.path.join(outpath, 'laplacian_interpolation_report')
+REPORT_LAPLACIAN_KERNEL_OUTPATH = os.path.join(outpath, 'laplacian_kernel_interpolation_report')
 
-def laplacian_experimental_report(
+def experimental_report(
+    model,
     datasets,
     n_iters,
     ):
     sample_range = [1,2,4,8,16]
-    errors = np.zeros((4,5,n_iters))
+    accuracy = np.zeros((4,5,n_iters))
+    
     for iter in range(n_iters):
-        for i in range(4):
-            for j in range(5):
-                X,y_train,y_test = ssl_data_sample(datasets[i],sample_range[j])
-                errors[i,j, iter] = (laplacian_interpolation(X,y_train) == y_test).mean()
-    return errors.mean(-1), errors.std(-1)
+        for i, dataset in enumerate(datasets):
+            y = dataset[:,0]
+            W = KNN_adjacency_matrix(dataset[:,1:], k = 3)
+            for j, sample_size in enumerate(sample_range):
+                sample = ssl_data_sample(y,sample_size)
+                y_train, y_test = y[sample[:2*sample_size]], y[sample[2*sample_size:]] 
+                accuracy[i,j,iter] = (model.predict(W[sample,:][:,sample], y_train) == y_test).mean()
+    return accuracy.mean(-1), accuracy.std(-1)
 
 
 def write_report_to_csv(means, stds, outpath):
     df = pd.DataFrame(means).round(2).astype('str')
[…]

### 2022-11-30 submission.tex
pretty pictures added

@@
 \section{PART I}
-\subsection{Kerenl Perceptron}
+\subsection{Kernel Perceptron}
 \newpage
@@
 \subsection{Semi-supervised Leanrning via Laplacian Interpolation}
+Experimental report for the laplacian interpolation approach:
+\\
+
+\includegraphics{outputs/part2/laplacian_interpolation_report.png}
+
+\\
+
+And for the laplacian kernel method:
+
+\includegraphics{outputs/part2/laplacian_kernel_interpolation_report.png}
+
 \newpage
+
 \section{PART III}

### 2022-11-30 src/solutions/q2.py

@@ -3,14 +3,16 @@ from src.models.SSL import LaplacianInterpolation, LaplacianKernelInterpolation
 import os
 import numpy as np
 import pandas as pd
+import dataframe_image as dfi
+
 
 outpath =  os.path.join('outputs', 'part2')
 DATAPATH50 = os.path.join('data','dtrain13_50.dat')
 DATAPATH100 = os.path.join('data','dtrain13_100.dat')
 DATAPATH200 = os.path.join('data','dtrain13_200.dat')
 DATAPATH400 = os.path.join('data','dtrain13_400.dat')
-REPORT_LAPLACIAN_OUTPATH = os.path.join(outpath, 'laplacian_interpolation_report')
-REPORT_LAPLACIAN_KERNEL_OUTPATH = os.path.join(outpath, 'laplacian_kernel_interpolation_report')
+REPORT_LAPLACIAN_OUTPATH = os.path.join(outpath, 'laplacian_interpolation_report.png')
+REPORT_LAPLACIAN_KERNEL_OUTPATH = os.path.join(outpath, 'laplacian_kernel_interpolation_report.png')
 
 def experimental_report(
     model,
@@ -34,11 +36,17 @@ def experimental_report(
 def write_report_to_csv(means, stds, outpath):
     df = pd.DataFrame(means).round(2).astype('str')
     df2 = pd.DataFrame(stds).round(4).astype('str')
-
     report = df + '±' + df2
     report.columns = [1,2,4,8,16]
     report.index = [50,100,200,400]
-    report.to_csv(outpath)
+    report = pd.concat(
+                        [pd.concat(
+                            [report],
+                            keys=['# of known labels (per class)'], axis=1)],
+                        keys=['accuracy']
+                    )
+    dfi.export(report,outpath)
+
 
 def q2():
     datasets = []

### 2022-11-30 main.py
part 1 updates

@@ -1,11 +1,16 @@
 import os
 
-import jax
+import jax.numpy as jnp
 import numpy as np
 import pandas as pd
 
-from src.constants import DATA_FOLDER, DEFAULT_SEED, OUTPUTS_FOLDER
+from src.constants import DATA_FOLDER, DEFAULT_SEED, OUTPUTS_FOLDER, PART_1_MINI_TRAIN_SET_PATH
 from src.solutions.q2 import q2
+from src.solutions import part_1
+from src.models.helpers import one_hot_encode, split_train_test_data, TrainTestData
+from src.models.kernels import PolynomialKernel, GaussianKernel
+import jax
+
 if __name__ == "__main__":
     jax.config.update("jax_platform_name", "cpu")
     jax.config.update("jax_enable_x64", True)
@@ -18,9 +23,68 @@ if __name__ == "__main__":
     if not os.path.exists(PART_1_OUTPUT_FOLDER):
         os.makedirs(PART_1_OUTPUT_FOLDER)
 
-    # Question 2
-    PART_2_OUTPUT_FOLDER = os.path.join(OUTPUTS_FOLDER, "part2")
-    if not os.path.exists(PART_2_OUTPUT_FOLDER):
-        os.makedirs(PART_2_OUTPUT_FOLDER)
+    data = np.genfromtxt(PART_1_MINI_TRAIN_SET_PATH)
+    x, labels = data[:, 1:], data[:, 0]
+    # shift so that our labels start at zero
+    shifted_labels = labels - jnp.min(labels)
+    y = one_hot_encode(shifted_labels)
 
-    q2()
+    number_of_runs = 20
+    percent_split = 0.8
+    run_splits = [split_train_test_data(x, y, percent_split) for _ in range(number_of_runs)]
+
+    train_test_data = TrainTestData(
+        x_train=np.array([run_split.x_train for run_split in run_splits]),
+        y_train=np.array([run_split.y_train for run_split in run_splits]),
+        x_test=np.array([run_split.x_test for run_split in run_splits]),
+        y_test=np.array([run_split.y_test for run_split in run_splits]),
+    )
+
+    part_1.q1(
+        data=train_test_data,
+        kernel_class=PolynomialKernel(),
+        kernel_parameters=np.arange(1, 2),
+        kernel_parameter_name="degree",
+        number_of_runs=20,
[…]

### 2022-11-30 src/models/helpers.py

@@ -26,7 +26,9 @@ def split_train_test_data(
     x: np.ndarray, y: np.ndarray, train_percentage: float
 ) -> TrainTestData:
     n, _ = x.shape
-    test_indices = np.random.choice(np.arange(n), int((1-train_percentage) * n), replace=False)
+    test_indices = np.random.choice(
+        np.arange(n), int(np.round((1 - train_percentage) * n)), replace=False
+    )
     return _build_train_test_data(x, y, indices=test_indices)
 
 
@@ -57,6 +59,7 @@ def one_hot_encode(shifted_labels: np.ndarray) -> np.ndarray:
     return 2 * one_hot_encoding - 1
 
 
+<<<<<<< Updated upstream
 def ssl_data_sample(y, sample_size):
     idxs = np.random.choice(list(np.where(y == -1.)[0]), size = sample_size, replace = False).tolist()
     idxs += np.random.choice(list(np.where(y == 1.)[0]), size = sample_size, replace = False).tolist()
@@ -73,3 +76,19 @@ def KNN_adjacency_matrix(X,k):
         W[i,graph[i,:]] = 1
         W[graph[i,:],i] = 1
     return W
+=======
+def ssl_data_sample(data, sample_size):
+    idxs = np.random.choice(
+        list(np.where(data[:, 0] == -1.0)[0]), size=sample_size, replace=False
+    ).tolist()
+    idxs += np.random.choice(
+        list(np.where(data[:, 0] == 1.0)[0]), size=sample_size, replace=False
+    ).tolist()
+    temp = np.concatenate((data[idxs], np.delete(data, idxs, axis=0)))
+    X, y_train, y_test = (
+        temp[:, 1:],
+        temp[: 2 * sample_size, 0],
+        temp[2 * sample_size :, 0],
+    )
+    return X, y_train, y_test
+>>>>>>> Stashed changes

### 2022-11-30 src/models/kernels.py

@@ -41,7 +41,9 @@ class BaseKernel(ABC):
         x = jnp.atleast_2d(x)
         y = jnp.atleast_2d(y)
 
-        assert x.shape[1] == y.shape[1], f"Dimension Mismatch: {x.shape[1]=} != {y.shape[1]=}"
+        assert (
+            x.shape[1] == y.shape[1]
+        ), f"Dimension Mismatch: {x.shape[1]=} != {y.shape[1]=}"
 
         return vmap(
             lambda x_i: vmap(
@@ -62,9 +64,7 @@ class BaseKernel(ABC):
 
     @classmethod
     @abstractmethod
-    def tree_unflatten(
-        cls, aux_data: Dict[str, Any], children: Tuple
-    ) -> BaseKernel:
+    def tree_unflatten(cls, aux_data: Dict[str, Any], children: Tuple) -> BaseKernel:
         """
         To have JIT-compiled class methods by registering the type as a custom PyTree object.
         As referenced in:

### 2022-11-30 src/models/perceptron.py

@@ -7,7 +7,9 @@ from typing import Dict, Any, Tuple
 
 class Perceptron:
     @staticmethod
-    def train(w: np.ndarray, gram: np.ndarray, y: np.ndarray, number_of_epochs: int) -> np.ndarray:
+    def train(
+        w: np.ndarray, gram: np.ndarray, y: np.ndarray, number_of_epochs: int
+    ) -> np.ndarray:
         """
 
         :param w:
@@ -25,7 +27,9 @@ class Perceptron:
                 correct_prediction_indicator = jnp.multiply(y[i], prediction)
 
                 # zero if prediction was incorrect
-                clipped_correct_prediction_indicator = correct_prediction_indicator.clip(0, 1)
+                clipped_correct_prediction_indicator = (
+                    correct_prediction_indicator.clip(0, 1)
+                )
 
                 # mask weights to update
                 update_mask = ~clipped_correct_prediction_indicator.astype(bool)

### 2022-11-30 src/solutions/part_1.py

@@ -1,0 +1,309 @@
+from dataclasses import dataclass
+import pandas as pd
+import numpy as np
+import jax.numpy as jnp
+from jax import vmap
+
+from src.models.helpers import TrainTestData, make_folds
+from src.models.perceptron import Perceptron
+from src.models.kernels import BaseKernel
+
+def _convert_to_scientific_notation(x: float) -> str:
+    """
+    Convert value to string in scientific notation
+    :param x: value to convert
+    :return: string of x in scientific notation
+    """
+    return "{:.2e}".format(float(x))
+
+
+@dataclass
+class Performance:
+    mean: np.ndarray
+    stdev: np.ndarray
+
+    def build_df(self, kernel_parameters, kernel_parameter_name, index):
+        df = pd.DataFrame(
+            data=[
+                [
+                    f"{'%.2f' % (100 * self.mean[i])}%±{'%.2f' % (100 * self.stdev[i])}%"
+                    for i in range(len(kernel_parameters))
+                ]
+            ],
+            columns=[
+                f"{kernel_parameter_name}={kernel_parameters[i]}"
+                for i in range(len(kernel_parameters))
+            ],
+        )
+        df.index = [index]
+        return df
+
+
+def _build_folds_data(x, y, number_of_folds):
+    x_train = []
+    y_train = []
+    x_test = []
+    y_test = []
+    number_of_runs = x.shape[0]
+    for i in range(number_of_runs):
+        folds = make_folds(
+            x=x[i],
+            y=y[i],
+            number_of_folds=number_of_folds,
+        )
+        min_fold_size_train = np.min([fold.x_train.shape[0] for fold in folds])
+        x_train.append(np.vstack([fold.x_train[None, :min_fold_size_train, ...] for fold in folds]))
+        y_train.append(np.vstack([fold.y_train[None, :min_fold_size_train, ...] for fold in folds]))
+
+        min_fold_size_test = np.min([fold.x_test.shape[0] for fold in folds])
+        x_test.append(np.vstack([fold.x_test[None, :min_fold_size_test, ...] for fold in folds]))
+        y_test.append(np.vstack([fold.y_test[None, :min_fold_size_test, ...] for fold in folds]))
+    return TrainTestData(
+        x_train=np.swapaxes(np.array(x_train), 0, 1),
+        y_train=np.swapaxes(np.array(y_train), 0, 1),
+        x_test=np.swapaxes(np.array(x_test), 0, 1),
[…]

### 2022-11-30 src/solutions/q2.py

@@ -50,9 +50,9 @@ def write_report_to_csv(means, stds, outpath):
 
 def q2():
     datasets = []
-    for path in [DATAPATH50,DATAPATH100,DATAPATH200,DATAPATH400]:
+    for path in [DATAPATH50, DATAPATH100, DATAPATH200, DATAPATH400]:
         data = np.genfromtxt(path)
-        data[:,0] -= 2
+        data[:, 0] -= 2
         datasets.append(data)
     means, stds = experimental_report(LaplacianInterpolation(), datasets, n_iters = 20)
     write_report_to_csv(means, stds, outpath = REPORT_LAPLACIAN_OUTPATH)
@@ -60,8 +60,6 @@ def q2():
     means, stds = experimental_report(LaplacianKernelInterpolation(), datasets, n_iters = 20)
     write_report_to_csv(means, stds, outpath = REPORT_LAPLACIAN_KERNEL_OUTPATH)
 
+
 if __name__ == '__main__':
     q2()
-
-
-

### 2022-11-30 main.py
add confusion matrix

@@ -4,7 +4,7 @@ import jax.numpy as jnp
 import numpy as np
 import pandas as pd
 
-from src.constants import DATA_FOLDER, DEFAULT_SEED, OUTPUTS_FOLDER, PART_1_MINI_TRAIN_SET_PATH
+from src.constants import DATA_FOLDER, DEFAULT_SEED, OUTPUTS_FOLDER, PART_1_MINI_TRAIN_SET_PATH, PART_1_DATA_SET_PATH
 from src.solutions.q2 import q2
 from src.solutions import part_1
 from src.models.helpers import one_hot_encode, split_train_test_data, TrainTestData
@@ -40,26 +40,28 @@ if __name__ == "__main__":
         y_test=np.array([run_split.y_test for run_split in run_splits]),
     )
 
-    part_1.q1(
-        data=train_test_data,
-        kernel_class=PolynomialKernel(),
-        kernel_parameters=np.arange(1, 2),
-        kernel_parameter_name="degree",
-        number_of_runs=20,
-        number_of_epochs=5,
-        df_performance_path=os.path.join(PART_1_OUTPUT_FOLDER, "q1.csv")
-    )
-
-    # part_1.q2(
+    # part_1.q1(
     #     data=train_test_data,
     #     kernel_class=PolynomialKernel(),
-    #     kernel_parameters=np.arange(1, 8),
+    #     kernel_parameters=np.arange(1, 2),
     #     kernel_parameter_name="degree",
     #     number_of_runs=20,
     #     number_of_epochs=5,
-    #     number_of_folds=5,
-    #     df_performance_path=os.path.join(PART_1_OUTPUT_FOLDER, "q2.csv")
+    #     df_performance_path=os.path.join(PART_1_OUTPUT_FOLDER, "q1.csv")
     # )
+
+    part_1.q2(
+        data=train_test_data,
+        kernel_class=PolynomialKernel(),
+        kernel_parameters=np.arange(1, 8),
+        kernel_parameter_name="degree",
+        number_of_runs=20,
+        number_of_epochs=5,
+        number_of_folds=5,
+        labels=np.sort(list(set(labels))),
+        df_performance_path=os.path.join(PART_1_OUTPUT_FOLDER, "q2.csv"),
+        df_confusion_matrix_path=os.path.join(PART_1_OUTPUT_FOLDER, "q2_confusion.csv"),
+    )
     #
     # part_1.q1(
[…]

### 2022-11-30 src/models/helpers.py

@@ -59,7 +59,6 @@ def one_hot_encode(shifted_labels: np.ndarray) -> np.ndarray:
     return 2 * one_hot_encoding - 1
 
 
-<<<<<<< Updated upstream
 def ssl_data_sample(y, sample_size):
     idxs = np.random.choice(list(np.where(y == -1.)[0]), size = sample_size, replace = False).tolist()
     idxs += np.random.choice(list(np.where(y == 1.)[0]), size = sample_size, replace = False).tolist()
@@ -76,19 +75,3 @@ def KNN_adjacency_matrix(X,k):
         W[i,graph[i,:]] = 1
         W[graph[i,:],i] = 1
     return W
-=======
-def ssl_data_sample(data, sample_size):
-    idxs = np.random.choice(
-        list(np.where(data[:, 0] == -1.0)[0]), size=sample_size, replace=False
-    ).tolist()
-    idxs += np.random.choice(
-        list(np.where(data[:, 0] == 1.0)[0]), size=sample_size, replace=False
-    ).tolist()
-    temp = np.concatenate((data[idxs], np.delete(data, idxs, axis=0)))
-    X, y_train, y_test = (
-        temp[:, 1:],
-        temp[: 2 * sample_size, 0],
-        temp[2 * sample_size :, 0],
-    )
-    return X, y_train, y_test
->>>>>>> Stashed changes

### 2022-11-30 src/solutions/part_1.py

@@ -226,6 +226,7 @@ def q2(
     number_of_folds,
     labels,
     df_performance_path,
+    df_confusion_matrix_path,
 ):
     number_of_parameters = len(kernel_parameters)
     number_classes = data.y_train.shape[2]
@@ -294,16 +295,28 @@ def q2(
         index="Test Error Rate",
     ).to_csv(df_performance_path)
 
-    # confusion_matrix = np.zeros((number_of_runs, number_classes, number_classes))
-    # for i in range(number_of_runs):
-    #     np.add.at(
-    #         confusion_matrix[i, ...],
-    #         (np.argmax(data.y_test[i, ...], axis=-1), np.argmax(test_predictions[i, ...], axis=-1)),
-    #         1
-    #     )
-    #     np.fill_diagonal(confusion_matrix[i, ...], 0)
-    # df = pd.DataFrame(
-    #     confusion_matrix,
-    #     columns=labels,
-    # )
-    # df.index = labels
+    confusion_matrix = np.zeros((number_of_runs, number_classes, number_classes))
+    for i in range(number_of_runs):
+        np.add.at(
+            confusion_matrix[i, ...],
+            (np.argmax(data.y_test[i, ...], axis=-1), np.argmax(test_predictions[i, ...], axis=-1)),
+            1
+        )
+    confusion_matrix = confusion_matrix / confusion_matrix.sum(axis=2)[..., None]
+    confusion_mean = np.round(100*confusion_matrix.mean(axis=0), 2)
+    np.fill_diagonal(confusion_mean, 0)
+    confusion_stdev = np.round(100*confusion_matrix.std(axis=0))
+    np.fill_diagonal(confusion_stdev, 0)
+
+    df = pd.DataFrame(
+        [
+            [
+                f"{confusion_mean[i, j]}%±{confusion_stdev[i, j]}%"
+                for j in range(number_classes)
+            ]
+            for i in range(number_classes)
+        ],
+        columns=labels,
+    )
+    df.index = labels
+    df.to_csv(df_confusion_matrix_path)

### 2022-12-04 main.py
perceptron code update and add winnow implementation

@@ -4,10 +4,16 @@ import jax.numpy as jnp
 import numpy as np
 import pandas as pd
 
-from src.constants import DATA_FOLDER, DEFAULT_SEED, OUTPUTS_FOLDER, PART_1_MINI_TRAIN_SET_PATH, PART_1_DATA_SET_PATH
+from src.constants import (
+    DATA_FOLDER,
+    DEFAULT_SEED,
+    OUTPUTS_FOLDER,
+    PART_1_MINI_TRAIN_SET_PATH,
+    PART_1_DATA_SET_PATH,
+)
 from src.solutions.q2 import q2
 from src.solutions import part_1
-from src.models.helpers import one_hot_encode, split_train_test_data, TrainTestData
+from src.models.helpers import one_hot_encode, split_train_test_data
 from src.models.kernels import PolynomialKernel, GaussianKernel
 import jax
 
@@ -23,7 +29,7 @@ if __name__ == "__main__":
     if not os.path.exists(PART_1_OUTPUT_FOLDER):
         os.makedirs(PART_1_OUTPUT_FOLDER)
 
-    data = np.genfromtxt(PART_1_MINI_TRAIN_SET_PATH)
+    data = np.genfromtxt(PART_1_DATA_SET_PATH)
     x, labels = data[:, 1:], data[:, 0]
     # shift so that our labels start at zero
     shifted_labels = labels - jnp.min(labels)
@@ -31,59 +37,60 @@ if __name__ == "__main__":
 
     number_of_runs = 20
     percent_split = 0.8
-    run_splits = [split_train_test_data(x, y, percent_split) for _ in range(number_of_runs)]
 
-    train_test_data = TrainTestData(
-        x_train=np.array([run_split.x_train for run_split in run_splits]),
-        y_train=np.array([run_split.y_train for run_split in run_splits]),
-        x_test=np.array([run_split.x_test for run_split in run_splits]),
-        y_test=np.array([run_split.y_test for run_split in run_splits]),
-    )
-
-    # part_1.q1(
-    #     data=train_test_data,
-    #     kernel_class=PolynomialKernel(),
-    #     kernel_parameters=np.arange(1, 2),
-    #     kernel_parameter_name="degree",
-    #     number_of_runs=20,
-    #     number_of_epochs=5,
-    #     df_performance_path=os.path.join(PART_1_OUTPUT_FOLDER, "q1.csv")
-    # )
-
-    part_1.q2(
-        data=train_test_data,
[…]

### 2022-12-04 src/models/SSL.py

@@ -1,18 +1,18 @@
 import numpy as np
 
 
-class LaplacianInterpolation():
+class LaplacianInterpolation:
     def __init__(self):
         self.W = None
 
     def predict(self, W, y):
-        """ 
+        """
         Inputs:
-        
+
         X : design matrix of input variables
         y : set of labels for x_1, ..., x_l
 
-        Note: we have ordered our graph nodes so the first l datapoints are the 
+        Note: we have ordered our graph nodes so the first l datapoints are the
         labelled datapoints.
 
         The following expression was given in the paper provided, and hence used in
@@ -21,16 +21,18 @@ class LaplacianInterpolation():
         """
         s = y.shape[0]
         D = np.diag(W.sum(0))
-        return np.sign(np.linalg.lstsq(D[s:,s:] - W[s:,s:], W[s:,:s] @ y, rcond = None)[0])
+        return np.sign(
+            np.linalg.lstsq(D[s:, s:] - W[s:, s:], W[s:, :s] @ y, rcond=None)[0]
+        )
 
 
-class LaplacianKernelInterpolation():
+class LaplacianKernelInterpolation:
     def __init__(self):
         pass
 
-    def predict(self, W, y):        
+    def predict(self, W, y):
         L = np.diag(W.sum(0)) - W
         m = y.shape[0]
         L_pinv = np.linalg.pinv(L)
-        alpha = np.linalg.pinv(L_pinv[:m,:m]) @ y
-        return np.sign(L_pinv[:m,:].T @ alpha)[m:]
+        alpha = np.linalg.pinv(L_pinv[:m, :m]) @ y
+        return np.sign(L_pinv[:m, :].T @ alpha)[m:]

### 2022-12-04 src/models/helpers.py

@@ -12,6 +12,14 @@ class TrainTestData:
     x_test: np.ndarray
     y_test: np.ndarray
 
+    @property
+    def x(self):
+        return np.concatenate((self.x_train, self.x_test))
+
+    @property
+    def y(self):
+        return np.concatenate((self.y_train, self.y_test))
+
 
 def _build_train_test_data(x, y, indices):
     return TrainTestData(
@@ -55,23 +63,27 @@ def one_hot_encode(shifted_labels: np.ndarray) -> np.ndarray:
     number_classes = len(set(np.array(shifted_labels)))
     one_hot_encoding = np.eye(number_classes)[shifted_labels.astype(int)]
 
-    # return one hot encoding with (-1 , 1)
+    # one hot encoding with (-1 , 1)
     return 2 * one_hot_encoding - 1
 
 
 def ssl_data_sample(y, sample_size):
-    idxs = np.random.choice(list(np.where(y == -1.)[0]), size = sample_size, replace = False).tolist()
-    idxs += np.random.choice(list(np.where(y == 1.)[0]), size = sample_size, replace = False).tolist()
+    idxs = np.random.choice(
+        list(np.where(y == -1.0)[0]), size=sample_size, replace=False
+    ).tolist()
+    idxs += np.random.choice(
+        list(np.where(y == 1.0)[0]), size=sample_size, replace=False
+    ).tolist()
     idxs += [i for i in range(y.shape[0]) if i not in idxs]
     return idxs
 
 
-def KNN_adjacency_matrix(X,k):
+def KNN_adjacency_matrix(X, k):
     tree = KDTree(X)
     n = X.shape[0]
-    graph = tree.query(X, k)[1][:,1:]
-    W = np.zeros((n,n))
+    graph = tree.query(X, k)[1][:, 1:]
+    W = np.zeros((n, n))
     for i in range(n):
-        W[i,graph[i,:]] = 1
-        W[graph[i,:],i] = 1
+        W[i, graph[i, :]] = 1
+        W[graph[i, :], i] = 1
     return W

### 2022-12-04 src/models/perceptron.py

@@ -1,49 +1,81 @@
 from __future__ import annotations
 
-import jax.numpy as jnp
 import numpy as np
-from typing import Dict, Any, Tuple
+import jax.numpy as jnp
+from jax import jit
 
 
-class Perceptron:
-    @staticmethod
-    def train(
-        w: np.ndarray, gram: np.ndarray, y: np.ndarray, number_of_epochs: int
-    ) -> np.ndarray:
-        """
+def _predict(w: np.ndarray, gram: np.ndarray) -> jnp.ndarray:
+    """
+    prediction for a single data point (across all experiments)
+    :param w: weight matrix
+              (number_parameters, N_1,...,N_M, number_training_points, number_classes)
+    :param gram: precomputed gram matrix for a single input vs all training points (across all experiments)
+                 (number_parameters, N_1,...,N_M, number_training_points)
+    :return: a prediction for the single input (number_parameters, N_1,...,N_M, number_classes)
+    """
+    return jnp.sum(jnp.multiply(w, gram[..., None]), axis=-2)
 
-        :param w:
-        :param gram:
-        :param y:
-        :param number_of_epochs:
-        :return:
-        """
-        for _ in range(number_of_epochs):
-            for i in range(1, gram.shape[0]):
-                # make prediction
-                prediction = w.T @ gram[i, :]
 
-                # negative if prediction was incorrect
-                correct_prediction_indicator = jnp.multiply(y[i], prediction)
+def _compute_update(w: np.ndarray, y: np.ndarray, gram: np.ndarray) -> np.ndarray:
+    """
+    compute weight update for a single data point (across all experiments)
+    :param w: weight matrix
+              (number_parameters, N_1,...,N_M, number_training_points, number_classes)
+    :param gram: precomputed gram matrix for a single input vs all training points (across all experiments)
+                 (number_parameters, N_1,...,N_M, number_training_points)
+    :param y: matrix of a single response (across all experiments)
+              (N_1,...,N_M, number_classes)
+    :return: weight update for the weights pertaining to the single input (N_1,...,N_M, number_classes)
+    """
+    prediction = _predict(w, gram)
 
-                # zero if prediction was incorrect
-                clipped_correct_prediction_indicator = (
-                    correct_prediction_indicator.clip(0, 1)
-                )
+    # negative if prediction was incorrect across all parameters
+    correct_prediction_indicator = jnp.multiply(y[None, ...], prediction)
 
[…]

### 2022-12-04 src/models/winnow.py

@@ -1,0 +1,75 @@
+from __future__ import annotations
+
+import numpy as np
+import jax.numpy as jnp
+from jax import jit
+
+
+def _predict(w: np.ndarray, x: np.ndarray) -> jnp.ndarray:
+    """
+    prediction for a single data point (across all experiments)
+    :param w: weight matrix
+              (N_1,...,N_M, number_features)
+    :param x: input data point (across all experiments)
+              (N_1,...,N_M, number_features)
+    :return: winnow prediction
+             (N_1,...,N_M)
+    """
+    return (
+        (jnp.mean(jnp.multiply(w, x), axis=-1) - 1).clip(0, 1).astype(bool).astype(int)
+    )
+
+
+def _compute_update(w: np.ndarray, y: np.ndarray, x: np.ndarray) -> np.ndarray:
+    """
+    compute weight update for a single data point (across all experiments)
+    :param w: weight matrix
+              (N_1,...,N_M, number_features)
+    :param x: input data point (across all experiments)
+                 (N_1,...,N_M, number_features)
+    :param y: matrix of a responses (across all experiments)
+              (N_1,...,N_M)
+    :return: new weight matrix (N_1,...,N_M, number_features)
+    """
+    prediction = _predict(w, x)  # (N_1,...,N_M)
+    return jnp.multiply(w, 2 ** jnp.multiply((y - prediction)[..., None], x))
+
+
+def train(
+    w: np.ndarray, x: np.ndarray, y: np.ndarray, number_of_epochs: int
+) -> np.ndarray:
+    """
+    Vectorised winnow training by training multiple trials, etc. in parallel
+    The winnow is trained one data point at a time, the new weights depend on the weights of the previous
+    step, however each trial is independent, thus for our experiments, we can perform this in parallel.
+
+    All input matrices will share the first M dimensions representing the different independent experiments
+    that we want to train for. N_i will be the size of the ith dimension, and i = 1, 2, ..., M
+
+    :param w: initial weight matrix
+              (N_1,...,N_M, number_features)
+    :param x: design matrix
+              (N_1,...,N_M, number_features, number_training_points)
+    :param y: matrix of responses, the response for all parameter trials will be the same
+              (N_1,...,N_M, number_training_points)
+    :param number_of_epochs: number of epochs to train model
+    :return:
+    """
+    jit_compute_update = jit(_compute_update)
+    for _ in range(number_of_epochs):
[…]

### 2022-12-04 src/solutions/part_1.py

@@ -1,20 +1,14 @@
 from dataclasses import dataclass
+
+import matplotlib.pyplot as plt
 import pandas as pd
 import numpy as np
-import jax.numpy as jnp
 from jax import vmap
+from typing import List, Tuple
 
 from src.models.helpers import TrainTestData, make_folds
-from src.models.perceptron import Perceptron
+from src.models import perceptron
 from src.models.kernels import BaseKernel
-
-def _convert_to_scientific_notation(x: float) -> str:
-    """
-    Convert value to string in scientific notation
-    :param x: value to convert
-    :return: string of x in scientific notation
-    """
-    return "{:.2e}".format(float(x))
 
 
 @dataclass
@@ -39,176 +33,140 @@ class Performance:
         return df
 
 
-def _build_folds_data(x, y, number_of_folds):
-    x_train = []
-    y_train = []
-    x_test = []
-    y_test = []
-    number_of_runs = x.shape[0]
-    for i in range(number_of_runs):
-        folds = make_folds(
-            x=x[i],
-            y=y[i],
-            number_of_folds=number_of_folds,
-        )
-        min_fold_size_train = np.min([fold.x_train.shape[0] for fold in folds])
-        x_train.append(np.vstack([fold.x_train[None, :min_fold_size_train, ...] for fold in folds]))
-        y_train.append(np.vstack([fold.y_train[None, :min_fold_size_train, ...] for fold in folds]))
+def _analyse_prediction(actuals, predictions) -> Tuple[np.ndarray, np.ndarray]:
+    """
 
-        min_fold_size_test = np.min([fold.x_test.shape[0] for fold in folds])
-        x_test.append(np.vstack([fold.x_test[None, :min_fold_size_test, ...] for fold in folds]))
-        y_test.append(np.vstack([fold.y_test[None, :min_fold_size_test, ...] for fold in folds]))
-    return TrainTestData(
-        x_train=np.swapaxes(np.array(x_train), 0, 1),
-        y_train=np.swapaxes(np.array(y_train), 0, 1),
-        x_test=np.swapaxes(np.array(x_test), 0, 1),
-        y_test=np.swapaxes(np.array(y_test), 0, 1),
+    :param actuals: (N_1,...,N_M, number_of_test_points, number_classes)
+    :param predictions: (number_parameters, N_1,...,N_M, number_of_test_points, number_classes)
+    :return: comparison of labels (number_parameters, N_1,...,N_M, number_of_test_points)
+             and
+             confusion matrix
+    """
[…]

### 2022-12-04 src/solutions/q2.py

@@ -6,46 +6,52 @@ import pandas as pd
 import dataframe_image as dfi
 
 
-outpath =  os.path.join('outputs', 'part2')
-DATAPATH50 = os.path.join('data','dtrain13_50.dat')
-DATAPATH100 = os.path.join('data','dtrain13_100.dat')
-DATAPATH200 = os.path.join('data','dtrain13_200.dat')
-DATAPATH400 = os.path.join('data','dtrain13_400.dat')
-REPORT_LAPLACIAN_OUTPATH = os.path.join(outpath, 'laplacian_interpolation_report.png')
-REPORT_LAPLACIAN_KERNEL_OUTPATH = os.path.join(outpath, 'laplacian_kernel_interpolation_report.png')
+outpath = os.path.join("outputs", "part2")
+DATAPATH50 = os.path.join("data", "dtrain13_50.dat")
+DATAPATH100 = os.path.join("data", "dtrain13_100.dat")
+DATAPATH200 = os.path.join("data", "dtrain13_200.dat")
+DATAPATH400 = os.path.join("data", "dtrain13_400.dat")
+REPORT_LAPLACIAN_OUTPATH = os.path.join(outpath, "laplacian_interpolation_report.png")
+REPORT_LAPLACIAN_KERNEL_OUTPATH = os.path.join(
+    outpath, "laplacian_kernel_interpolation_report.png"
+)
+
 
 def experimental_report(
     model,
     datasets,
     n_iters,
-    ):
-    sample_range = [1,2,4,8,16]
-    accuracy = np.zeros((4,5,n_iters))
-    
+):
+    sample_range = [1, 2, 4, 8, 16]
+    accuracy = np.zeros((4, 5, n_iters))
+
     for iter in range(n_iters):
         for i, dataset in enumerate(datasets):
-            y = dataset[:,0]
-            W = KNN_adjacency_matrix(dataset[:,1:], k = 3)
+            y = dataset[:, 0]
+            W = KNN_adjacency_matrix(dataset[:, 1:], k=3)
             for j, sample_size in enumerate(sample_range):
-                sample = ssl_data_sample(y,sample_size)
-                y_train, y_test = y[sample[:2*sample_size]], y[sample[2*sample_size:]] 
-                accuracy[i,j,iter] = (model.predict(W[sample,:][:,sample], y_train) == y_test).mean()
+                sample = ssl_data_sample(y, sample_size)
+                y_train, y_test = (
[…]

### 2022-12-04 main.py
add results for gaussian kernel

@@ -18,8 +18,8 @@ from src.models.kernels import PolynomialKernel, GaussianKernel
 import jax
 
 if __name__ == "__main__":
-    jax.config.update("jax_platform_name", "cpu")
-    jax.config.update("jax_enable_x64", True)
+    # jax.config.update("jax_platform_name", "cpu")
+    # jax.config.update("jax_enable_x64", True)
 
     if not os.path.exists(OUTPUTS_FOLDER):
         os.makedirs(OUTPUTS_FOLDER)

### 2022-12-04 src/solutions/part_1.py

@@ -65,6 +65,12 @@ def _train_and_test(
     kernel_parameters,
     number_of_epochs,
 ):
+    # train_gram = np.array([kernel_class(
+    #         data.x_train, **{kernel_parameter_name: kernel_parameter}
+    #     ) for kernel_parameter in kernel_parameters])
+    # test_gram = np.array([kernel_class(
+    #         data.x_train, data.x_test, **{kernel_parameter_name: kernel_parameter}
+    #     ) for kernel_parameter in kernel_parameters])
     train_gram = vmap(
         lambda kernel_parameter: kernel_class(
             data.x_train, **{kernel_parameter_name: kernel_parameter}

### 2022-12-05 src/models/linear_regression_classifier.py
linear regression classifier

@@ -1,0 +1,9 @@
+import jax.numpy as jnp
+
+
+def train(x: jnp.ndarray, y: jnp.ndarray) -> jnp.ndarray:
+    return jnp.linalg.solve(x.T @ x, x.T @ y)
+
+
+def predict(w: jnp.ndarray, x: jnp.ndarray) -> jnp.ndarray:
+    return jnp.sign(x @ w)

### 2022-12-05 submission.tex
q2 report almost finished

@@
 \section{PART II}
-\subsection{Semi-supervised Leanrning via Laplacian Interpolation}
+\subsection{Semi-supervised Learning via Laplacian Interpolation}
+
 Experimental report for the laplacian interpolation approach:
@@
 
+Some observations to make here are:\\
+
+a) Both models seem to perform fairly well, even in the low-data setting.\\
+
+b) Increating the number of known labels increases the accuracy and decreases
+ the variance of the predictors.\\
+
+c) Increasing the total number of datapoints generally increases both model accuracies,
+and decreases variance. \\
+
+d) The laplacian kernel method outperforms the vanilla inerpolation approach considerably,
+on both accuracy and variance. \\
+
+The main reason for the success of this algorithm is the high degree of
+ cluster separation observed in the dataset.
+\\
+
+For illustration, here is a diagram representing the graph adjacency matrix,
+ with colours showing the labelling of an edge. Here blue edges are where both 
+labels are -1, teal when both are different, and yellow when both are +1.\\
+
+\includegraphics{outputs/part2/graph_label_diagram.png}#
+
+We see through this that the vast majority of datapoints are connected only to points
+of the same labelling, and that the graph is highly separated  into 2 clusters.
+Hence with minimal training information, both methods are able to predict with a
+ high degree of accuracy.\\
+
+Note that error variance decreases as a function of the number of known labels, but 
+has a muhc more significant impacgt for the vanilla interpolation method.
+
+We see that the kernel approach consistently outperforms the simple laplacian
+ interpolation method. A reasonable explanation for this is that the laplacian
+interpolation approach utilises local information to 'diffuse' labels through the graph. 
+This means that only datapoints close to labelled data receive information from the 
+labels themselves, and accuracy is likely reduced for datapoints far from the labels.
+In contrast, the kernel interpolation method takes global information from all the 
+labelled datapoints and weights them according to their proximity and connectedness 
+to eachother to predict labels.
 \newpage
@@
 \begin{itemize}
-    \item[1.]
-    \item[2.]
-    \item[3.]
+    \item[a.]
+    \item[b.]
+    \item[c.]
+    \item[D.]\\
+    We note that since for any $X_{t}$, $y_{t} = X_{1,t}$, we have the following
+     expression representing the linear separability of our dataset:\\
+    \[(v \cdot x_{t})y_{t} \ge 1\]\\
+    Where $v = (1,0, \dots, 0)^{T}$. Note that $\|v\| =1$.\\
+    Hence, in our online mistake bound for the perceptron, we have that $\gamma =1$.
+    Further note that $\forall t$, $x_{t} \in {-1,1}^{n} \implies \|x_{t}\|^{2}
+    = n$. This gives us that $R = max_{t} \|x_{t}\| = \sqrt{n}$.
+    Hence our mistake bound for the perceptron algorithm is given by:\\
+
+    \[M \le n \].\\
+
+    Using the theorem on page 60 of the online learning notes, we arrive at:\\
+
+    \[Prob(\mathcal{A_{S}}(x ^{\prime}) \ne y^{\prime} ) \le \frac{n}{m}\]\\
+
 \end{itemize}

### 2022-12-05 main.py

@@ -21,80 +21,79 @@ if __name__ == "__main__":
     # jax.config.update("jax_platform_name", "cpu")
     # jax.config.update("jax_enable_x64", True)
 
-    if not os.path.exists(OUTPUTS_FOLDER):
-        os.makedirs(OUTPUTS_FOLDER)
+    # if not os.path.exists(OUTPUTS_FOLDER):
+    #     os.makedirs(OUTPUTS_FOLDER)
 
-    # Question 1
-    PART_1_OUTPUT_FOLDER = os.path.join(OUTPUTS_FOLDER, "part1")
-    if not os.path.exists(PART_1_OUTPUT_FOLDER):
-        os.makedirs(PART_1_OUTPUT_FOLDER)
+    # # Question 1
+    # PART_1_OUTPUT_FOLDER = os.path.join(OUTPUTS_FOLDER, "part1")
+    # if not os.path.exists(PART_1_OUTPUT_FOLDER):
+    #     os.makedirs(PART_1_OUTPUT_FOLDER)
 
-    data = np.genfromtxt(PART_1_DATA_SET_PATH)
-    x, labels = data[:, 1:], data[:, 0]
-    # shift so that our labels start at zero
-    shifted_labels = labels - jnp.min(labels)
-    y = one_hot_encode(shifted_labels)
+    # data = np.genfromtxt(PART_1_DATA_SET_PATH)
+    # x, labels = data[:, 1:], data[:, 0]
+    # # shift so that our labels start at zero
+    # shifted_labels = labels - jnp.min(labels)
+    # y = one_hot_encode(shifted_labels)
 
-    number_of_runs = 20
-    percent_split = 0.8
+    # number_of_runs = 20
+    # percent_split = 0.8
 
-    part_1.q1(
-        data=[
-            split_train_test_data(x, y, percent_split) for _ in range(number_of_runs)
-        ],
-        kernel_class=PolynomialKernel(),
-        kernel_parameters=np.arange(1, 8),
-        kernel_parameter_name="degree",
-        number_of_epochs=1,
-        df_performance_path=os.path.join(PART_1_OUTPUT_FOLDER, "q1.csv"),
-    )
+    # part_1.q1(
+    #     data=[
+    #         split_train_test_data(x, y, percent_split) for _ in range(number_of_runs)
+    #     ],
+    #     kernel_class=PolynomialKernel(),
+    #     kernel_parameters=np.arange(1, 8),
+    #     kernel_parameter_name="degree",
[…]

### 2022-12-06 main.py
update figures and lin reg classifier

@@ -45,8 +45,8 @@ if __name__ == "__main__":
         kernel_class=PolynomialKernel(),
         kernel_parameters=np.arange(1, 8),
         kernel_parameter_name="degree",
-        number_of_epochs=1,
-        df_performance_path=os.path.join(PART_1_OUTPUT_FOLDER, "q1.csv"),
+        number_of_epochs=2,
+        df_performance_path=os.path.join(PART_1_OUTPUT_FOLDER, "q1"),
     )
 
     part_1.q2(
@@ -56,12 +56,12 @@ if __name__ == "__main__":
         kernel_class=PolynomialKernel(),
         kernel_parameters=np.arange(1, 8),
         kernel_parameter_name="degree",
-        number_of_epochs=1,
+        number_of_epochs=2,
         number_of_folds=5,
         labels=np.sort(list(set(labels))).astype(int),
-        df_performance_path=os.path.join(PART_1_OUTPUT_FOLDER, "q2.csv"),
-        df_confusion_matrix_path=os.path.join(PART_1_OUTPUT_FOLDER, "q2_confusion.csv"),
-        most_difficult_images_path=os.path.join(PART_1_OUTPUT_FOLDER, "q3.png"),
+        df_performance_path=os.path.join(PART_1_OUTPUT_FOLDER, "q2"),
+        df_confusion_matrix_path=os.path.join(PART_1_OUTPUT_FOLDER, "q3_confusion"),
+        most_difficult_images_path=os.path.join(PART_1_OUTPUT_FOLDER, "q4.png"),
     )
 
     part_1.q1(
@@ -71,8 +71,8 @@ if __name__ == "__main__":
         kernel_class=GaussianKernel(),
         kernel_parameters=np.arange(2e-3, 3e-2, 4e-3),
         kernel_parameter_name="sigma",
-        number_of_epochs=1,
-        df_performance_path=os.path.join(PART_1_OUTPUT_FOLDER, "q5_1.csv"),
+        number_of_epochs=2,
+        df_performance_path=os.path.join(PART_1_OUTPUT_FOLDER, "q5_1"),
     )
 
     part_1.q2(
@@ -82,11 +82,11 @@ if __name__ == "__main__":
         kernel_class=GaussianKernel(),
         kernel_parameters=np.arange(2e-3, 3e-2, 4e-3),
         kernel_parameter_name="sigma",
-        number_of_epochs=1,
+        number_of_epochs=2,
[…]

### 2022-12-06 src/models/linear_regression_classifier.py

@@ -1,8 +1,8 @@
 import jax.numpy as jnp
+import numpy as np
 
-
-def train(x: jnp.ndarray, y: jnp.ndarray) -> jnp.ndarray:
-    return jnp.linalg.solve(x.T @ x, x.T @ y)
+def train(x: np.ndarray, y: np.ndarray) -> np.ndarray:
+    return np.linalg.pinv(x) @ y
 
 
 def predict(w: jnp.ndarray, x: jnp.ndarray) -> jnp.ndarray:

### 2022-12-06 src/models/perceptron.py

@@ -42,7 +42,7 @@ def _compute_update(w: np.ndarray, y: np.ndarray, gram: np.ndarray) -> np.ndarra
 
 
 def train(
-    w: np.ndarray, gram: np.ndarray, y: np.ndarray, number_of_epochs: int
+    gram: np.ndarray, y: np.ndarray, number_of_epochs: int
 ) -> np.ndarray:
     """
     Vectorised perceptron training by training multiple trials, parameters, etc. in parallel
@@ -52,8 +52,6 @@ def train(
     All input matrices will share the first M dimensions representing the different independent experiments
     that we want to train for. N_i will be the size of the ith dimension, and i = 1, 2, ..., M
 
-    :param w: initial weight matrix
-              (number_parameters, N_1,...,N_M, number_training_points, number_classes)
     :param gram: precomputed gram matrix
                  (number_parameters, N_1,...,N_M, number_training_points, number_training_points)
     :param y: matrix of responses, the response for all parameter trials will be the same
@@ -61,6 +59,11 @@ def train(
     :param number_of_epochs: number of epochs to train model
     :return:
     """
+    number_of_parameters = gram.shape[0]
+    number_training_points = gram.shape[-1]
+    number_classes = y.shape[1]
+    w = np.zeros((number_of_parameters, number_training_points, number_classes))
+
     jit_compute_update = jit(_compute_update)
     for _ in range(number_of_epochs):
         for i in range(1, gram.shape[-2]):

### 2022-12-06 src/solutions/part_1.py

@@ -5,6 +5,7 @@ import pandas as pd
 import numpy as np
 from jax import vmap
 from typing import List, Tuple
+import dataframe_image as dfi
 
 from src.models.helpers import TrainTestData, make_folds
 from src.models import perceptron
@@ -58,7 +59,6 @@ def _analyse_prediction(actuals, predictions) -> Tuple[np.ndarray, np.ndarray]:
 
 
 def _train_and_test(
-    w,
     data: TrainTestData,
     kernel_class: BaseKernel,
     kernel_parameter_name,
@@ -82,7 +82,6 @@ def _train_and_test(
         )
     )(kernel_parameters)
     weights = perceptron.train(
-        w=w,
         gram=train_gram,
         y=data.y_train,
         number_of_epochs=number_of_epochs,
@@ -95,7 +94,7 @@ def _train_and_test(
         data.y_test, test_predictions
     )
     return (
-        w,
+        weights,
         np.mean(~train_comparisons, axis=-1),
         np.mean(~test_comparisons, axis=-1),
         test_confusion_matrix,
@@ -122,14 +121,13 @@ def _q1(
         i,
         data_run,
     ) in enumerate(data):
-        number_training_points = data[i].x_train.shape[0]
+
         (
             w,
             train_errors[:, i],
             test_errors[:, i],
             test_confusion_matrix[:, i, :, :],
         ) = _train_and_test(
-            w=np.zeros((number_of_parameters, number_training_points, number_classes)),
             data=data_run,
             kernel_class=kernel_class,
             kernel_parameter_name=kernel_parameter_name,
@@ -160,7 +158,7 @@ def q1(
         stdev=np.std(test_error, axis=-1),
     )
 
-    pd.concat(
+    df = pd.concat(
         [
             train_performance.build_df(
                 kernel_parameters=[
@@ -177,7 +175,9 @@ def q1(
                 index="Test",
             ),
         ]
-    ).to_csv(df_performance_path)
+    ).T
+    df.to_csv(df_performance_path+".csv")
+    dfi.export(df, df_performance_path+".png")
 
 
 def q2(
@@ -238,13 +238,15 @@ def q2(
             -1,
         ),
     )
-    test_performance.build_df(
+    df_test_performance = test_performance.build_df(
         kernel_parameters=[
[…]

### 2022-12-06 main.py
formatting

@@ -1,5 +1,6 @@
 import os
 
+import jax
 import jax.numpy as jnp
 import numpy as np
 import pandas as pd
@@ -8,92 +9,91 @@ from src.constants import (
     DATA_FOLDER,
     DEFAULT_SEED,
     OUTPUTS_FOLDER,
-    PART_1_MINI_TRAIN_SET_PATH,
     PART_1_DATA_SET_PATH,
+    PART_1_MINI_TRAIN_SET_PATH,
 )
-from src.solutions.q2 import q2
-from src.solutions import part_1
 from src.models.helpers import one_hot_encode, split_train_test_data
-from src.models.kernels import PolynomialKernel, GaussianKernel
-import jax
+from src.models.kernels import GaussianKernel, PolynomialKernel
+from src.solutions import part_1
+from src.solutions.q2 import q2
 
 if __name__ == "__main__":
-    # jax.config.update("jax_platform_name", "cpu")
-    # jax.config.update("jax_enable_x64", True)
-    #
-    # if not os.path.exists(OUTPUTS_FOLDER):
-    #     os.makedirs(OUTPUTS_FOLDER)
-    #
-    # # Question 1
-    # PART_1_OUTPUT_FOLDER = os.path.join(OUTPUTS_FOLDER, "part1")
-    # if not os.path.exists(PART_1_OUTPUT_FOLDER):
-    #     os.makedirs(PART_1_OUTPUT_FOLDER)
-    #
-    # data = np.genfromtxt(PART_1_DATA_SET_PATH)
-    # x, labels = data[:, 1:], data[:, 0]
-    # # shift so that our labels start at zero
-    # shifted_labels = labels - jnp.min(labels)
-    # y = one_hot_encode(shifted_labels)
-    #
-    # number_of_runs = 20
-    # percent_split = 0.8
-    #
-    # part_1.q1(
-    #     data=[
-    #         split_train_test_data(x, y, percent_split) for _ in range(number_of_runs)
-    #     ],
-    #     kernel_class=PolynomialKernel(),
-    #     kernel_parameters=np.arange(1, 8),
-    #     kernel_parameter_name="degree",
-    #     number_of_epochs=2,
-    #     df_performance_path=os.path.join(PART_1_OUTPUT_FOLDER, "q1"),
-    # )
-    #
-    # part_1.q2(
-    #     data=[
-    #         split_train_test_data(x, y, percent_split) for _ in range(number_of_runs)
[…]

### 2022-12-06 src/models/kernels.py

@@ -1,10 +1,11 @@
 from __future__ import annotations
 
 from abc import ABC, abstractmethod
-import numpy as np
+from typing import Any, Dict, Tuple
+
 import jax.numpy as jnp
-from jax import vmap, jit, tree_util
-from typing import Dict, Any, Tuple
+import numpy as np
+from jax import jit, tree_util, vmap
 
 
 class BaseKernel(ABC):

### 2022-12-06 src/models/linear_regression_classifier.py

@@ -1,6 +1,7 @@
 import jax.numpy as jnp
 import numpy as np
 
+
 def train(x: np.ndarray, y: np.ndarray) -> np.ndarray:
     return np.linalg.pinv(x) @ y
 

### 2022-12-06 src/models/perceptron.py

@@ -1,7 +1,7 @@
 from __future__ import annotations
 
-import numpy as np
 import jax.numpy as jnp
+import numpy as np
 from jax import jit
 
 
@@ -41,9 +41,7 @@ def _compute_update(w: np.ndarray, y: np.ndarray, gram: np.ndarray) -> np.ndarra
     return jnp.multiply(y[None, ...], update_mask)
 
 
-def train(
-    gram: np.ndarray, y: np.ndarray, number_of_epochs: int
-) -> np.ndarray:
+def train(gram: np.ndarray, y: np.ndarray, number_of_epochs: int) -> np.ndarray:
     """
     Vectorised perceptron training by training multiple trials, parameters, etc. in parallel
     The perceptron is trained one data point at a time, the new weights depend on the weights of the previous

### 2022-12-06 src/solutions/part_1.py

@@ -1,14 +1,14 @@
 from dataclasses import dataclass
-
-import matplotlib.pyplot as plt
-import pandas as pd
-import numpy as np
-from jax import vmap
 from typing import List, Tuple
-import dataframe_image as dfi
 
-from src.models.helpers import TrainTestData, make_folds
+import dataframe_image as dfi
+import matplotlib.pyplot as plt
+import numpy as np
+import pandas as pd
+from jax import vmap
+
 from src.models import perceptron
+from src.models.helpers import TrainTestData, make_folds
 from src.models.kernels import BaseKernel
 
 
@@ -176,8 +176,8 @@ def q1(
             ),
         ]
     ).T
-    df.to_csv(df_performance_path+".csv")
-    dfi.export(df, df_performance_path+".png")
+    df.to_csv(df_performance_path + ".csv")
+    dfi.export(df, df_performance_path + ".png")
 
 
 def q2(
@@ -245,8 +245,8 @@ def q2(
         kernel_parameter_name=f"Mean Optimal {kernel_parameter_name}",
         index="Test Error Rate",
     ).T
-    df_test_performance.to_csv(df_performance_path+".csv")
-    dfi.export(df_test_performance, df_performance_path+".png")
+    df_test_performance.to_csv(df_performance_path + ".csv")
+    dfi.export(df_test_performance, df_performance_path + ".png")
 
     test_confusion_matrix = (
         test_confusion_matrix / test_confusion_matrix.sum(axis=2)[..., None]
@@ -266,8 +266,8 @@ def q2(
         columns=labels,
     )
     df.index = labels
-    df.to_csv(df_confusion_matrix_path+".csv")
-    dfi.export(df, df_confusion_matrix_path+".png")
+    df.to_csv(df_confusion_matrix_path + ".csv")
+    dfi.export(df, df_confusion_matrix_path + ".png")
 
     # find hardest to predict images
     # for each model, predict on the entire dataset
@@ -293,6 +293,6 @@ def q2(
     for i in range(len(most_difficult_image_indices)):
         ax[i].imshow(most_difficult_images[i].reshape(16, 16))
         ax[i].title.set_text(f"Label={most_difficult_labels[i]}")
-        ax[i].axis('off')
+        ax[i].axis("off")
     plt.savefig(most_difficult_images_path)
     plt.close(fig)

### 2022-12-06 src/models/1_NN.py
1-nn added

@@ -1,0 +1,5 @@
+from sklearn.neighbors import KDTree
+
+def KNN_predict(X_train,y_train, X_test, K):
+    tree = KDTree(X_train)
+    return y_train[tree.query(X_test, k=1)[1]]

### 2022-12-06 src/models/SSL.py

@@ -9,8 +9,12 @@ class LaplacianInterpolation:
         """
         Inputs:
 
-        X : design matrix of input variables
+        W : 3-NN adjacency matrix for the datapoints in X
         y : set of labels for x_1, ..., x_l
+
+        Output:
+
+        y_hat: predicted labels for y_{l+1}, ... , y_{n} 
 
         Note: we have ordered our graph nodes so the first l datapoints are the
         labelled datapoints.
@@ -31,6 +35,19 @@ class LaplacianKernelInterpolation:
         pass
 
     def predict(self, W, y):
+        
+        """
+        Inputs:
+
+        W : 3-NN adjacency matrix for the datapoints in X
+        y : set of labels for x_1, ..., x_l
+
+        Output:
+        
+        y_hat: predicted labels for y_{l+1}, ... , y_{n} 
+        
+        """
+
         L = np.diag(W.sum(0)) - W
         m = y.shape[0]
         L_pinv = np.linalg.pinv(L)

### 2022-12-06 main.py
add rough part 3

@@ -15,7 +15,7 @@ from src.constants import (
 from src.models.helpers import one_hot_encode, split_train_test_data
 from src.models.kernels import GaussianKernel, PolynomialKernel
 from src.solutions import part_1
-from src.solutions.q2 import q2
+from src.solutions.part_2 import q2
 
 if __name__ == "__main__":
     jax.config.update("jax_platform_name", "cpu")

### 2022-12-06 src/models/1_NN.py

@@ -1,5 +1,0 @@
-from sklearn.neighbors import KDTree
-
-def KNN_predict(X_train,y_train, X_test, K):
-    tree = KDTree(X_train)
-    return y_train[tree.query(X_test, k=1)[1]]

### 2022-12-06 src/models/SSL.py

@@ -14,7 +14,7 @@ class LaplacianInterpolation:
 
         Output:
 
-        y_hat: predicted labels for y_{l+1}, ... , y_{n} 
+        y_hat: predicted labels for y_{l+1}, ... , y_{n}
 
         Note: we have ordered our graph nodes so the first l datapoints are the
         labelled datapoints.
@@ -35,7 +35,7 @@ class LaplacianKernelInterpolation:
         pass
 
     def predict(self, W, y):
-        
+
         """
         Inputs:
 
@@ -43,9 +43,9 @@ class LaplacianKernelInterpolation:
         y : set of labels for x_1, ..., x_l
 
         Output:
-        
-        y_hat: predicted labels for y_{l+1}, ... , y_{n} 
-        
+
+        y_hat: predicted labels for y_{l+1}, ... , y_{n}
+
         """
 
         L = np.diag(W.sum(0)) - W

### 2022-12-06 src/models/one_nn.py

@@ -1,0 +1,6 @@
+from sklearn.neighbors import KDTree
+
+
+def one_nn_predict(X_train, y_train, X_test):
+    tree = KDTree(X_train)
+    return y_train[tree.query(X_test, k=1)[1]].reshape(-1, 1)

### 2022-12-06 src/solutions/part_3.py

@@ -1,0 +1,81 @@
+import matplotlib.pyplot as plt
+import numpy as np
+
+from src.models import linear_regression_classifier
+from src.models.one_nn import one_nn_predict
+
+
+def generate_data(m, n):
+    x = np.random.choice([-1, 1], size=(m, n))
+    y = x[:, :1]
+    return x, y
+
+
+dimensions = np.arange(1, 21)
+number_train_points = np.arange(1, 50)
+number_of_iterations = 1000
+percentage = 1e-2
+m_test = int(1e3)
+
+mean_number_train_points = np.zeros((len(dimensions)))
+squared_mean_number_train_points = np.zeros((len(dimensions)))
+
+for i, n in enumerate(dimensions):
+    for j in range(number_of_iterations):
+        for k, m in enumerate(number_train_points):
+            x_train, y_train = generate_data(m, n)
+            w = linear_regression_classifier.train(x_train, y_train)
+
+            x_test, y_test = generate_data(m_test, n)
+            y_pred = linear_regression_classifier.predict(w, x_test)
+            if np.mean(y_pred != y_test) < 0.1:
+                mean_number_train_points[i] = (mean_number_train_points[i] * j + m) / (
+                    j + 1
+                )
+                squared_mean_number_train_points[i] = (
+                    squared_mean_number_train_points[i] * j + m**2
+                ) / (j + 1)
+                break
+
+variance_number_train_points = (
+    squared_mean_number_train_points - mean_number_train_points**2
+)
+
+plt.errorbar(
+    dimensions, mean_number_train_points, yerr=variance_number_train_points, capsize=2
+)
+
+
+dimensions = np.arange(1, 11)
+number_train_points = np.arange(1, 201)
+number_of_iterations = 1000
+percentage = 1e-2
+m_test = int(1e3)
+
+mean_number_train_points = np.ones((len(dimensions))) * np.nan
+squared_mean_number_train_points = np.ones((len(dimensions))) * np.nan
+
+for i, n in enumerate(dimensions):
+    for _ in range(number_of_iterations):
+        j = 0
+        for k, m in enumerate(number_train_points):
+            x_train, y_train = generate_data(m, n)
+            x_test, y_test = generate_data(m_test, n)
+
+            y_pred = one_nn_predict(x_train, y_train, x_test)
+            if np.mean(y_pred != y_test) < 0.1:
+                mean_number_train_points[i] = np.nansum(
+                    [mean_number_train_points[i] * j, m]
[…]

### 2022-12-06 main.py
part 3 models

@@ -14,7 +14,11 @@ from src.constants import (
 )
 from src.models.helpers import one_hot_encode, split_train_test_data
 from src.models.kernels import GaussianKernel, PolynomialKernel
-from src.solutions import part_1
+from src.models.linear_regression_classifier import LinearRegressionClassifier
+from src.models.one_nn import OneNN
+from src.models.single_class_perceptron import SingleClassPerceptron
+from src.models.winnow import Winnow
+from src.solutions import part_1, part_3
 from src.solutions.part_2 import q2
 
 if __name__ == "__main__":
@@ -97,3 +101,42 @@ if __name__ == "__main__":
     if not os.path.exists(PART_2_OUTPUT_FOLDER):
         os.makedirs(PART_2_OUTPUT_FOLDER)
     q2()
+
+    # Question 3
+    PART_3_OUTPUT_FOLDER = os.path.join(OUTPUTS_FOLDER, "part3")
+    if not os.path.exists(PART_3_OUTPUT_FOLDER):
+        os.makedirs(PART_3_OUTPUT_FOLDER)
+    part_3.a(
+        model=OneNN(),
+        dimensions=np.arange(1, 11),
+        number_train_points=np.arange(1, 101),
+        number_of_trials=10,
+        m_test=20,
+        figure_save_path=os.path.join(PART_3_OUTPUT_FOLDER, "q1a_one_nn.png"),
+    )
+    part_3.a(
+        model=Winnow(),
+        dimensions=np.arange(2, 11),
+        number_train_points=np.arange(2, 101),
+        number_of_trials=10,
+        m_test=20,
+        figure_save_path=os.path.join(PART_3_OUTPUT_FOLDER, "q1a_winnow.png"),
+    )
+    part_3.a(
+        model=LinearRegressionClassifier(),
+        dimensions=np.arange(2, 11),
+        number_train_points=np.arange(2, 101),
+        number_of_trials=10,
+        m_test=20,
+        figure_save_path=os.path.join(PART_3_OUTPUT_FOLDER, "q1a_lin_reg.png"),
+    )
+    part_3.a(
+        model=SingleClassPerceptron(
+            kernel=PolynomialKernel(), kernel_kwargs={"degree": 1}
+        ),
+        dimensions=np.arange(3, 11),
+        number_train_points=np.arange(2, 50),
+        number_of_trials=10,
+        m_test=20,
+        figure_save_path=os.path.join(PART_3_OUTPUT_FOLDER, "q1a_perceptron.png"),
+    )

### 2022-12-06 src/models/linear_regression_classifier.py

@@ -1,10 +1,16 @@
 import jax.numpy as jnp
 import numpy as np
 
-
-def train(x: np.ndarray, y: np.ndarray) -> np.ndarray:
-    return np.linalg.pinv(x) @ y
+from src.models.model import Model
 
 
-def predict(w: jnp.ndarray, x: jnp.ndarray) -> jnp.ndarray:
-    return jnp.sign(x @ w)
+class LinearRegressionClassifier(Model):
+    def __init__(self, w=None):
+        self.w: np.ndarray = w
+        super().__init__()
+
+    def fit(self, x: np.ndarray, y: np.ndarray, **kwargs) -> None:
+        self.w = np.linalg.pinv(x.T) @ y
+
+    def predict(self, x: jnp.ndarray) -> jnp.ndarray:
+        return jnp.sign(x.T @ self.w)

### 2022-12-06 src/models/model.py

@@ -1,0 +1,31 @@
+from abc import ABC, abstractmethod
+
+import numpy as np
+
+
+class Model(ABC):
+    def __init__(self):
+        pass
+
+    """
+    Abstract model class
+    """
+
+    @abstractmethod
+    def fit(self, x: np.ndarray, y: np.ndarray, **kwargs) -> None:
+        """
+        Fitting model
+        :param x: dataset of shape (number of dimensions, number of examples)
+        :param y: labels of shape (number of examples, 1)
+        :return: None
+        """
+        pass
+
+    @abstractmethod
+    def predict(self, x: np.ndarray) -> np.ndarray:
+        """
+        Prediction of x
+        :param x: dataset of shape (number of dimensions, number of examples)
+        :return: predicted labels of shape (number of examples, 1)
+        """
+        pass

### 2022-12-06 src/models/one_nn.py

@@ -1,6 +1,22 @@
+import numpy as np
 from sklearn.neighbors import KDTree
 
+from src.models.model import Model
 
-def one_nn_predict(X_train, y_train, X_test):
-    tree = KDTree(X_train)
-    return y_train[tree.query(X_test, k=1)[1]].reshape(-1, 1)
+
+class OneNN(Model):
+    k = 1
+
+    def __init__(self, tree=None, y=None):
+        self.tree: KDTree = tree
+        self.y: np.ndarray = y
+        super().__init__()
+
+    def fit(self, x: np.ndarray, y: np.ndarray, **kwargs) -> None:
+        self.tree = KDTree(x.T)
+        self.y = y
+
+    def predict(self, x: np.ndarray) -> np.ndarray:
+        return self.y[self.tree.query(x.T, k=self.k)[1]].reshape(
+            -1,
+        )

### 2022-12-06 src/models/single_class_perceptron.py

@@ -1,0 +1,79 @@
+from typing import Any, Dict
+
+import numpy as np
+
+from src.models.kernels import BaseKernel
+from src.models.model import Model
+
+
+class SingleClassPerceptron(Model):
+    def __init__(
+        self, kernel: BaseKernel, kernel_kwargs: Dict[str, Any], w=None, x=None
+    ):
+        self.kernel = kernel
+        self.kernel_kwargs = kernel_kwargs
+        self.x: np.ndarray = x
+        self.w: np.ndarray = w
+        super().__init__()
+
+    @staticmethod
+    def _predict(w: np.ndarray, gram: np.ndarray) -> np.ndarray:
+        """
+        prediction for a single data point (across all experiments)
+
+        :param gram: gram matrix
+                     (number_features, number_points)
+        :return: a prediction for the single input
+        """
+        return np.sign(w @ gram)
+
+    @staticmethod
+    def _compute_update(w: np.ndarray, y: np.ndarray, gram: np.ndarray) -> np.ndarray:
+        """
+        compute weight update for a single data point (across all experiments)
+        :param w: weight matrix
+                  (number_training_points)
+        :param gram: gram matrix
+                     (number_features, number_features)
+        :param y: matrix of a single response
+        :return: weight update for the weights pertaining to the single input
+        """
+        prediction = SingleClassPerceptron._predict(w, gram)
+
+        return (y != prediction) * y
+
+    def fit(self, x: np.ndarray, y: np.ndarray, **kwargs) -> None:
+        """
+        All input matrices will share the first M dimensions representing the different independent experiments
+        that we want to train for. N_i will be the size of the ith dimension, and i = 1, 2, ..., M
+
+        :param x: design matrix
+                  (number_training_points, number_of_dimensions)
+        :param y: matrix of responses, the response for all parameter trials will be the same
+                  (number_training_points)
+        :return:
+        """
+        if "number_of_epochs" in kwargs:
+            number_of_epochs = kwargs["number_of_epochs"]
+        else:
+            number_of_epochs = 1
+
+        self.x = x
+        gram = self.kernel(x, **self.kernel_kwargs)
+
+        self.w = np.zeros(y.shape)
+
+        for _ in range(number_of_epochs):
+            for i in range(1, len(self.w)):
+                self.w[i] += self._compute_update(w=self.w, y=y[i], gram=gram[:, i])
+
+    def predict(self, x: np.ndarray) -> np.ndarray:
+        """
[…]

### 2022-12-06 src/models/winnow.py

@@ -1,75 +1,95 @@
-from __future__ import annotations
-
-import jax.numpy as jnp
 import numpy as np
-from jax import jit
+
+from src.models.model import Model
 
 
-def _predict(w: np.ndarray, x: np.ndarray) -> jnp.ndarray:
-    """
-    prediction for a single data point (across all experiments)
-    :param w: weight matrix
-              (N_1,...,N_M, number_features)
-    :param x: input data point (across all experiments)
-              (N_1,...,N_M, number_features)
-    :return: winnow prediction
-             (N_1,...,N_M)
-    """
-    return (
-        (jnp.mean(jnp.multiply(w, x), axis=-1) - 1).clip(0, 1).astype(bool).astype(int)
-    )
+class Winnow(Model):
+    def __init__(self, w=None):
+        self.w: np.ndarray = w
+        super().__init__()
 
+    @staticmethod
+    def _preprocess(y):
+        y[y == -1] = 0
+        return y
 
-def _compute_update(w: np.ndarray, y: np.ndarray, x: np.ndarray) -> np.ndarray:
-    """
-    compute weight update for a single data point (across all experiments)
-    :param w: weight matrix
-              (N_1,...,N_M, number_features)
-    :param x: input data point (across all experiments)
-                 (N_1,...,N_M, number_features)
-    :param y: matrix of a responses (across all experiments)
-              (N_1,...,N_M)
-    :return: new weight matrix (N_1,...,N_M, number_features)
-    """
-    prediction = _predict(w, x)  # (N_1,...,N_M)
-    return jnp.multiply(w, 2 ** jnp.multiply((y - prediction)[..., None], x))
+    @staticmethod
+    def _postprocess(y):
+        y[y == 0] = -1
+        return y
 
+    @staticmethod
+    def _predict(w: np.ndarray, x: np.ndarray) -> np.ndarray:
+        """
+        prediction for a single data point (across all experiments)
+        :param w: weight matrix
+                  (N_1,...,N_M, number_features)
+        :param x: input data point (across all experiments)
+                  (N_1,...,N_M, number_features)
+        :return: winnow prediction
+                 (N_1,...,N_M)
+        """
+        return (
+            (np.mean(np.multiply(w, x), axis=-1) - 1)
+            .clip(0, 1)
+            .astype(bool)
+            .astype(int)
+        )
 
-def train(
-    w: np.ndarray, x: np.ndarray, y: np.ndarray, number_of_epochs: int
[…]

### 2022-12-06 src/solutions/part_3.py

@@ -1,81 +1,54 @@
 import matplotlib.pyplot as plt
 import numpy as np
 
-from src.models import linear_regression_classifier
-from src.models.one_nn import one_nn_predict
+from src.models.model import Model
 
 
-def generate_data(m, n):
+def generate_data(m: int, n: int):
+    """
+    Generate data with the provided protocol
+    :param m: number of examples
+    :param n: number of dimensions
+    :return: Tuple containing an array of patterns (m, n) and an array of labels (m,)
+    """
     x = np.random.choice([-1, 1], size=(m, n))
-    y = x[:, :1]
+    y = x[:, 0]
     return x, y
 
 
-dimensions = np.arange(1, 21)
-number_train_points = np.arange(1, 50)
-number_of_iterations = 1000
-percentage = 1e-2
-m_test = int(1e3)
+def a(
+    model: Model,
+    dimensions: np.ndarray,
+    number_train_points: np.ndarray,
+    number_of_trials: int,
+    m_test: int,
+    figure_save_path: str,
+    generalisation_error: float = 0.1,
+):
+    number_of_dimensions = len(dimensions)
+    train_points_for_generalisation_error = (
+        np.ones((number_of_dimensions, number_of_trials)) * np.nan
+    )
 
-mean_number_train_points = np.zeros((len(dimensions)))
-squared_mean_number_train_points = np.zeros((len(dimensions)))
+    for i, n in enumerate(dimensions):
+        for j in range(number_of_trials):
+            for k, m in enumerate(number_train_points):
+                x_train, y_train = generate_data(m, n)
+                model.fit(x_train, y_train)
 
-for i, n in enumerate(dimensions):
-    for j in range(number_of_iterations):
-        for k, m in enumerate(number_train_points):
-            x_train, y_train = generate_data(m, n)
-            w = linear_regression_classifier.train(x_train, y_train)
-
-            x_test, y_test = generate_data(m_test, n)
-            y_pred = linear_regression_classifier.predict(w, x_test)
-            if np.mean(y_pred != y_test) < 0.1:
-                mean_number_train_points[i] = (mean_number_train_points[i] * j + m) / (
-                    j + 1
-                )
-                squared_mean_number_train_points[i] = (
-                    squared_mean_number_train_points[i] * j + m**2
-                ) / (j + 1)
-                break
-
-variance_number_train_points = (
-    squared_mean_number_train_points - mean_number_train_points**2
-)
-
-plt.errorbar(
[…]

### 2022-12-06 main.py
part 3 models

@@ -28,79 +28,79 @@ if __name__ == "__main__":
     if not os.path.exists(OUTPUTS_FOLDER):
         os.makedirs(OUTPUTS_FOLDER)
 
-    # Question 1
-    PART_1_OUTPUT_FOLDER = os.path.join(OUTPUTS_FOLDER, "part1")
-    if not os.path.exists(PART_1_OUTPUT_FOLDER):
-        os.makedirs(PART_1_OUTPUT_FOLDER)
-
-    data = np.genfromtxt(PART_1_DATA_SET_PATH)
-    x, labels = data[:, 1:], data[:, 0]
-    # shift so that our labels start at zero
-    shifted_labels = labels - jnp.min(labels)
-    y = one_hot_encode(shifted_labels)
-
-    number_of_runs = 20
-    percent_split = 0.8
-
-    part_1.q1(
-        data=[
-            split_train_test_data(x, y, percent_split) for _ in range(number_of_runs)
-        ],
-        kernel_class=PolynomialKernel(),
-        kernel_parameters=np.arange(1, 8),
-        kernel_parameter_name="degree",
-        number_of_epochs=2,
-        df_performance_path=os.path.join(PART_1_OUTPUT_FOLDER, "q1"),
-    )
-
-    part_1.q2(
-        data=[
-            split_train_test_data(x, y, percent_split) for _ in range(number_of_runs)
-        ],
-        kernel_class=PolynomialKernel(),
-        kernel_parameters=np.arange(1, 8),
-        kernel_parameter_name="degree",
-        number_of_epochs=2,
-        number_of_folds=5,
-        labels=np.sort(list(set(labels))).astype(int),
-        df_performance_path=os.path.join(PART_1_OUTPUT_FOLDER, "q2"),
-        df_confusion_matrix_path=os.path.join(PART_1_OUTPUT_FOLDER, "q3_confusion"),
-        most_difficult_images_path=os.path.join(PART_1_OUTPUT_FOLDER, "q4.png"),
-    )
-
-    part_1.q1(
-        data=[
-            split_train_test_data(x, y, percent_split) for _ in range(number_of_runs)
-        ],
-        kernel_class=GaussianKernel(),
-        kernel_parameters=np.arange(2e-3, 3e-2, 4e-3),
-        kernel_parameter_name="sigma",
-        number_of_epochs=2,
[…]

### 2022-12-06 src/models/linear_regression_classifier.py

@@ -10,7 +10,7 @@ class LinearRegressionClassifier(Model):
         super().__init__()
 
     def fit(self, x: np.ndarray, y: np.ndarray, **kwargs) -> None:
-        self.w = np.linalg.pinv(x.T) @ y
+        self.w = np.linalg.pinv(x) @ y
 
     def predict(self, x: jnp.ndarray) -> jnp.ndarray:
-        return jnp.sign(x.T @ self.w)
+        return jnp.sign(x @ self.w)

### 2022-12-06 src/models/one_nn.py

@@ -13,10 +13,10 @@ class OneNN(Model):
         super().__init__()
 
     def fit(self, x: np.ndarray, y: np.ndarray, **kwargs) -> None:
-        self.tree = KDTree(x.T)
+        self.tree = KDTree(x)
         self.y = y
 
     def predict(self, x: np.ndarray) -> np.ndarray:
-        return self.y[self.tree.query(x.T, k=self.k)[1]].reshape(
+        return self.y[self.tree.query(x, k=self.k)[1]].reshape(
             -1,
         )

### 2022-12-06 src/models/winnow.py

@@ -23,11 +23,10 @@ class Winnow(Model):
         """
         prediction for a single data point (across all experiments)
         :param w: weight matrix
-                  (N_1,...,N_M, number_features)
+                  (number_of_dimensions)
         :param x: input data point (across all experiments)
-                  (N_1,...,N_M, number_features)
+                  (number_points, number_of_dimensions)
         :return: winnow prediction
-                 (N_1,...,N_M)
         """
         return (
             (np.mean(np.multiply(w, x), axis=-1) - 1)
@@ -41,12 +40,11 @@ class Winnow(Model):
         """
         compute weight update for a single data point (across all experiments)
         :param w: weight matrix
-                  (N_1,...,N_M, number_features)
+                  (number_of_dimensions)
         :param x: input data point (across all experiments)
-                     (N_1,...,N_M, number_features)
-        :param y: matrix of a responses (across all experiments)
-                  (N_1,...,N_M)
-        :return: new weight matrix (N_1,...,N_M, number_features)
+                     (number_of_dimensions)
+        :param y: response
+        :return: new weight update (number_of_dimensions)
         """
         prediction = Winnow._predict(w, x)  # (N_1,...,N_M)
         return np.multiply(
@@ -63,9 +61,9 @@ class Winnow(Model):
         that we want to train for. N_i will be the size of the ith dimension, and i = 1, 2, ..., M
 
         :param x: design matrix
-                  (number_features, number_training_points)
+                  (number_training_points, number_of_dimensions)
         :param y: matrix of responses, the response for all parameter trials will be the same
-                  (N_1,...,N_M, number_training_points)
+                  (number_training_points)
         :param **kwargs: number_of_epochs: number of epochs to train model
         :return:
         """
@@ -74,22 +72,18 @@ class Winnow(Model):
         else:
             number_of_epochs = 1
 
-        self.w = np.ones((x.shape[:-1]))
+        self.w = np.ones(x.shape[1])
         y = self._preprocess(y)
         for _ in range(number_of_epochs):
-            for i in range(1, x.shape[-1]):
-                self.w = self._compute_update(self.w, y=y[..., i], x=x[..., i])
+            for i in range(1, x.shape[0]):
+                self.w = self._compute_update(self.w, y=y[i], x=x[i, :])
 
     def predict(self, x: np.ndarray) -> np.ndarray:
         """
         winnow prediction
         :param x: design matrix
-                  (N_1,...,N_M, number_features, number_of_test_points)
[…]

### 2022-12-07 main.py
knn implementation and refactor

@@ -1,25 +1,13 @@
 import os
 
 import jax
-import jax.numpy as jnp
 import numpy as np
-import pandas as pd
 
 from src.constants import (
-    DATA_FOLDER,
-    DEFAULT_SEED,
     OUTPUTS_FOLDER,
-    PART_1_DATA_SET_PATH,
-    PART_1_MINI_TRAIN_SET_PATH,
 )
-from src.models.helpers import one_hot_encode, split_train_test_data
-from src.models.kernels import GaussianKernel, PolynomialKernel
-from src.models.linear_regression_classifier import LinearRegressionClassifier
-from src.models.one_nn import OneNN
-from src.models.single_class_perceptron import SingleClassPerceptron
-from src.models.winnow import Winnow
-from src.solutions import part_1, part_3
-from src.solutions.part_2 import q2
+from src.models.single_class.one_nn import OneNN
+from src.solutions import part_3
 
 if __name__ == "__main__":
     jax.config.update("jax_platform_name", "cpu")
@@ -106,37 +94,56 @@ if __name__ == "__main__":
     PART_3_OUTPUT_FOLDER = os.path.join(OUTPUTS_FOLDER, "part3")
     if not os.path.exists(PART_3_OUTPUT_FOLDER):
         os.makedirs(PART_3_OUTPUT_FOLDER)
+
+    candidate_complexity_functions = {
+        "linear": lambda x: x,
+        "quadratic": lambda x: x**2,
+        "cubic": lambda x: x**3,
+        "exponential": lambda x: 2**x,
+        "logarithm": lambda x: np.log(x),
+    }
+    # part_3.a(
+    #     model=OneNN(),
+    #     dimensions=np.arange(1, 21),
+    #     number_of_trials=100,
+    #     m_test=200,
+    #     candidate_complexity_functions=candidate_complexity_functions,
+    #     figure_save_path=os.path.join(PART_3_OUTPUT_FOLDER, "q1a_one_nn"),
+    # )
     part_3.a(
         model=OneNN(),
-        dimensions=np.arange(1, 11),
-        number_train_points=np.arange(1, 101),
-        number_of_trials=10,
-        m_test=20,
-        figure_save_path=os.path.join(PART_3_OUTPUT_FOLDER, "q1a_one_nn.png"),
+        dimensions=np.arange(1, 21),
+        number_of_trials=100,
+        m_test=200,
[…]

### 2022-12-07 src/models/SSL.py

@@ -1,55 +1,0 @@
-import numpy as np
-
-
-class LaplacianInterpolation:
-    def __init__(self):
-        self.W = None
-
-    def predict(self, W, y):
-        """
-        Inputs:
-
-        W : 3-NN adjacency matrix for the datapoints in X
-        y : set of labels for x_1, ..., x_l
-
-        Output:
-
-        y_hat: predicted labels for y_{l+1}, ... , y_{n}
-
-        Note: we have ordered our graph nodes so the first l datapoints are the
-        labelled datapoints.
-
-        The following expression was given in the paper provided, and hence used in
-        this example for a closed-form solution.
-
-        """
-        s = y.shape[0]
-        D = np.diag(W.sum(0))
-        return np.sign(
-            np.linalg.lstsq(D[s:, s:] - W[s:, s:], W[s:, :s] @ y, rcond=None)[0]
-        )
-
-
-class LaplacianKernelInterpolation:
-    def __init__(self):
-        pass
-
-    def predict(self, W, y):
-
-        """
-        Inputs:
-
-        W : 3-NN adjacency matrix for the datapoints in X
-        y : set of labels for x_1, ..., x_l
-
-        Output:
-
-        y_hat: predicted labels for y_{l+1}, ... , y_{n}
-
-        """
-
-        L = np.diag(W.sum(0)) - W
-        m = y.shape[0]
-        L_pinv = np.linalg.pinv(L)
-        alpha = np.linalg.pinv(L_pinv[:m, :m]) @ y
-        return np.sign(L_pinv[:m, :].T @ alpha)[m:]

### 2022-12-07 src/models/helpers.py

@@ -79,12 +79,12 @@ def ssl_data_sample(y, sample_size):
     return idxs
 
 
-def KNN_adjacency_matrix(X, k):
-    tree = KDTree(X)
-    n = X.shape[0]
-    graph = tree.query(X, k)[1][:, 1:]
-    W = np.zeros((n, n))
+def knn_adjacency_matrix(x, k):
+    tree = KDTree(x)
+    n = x.shape[0]
+    graph = tree.query(x, k)[1][:, 1:]
+    w = np.zeros((n, n))
     for i in range(n):
-        W[i, graph[i, :]] = 1
-        W[graph[i, :], i] = 1
-    return W
+        w[i, graph[i, :]] = 1
+        w[graph[i, :], i] = 1
+    return w

### 2022-12-07 src/models/laplacian_interpolation.py

@@ -1,0 +1,38 @@
+import numpy as np
+
+
+class LaplacianInterpolation:
+    @staticmethod
+    def predict(w, y):
+        """
+        Note: we have ordered our graph nodes so the first l datapoints are the
+        labelled datapoints.
+
+        The following expression was given in the paper provided, and hence used in
+        this example for a closed-form solution.
+
+        :param w: 3-NN adjacency matrix for the datapoints in X
+        :param y: set of labels for x_1, ..., x_l
+        :return: y_hat: predicted labels for y_{l+1}, ... , y_{n}
+        """
+        s = y.shape[0]
+        diagonal = np.diag(w.sum(0))
+        return np.sign(
+            np.linalg.lstsq(diagonal[s:, s:] - w[s:, s:], w[s:, :s] @ y, rcond=None)[0]
+        )
+
+
+class LaplacianKernelInterpolation:
+    @staticmethod
+    def predict(w, y):
+        """
+
+        :param w: 3-NN adjacency matrix for the datapoints in X
+        :param y: set of labels for x_1, ..., x_l
+        :return: y_hat: predicted labels for y_{l+1}, ... , y_{n}
+        """
+        l_matrix = np.diag(w.sum(0)) - w
+        m = y.shape[0]
+        l_matrix_pinv = np.linalg.pinv(l_matrix)
+        alpha = np.linalg.pinv(l_matrix_pinv[:m, :m]) @ y
+        return np.sign(l_matrix_pinv[:m, :].T @ alpha)[m:]

### 2022-12-07 src/models/linear_regression_classifier.py

@@ -1,16 +1,0 @@
-import jax.numpy as jnp
-import numpy as np
-
-from src.models.model import Model
-
-
-class LinearRegressionClassifier(Model):
-    def __init__(self, w=None):
-        self.w: np.ndarray = w
-        super().__init__()
-
-    def fit(self, x: np.ndarray, y: np.ndarray, **kwargs) -> None:
-        self.w = np.linalg.pinv(x) @ y
-
-    def predict(self, x: jnp.ndarray) -> jnp.ndarray:
-        return jnp.sign(x @ self.w)

### 2022-12-07 src/models/model.py

@@ -1,31 +1,0 @@
-from abc import ABC, abstractmethod
-
-import numpy as np
-
-
-class Model(ABC):
-    def __init__(self):
-        pass
-
-    """
-    Abstract model class
-    """
-
-    @abstractmethod
-    def fit(self, x: np.ndarray, y: np.ndarray, **kwargs) -> None:
-        """
-        Fitting model
-        :param x: dataset of shape (number of dimensions, number of examples)
-        :param y: labels of shape (number of examples, 1)
-        :return: None
-        """
-        pass
-
-    @abstractmethod
-    def predict(self, x: np.ndarray) -> np.ndarray:
-        """
-        Prediction of x
-        :param x: dataset of shape (number of dimensions, number of examples)
-        :return: predicted labels of shape (number of examples, 1)
-        """
-        pass

### 2022-12-07 src/models/one_nn.py

@@ -1,22 +1,0 @@
-import numpy as np
-from sklearn.neighbors import KDTree
-
-from src.models.model import Model
-
-
-class OneNN(Model):
-    k = 1
-
-    def __init__(self, tree=None, y=None):
-        self.tree: KDTree = tree
-        self.y: np.ndarray = y
-        super().__init__()
-
-    def fit(self, x: np.ndarray, y: np.ndarray, **kwargs) -> None:
-        self.tree = KDTree(x)
-        self.y = y
-
-    def predict(self, x: np.ndarray) -> np.ndarray:
-        return self.y[self.tree.query(x, k=self.k)[1]].reshape(
-            -1,
-        )

### 2022-12-07 src/models/single_class/linear_regression_classifier.py

@@ -1,0 +1,11 @@
+import jax.numpy as jnp
+import numpy as np
+
+from src.models.single_class.model import Model
+
+
+class LinearRegressionClassifier(Model):
+    @staticmethod
+    def fit_predict(x_train, y_train, x_test, **kwargs):
+        w = np.linalg.pinv(x_train) @ y_train
+        return jnp.sign(x_test @ w)

### 2022-12-07 src/models/single_class/model.py

@@ -1,0 +1,17 @@
+from abc import ABC, abstractmethod
+
+import numpy as np
+
+
+class Model(ABC):
+    def __init__(self):
+        pass
+
+    """
+    Abstract model class
+    """
+
+    @abstractmethod
+    def fit_predict(self, x_train, y_train, x_test, **kwargs):
+        pass
+

### 2022-12-07 src/models/single_class/one_nn.py

@@ -1,0 +1,21 @@
+from sklearn.neighbors import KDTree
+import numpy as np
+
+from src.models.single_class.model import Model
+
+
+class OneNN(Model):
+    @staticmethod
+    def _all_distances(a, b):
+        """
+        a is (N, D)
+        b is (M, D)
+        returns all euclidean norm distances between a and b (N, M)
+
+        """
+        return np.sqrt(((a.T[:, None] - b.T[:, :, None]) ** 2).sum(0)).T
+
+    @staticmethod
+    def fit_predict(x_train, y_train, x_test, **kwargs):
+        idx = np.argmin(OneNN._all_distances(x_test, x_train), axis=1)
+        return y_train[idx]

### 2022-12-07 src/models/single_class/perceptron.py

@@ -3,17 +3,15 @@ from typing import Any, Dict
 import numpy as np
 
 from src.models.kernels import BaseKernel
-from src.models.model import Model
+from src.models.single_class.model import Model
 
 
 class SingleClassPerceptron(Model):
     def __init__(
-        self, kernel: BaseKernel, kernel_kwargs: Dict[str, Any], w=None, x=None
+        self, kernel: BaseKernel, kernel_kwargs: Dict[str, Any],
     ):
         self.kernel = kernel
         self.kernel_kwargs = kernel_kwargs
-        self.x: np.ndarray = x
-        self.w: np.ndarray = w
         super().__init__()
 
     @staticmethod
@@ -42,7 +40,7 @@ class SingleClassPerceptron(Model):
 
         return (y != prediction) * y
 
-    def fit(self, x: np.ndarray, y: np.ndarray, **kwargs) -> None:
+    def fit_predict(self, x_train: np.ndarray, y_train: np.ndarray, x_test: np.ndarray, **kwargs) -> np.ndarray:
         """
         All input matrices will share the first M dimensions representing the different independent experiments
         that we want to train for. N_i will be the size of the ith dimension, and i = 1, 2, ..., M
@@ -58,22 +56,10 @@ class SingleClassPerceptron(Model):
         else:
             number_of_epochs = 1
 
-        self.x = x
-        gram = self.kernel(x, **self.kernel_kwargs)
-
-        self.w = np.zeros(y.shape)
-
+        gram_train = self.kernel(x_train, **self.kernel_kwargs)
+        w = np.zeros(y_train.shape)
         for _ in range(number_of_epochs):
             for i in range(1, len(self.w)):
-                self.w[i] += self._compute_update(w=self.w, y=y[i], gram=gram[:, i])
-
-    def predict(self, x: np.ndarray) -> np.ndarray:
-        """
-        perceptron prediction
-        :param x: design matrix
-                  (number_of_points, number_of_dimensions)
-        :return: predictions for x
-                 (number_of_points, number_classes)
-        """
-        gram = self.kernel(self.x, x, **self.kernel_kwargs)
-        return self._predict(self.w, gram)
+                w[i] += self._compute_update(w=self.w, y=y_train[i], gram=gram_train[:, i])
+        gram_test = self.kernel(x_train, x_test, **self.kernel_kwargs)
+        return self._predict(w, gram_test)

### 2022-12-07 src/models/single_class/winnow.py

@@ -1,13 +1,9 @@
 import numpy as np
 
-from src.models.model import Model
+from src.models.single_class.model import Model
 
 
 class Winnow(Model):
-    def __init__(self, w=None):
-        self.w: np.ndarray = w
-        super().__init__()
-
     @staticmethod
     def _preprocess(y):
         y[y == -1] = 0
@@ -51,7 +47,7 @@ class Winnow(Model):
             w, 2 ** np.multiply((y - prediction)[..., None], x).astype(float)
         )
 
-    def fit(self, x: np.ndarray, y: np.ndarray, **kwargs) -> None:
+    def fit_predict(self, x_train, y_train, x_test, **kwargs):
         """
         Vectorised winnow training by training multiple trials, etc. in parallel
         The winnow is trained one data point at a time, the new weights depend on the weights of the previous
@@ -72,18 +68,9 @@ class Winnow(Model):
         else:
             number_of_epochs = 1
 
-        self.w = np.ones(x.shape[1])
-        y = self._preprocess(y)
+        w = np.ones(x_train.shape[1])
+        y_train = self._preprocess(y_train)
         for _ in range(number_of_epochs):
-            for i in range(1, x.shape[0]):
-                self.w = self._compute_update(self.w, y=y[i], x=x[i, :])
-
-    def predict(self, x: np.ndarray) -> np.ndarray:
-        """
-        winnow prediction
-        :param x: design matrix
-                  (number_points, number_of_dimensions)
-        :return: predictions for test points
-                 (number_points)
-        """
-        return self._postprocess(self._predict(self.w, x))
+            for i in range(1, x_train.shape[0]):
+                w = self._compute_update(w, y=y_train[i], x=x_train[i, :])
+        return self._postprocess(self._predict(w, x_test))

### 2022-12-07 src/solutions/part_1.py

@@ -7,7 +7,7 @@ import numpy as np
 import pandas as pd
 from jax import vmap
 
-from src.models import perceptron
+from src.models.multi_class import perceptron
 from src.models.helpers import TrainTestData, make_folds
 from src.models.kernels import BaseKernel
 

### 2022-12-07 src/solutions/part_2.py

@@ -5,8 +5,8 @@ import matplotlib.pyplot as plt
 import numpy as np
 import pandas as pd
 
-from src.models.helpers import KNN_adjacency_matrix, ssl_data_sample
-from src.models.SSL import LaplacianInterpolation, LaplacianKernelInterpolation
+from src.models.helpers import knn_adjacency_matrix, ssl_data_sample
+from src.models.laplacian_interpolation import LaplacianInterpolation, LaplacianKernelInterpolation
 
 outpath = os.path.join("outputs", "part2")
 DATAPATH50 = os.path.join("data", "dtrain13_50.dat")
@@ -23,26 +23,26 @@ GRAPH_LABEL_DIAGRAM_PATH = os.path.join(outpath, "graph_label_diagram.png")
 def experimental_report(
     model,
     datasets,
-    n_iters,
+    number_iterations,
 ):
     sample_range = [1, 2, 4, 8, 16]
-    accuracy = np.zeros((4, 5, n_iters))
+    accuracy = np.zeros((4, 5, number_iterations))
 
-    for iter in range(n_iters):
+    for iteration in range(number_iterations):
         for i, dataset in enumerate(datasets):
             y = dataset[:, 0]
-            W = KNN_adjacency_matrix(dataset[:, 1:], k=3)
+            w = knn_adjacency_matrix(dataset[:, 1:], k=3)
             for j, sample_size in enumerate(sample_range):
                 sample = ssl_data_sample(y, sample_size)
                 y_train, y_test = (
                     y[sample[: 2 * sample_size]],
                     y[sample[2 * sample_size :]],
                 )
-                accuracy[i, j, iter] = (
-                    model.predict(W[sample, :][:, sample], y_train) == y_test
-                ).mean()
+                accuracy[i, j, iteration] = np.mean(
+                    model.predict(w[sample, :][:, sample], y_train) == y_test
+                )
                 if i == 0:
-                    graph_edge_label_diagram(W, y, GRAPH_LABEL_DIAGRAM_PATH)
+                    graph_edge_label_diagram(w, y, GRAPH_LABEL_DIAGRAM_PATH)
     return accuracy.mean(-1), accuracy.std(-1)
 
 
@@ -68,14 +68,13 @@ def edge_colour(y1, y2):
         return 3.0
 
 
-def graph_edge_label_diagram(W, y, outpath):
[…]

### 2022-12-07 src/solutions/part_3.py

@@ -1,7 +1,9 @@
 import matplotlib.pyplot as plt
 import numpy as np
 
-from src.models.model import Model
+from tqdm import tqdm
+from src.models.single_class.model import Model
+from typing import Dict, Callable
 
 
 def generate_data(m: int, n: int):
@@ -19,36 +21,58 @@ def generate_data(m: int, n: int):
 def a(
     model: Model,
     dimensions: np.ndarray,
-    number_train_points: np.ndarray,
     number_of_trials: int,
     m_test: int,
     figure_save_path: str,
+    candidate_complexity_functions: Dict[str, Callable],
     generalisation_error: float = 0.1,
 ):
     number_of_dimensions = len(dimensions)
+
+    # initialise as maximum training points such that in the event we do not find
+    # an error rate below the generalisation error, we just take the maximum number
+    # of training points, this will be a lower bound on the required number of training
+    # points and our estimate will be biased slightly lower than the actual.
     train_points_for_generalisation_error = (
         np.ones((number_of_dimensions, number_of_trials)) * np.nan
     )
 
-    for i, n in enumerate(dimensions):
-        for j in range(number_of_trials):
-            for k, m in enumerate(number_train_points):
+    for i, n in tqdm(enumerate(dimensions)):
+        for j in tqdm(range(number_of_trials)):
+            x_test, y_test = generate_data(m_test, n)
+            error_rate = 1
+            m = 0
+            while error_rate > generalisation_error:
+                m += 1
                 x_train, y_train = generate_data(m, n)
-                model.fit(x_train, y_train)
-
-                x_test, y_test = generate_data(m_test, n)
-                y_predicted = model.predict(x_test)
+                y_predicted = model.fit_predict(x_train, y_train, x_test)
+                assert y_predicted.shape == y_test.shape
                 error_rate = np.mean(y_predicted != y_test)
-                if error_rate < generalisation_error:
-                    # update mean and squared mean vectors with nansum to ensure that the resulting vector indicates
-                    # when the generalisation error requirement is reached
-                    train_points_for_generalisation_error[i, j] = m
-                    break
+            train_points_for_generalisation_error[i, j] = m
     plt.errorbar(
         dimensions,
-        np.nanmean(train_points_for_generalisation_error, axis=1),
-        yerr=np.nanstd(train_points_for_generalisation_error, axis=1),
[…]

### 2022-12-08 main.py
update part 3 plots with numpy arrays stored for future use

@@ -3,10 +3,14 @@ import os
 import jax
 import numpy as np
 
-from src.constants import (
-    OUTPUTS_FOLDER,
+from src.constants import OUTPUTS_FOLDER
+from src.models.kernels import PolynomialKernel
+from src.models.single_class.linear_regression_classifier import (
+    LinearRegressionClassifier,
 )
 from src.models.single_class.one_nn import OneNN
+from src.models.single_class.perceptron import Perceptron
+from src.models.single_class.winnow import Winnow
 from src.solutions import part_3
 
 if __name__ == "__main__":
@@ -94,22 +98,15 @@ if __name__ == "__main__":
     PART_3_OUTPUT_FOLDER = os.path.join(OUTPUTS_FOLDER, "part3")
     if not os.path.exists(PART_3_OUTPUT_FOLDER):
         os.makedirs(PART_3_OUTPUT_FOLDER)
+    LOAD_PREVIOUS_RESULTS = False
 
     candidate_complexity_functions = {
         "linear": lambda x: x,
         "quadratic": lambda x: x**2,
         "cubic": lambda x: x**3,
-        "exponential": lambda x: 2**x,
+        "exponential": lambda x: np.exp(x),
         "logarithm": lambda x: np.log(x),
     }
-    # part_3.a(
-    #     model=OneNN(),
-    #     dimensions=np.arange(1, 21),
-    #     number_of_trials=100,
-    #     m_test=200,
-    #     candidate_complexity_functions=candidate_complexity_functions,
-    #     figure_save_path=os.path.join(PART_3_OUTPUT_FOLDER, "q1a_one_nn"),
-    # )
     part_3.a(
         model=OneNN(),
         dimensions=np.arange(1, 21),
@@ -117,33 +114,32 @@ if __name__ == "__main__":
         m_test=200,
         candidate_complexity_functions=candidate_complexity_functions,
         figure_save_path=os.path.join(PART_3_OUTPUT_FOLDER, "q1a_one_nn"),
+        load_previous_results=LOAD_PREVIOUS_RESULTS,
     )
-    # part_3.a(
-    #     model=Winnow(),
-    #     dimensions=np.arange(1, 21),
-    #     number_train_points=np.arange(1, 101),
-    #     number_of_trials=10,
-    #     m_test=20,
-    #     candidate_complexity_functions=candidate_complexity_functions,
[…]

### 2022-12-08 src/models/single_class/one_nn.py

@@ -1,5 +1,4 @@
-import numpy as np
-from sklearn.neighbors import KDTree
+import jax.numpy as jnp
 
 from src.models.single_class.model import Model
 
@@ -13,9 +12,9 @@ class OneNN(Model):
         returns all euclidean norm distances between a and b (N, M)
 
         """
-        return np.sqrt(((a.T[:, None] - b.T[:, :, None]) ** 2).sum(0)).T
+        return jnp.sqrt(((a.T[:, None] - b.T[:, :, None]) ** 2).sum(0)).T
 
     @staticmethod
     def fit_predict(x_train, y_train, x_test, **kwargs):
-        idx = np.argmin(OneNN._all_distances(x_test, x_train), axis=1)
+        idx = jnp.argmin(OneNN._all_distances(x_test, x_train), axis=1)
         return y_train[idx]

### 2022-12-08 src/models/single_class/perceptron.py

@@ -6,7 +6,7 @@ from src.models.kernels import BaseKernel
 from src.models.single_class.model import Model
 
 
-class SingleClassPerceptron(Model):
+class Perceptron(Model):
     def __init__(
         self,
         kernel: BaseKernel,
@@ -38,7 +38,7 @@ class SingleClassPerceptron(Model):
         :param y: matrix of a single response
         :return: weight update for the weights pertaining to the single input
         """
-        prediction = SingleClassPerceptron._predict(w, gram)
+        prediction = Perceptron._predict(w, gram)
 
         return (y != prediction) * y
 
@@ -63,9 +63,7 @@ class SingleClassPerceptron(Model):
         gram_train = self.kernel(x_train, **self.kernel_kwargs)
         w = np.zeros(y_train.shape)
         for _ in range(number_of_epochs):
-            for i in range(1, len(self.w)):
-                w[i] += self._compute_update(
-                    w=self.w, y=y_train[i], gram=gram_train[:, i]
-                )
+            for i in range(1, len(w)):
+                w[i] += self._compute_update(w=w, y=y_train[i], gram=gram_train[:, i])
         gram_test = self.kernel(x_train, x_test, **self.kernel_kwargs)
         return self._predict(w, gram_test)

### 2022-12-08 src/solutions/part_3.py

@@ -1,3 +1,4 @@
+import os
 from typing import Callable, Dict
 
 import matplotlib.pyplot as plt
@@ -19,14 +20,12 @@ def generate_data(m: int, n: int):
     return x, y
 
 
-def a(
+def run_experiment(
     model: Model,
     dimensions: np.ndarray,
     number_of_trials: int,
     m_test: int,
-    figure_save_path: str,
-    candidate_complexity_functions: Dict[str, Callable],
-    generalisation_error: float = 0.1,
+    generalisation_error: float,
 ):
     number_of_dimensions = len(dimensions)
 
@@ -39,24 +38,65 @@ def a(
     )
 
     for i, n in tqdm(enumerate(dimensions)):
-        for j in tqdm(range(number_of_trials)):
+        for j in range(number_of_trials):
             x_test, y_test = generate_data(m_test, n)
             error_rate = 1
             m = 0
+            x_train, y_train = generate_data(1, n)
             while error_rate > generalisation_error:
                 m += 1
-                x_train, y_train = generate_data(m, n)
                 y_predicted = model.fit_predict(x_train, y_train, x_test)
                 assert y_predicted.shape == y_test.shape
                 error_rate = np.mean(y_predicted != y_test)
+
+                x_train_new, y_train_new = generate_data(1, n)
+                x_train = np.concatenate((x_train, x_train_new))
+                y_train = np.concatenate((y_train, y_train_new))
+
             train_points_for_generalisation_error[i, j] = m
+    return train_points_for_generalisation_error
+
+
+def a(
+    model: Model,
+    dimensions: np.ndarray,
+    number_of_trials: int,
+    m_test: int,
+    figure_save_path: str,
+    candidate_complexity_functions: Dict[str, Callable],
+    generalisation_error: float = 0.1,
+    load_previous_results: bool = True,
+):
+    if load_previous_results and os.path.isfile(figure_save_path + ".npz"):
+        loaded_arrays = np.load(figure_save_path + ".npz")
+        train_points_for_generalisation_error = loaded_arrays[
+            "train_points_for_generalisation_error"
+        ]
+        dimensions = loaded_arrays["dimensions"]
+        generalisation_error = loaded_arrays["generalisation_error"].item()
+    else:
+        train_points_for_generalisation_error = run_experiment(
+            model,
+            dimensions,
+            number_of_trials,
+            m_test,
+            generalisation_error,
+        )
[…]

### 2022-12-09 submission.tex
update figures and lin reg classifier
challenge question completed

@@
 \subsection{Kernel Perceptron}
+\subsubsection{Experimental Results}
+
+\begin{itemize}
+    \item[1.] Basic Results:
+
+    \includegraphics{outputs/part1/q1.png}
+
+    \item[2.] Cross Validation Results:
+
+    \includegraphics{outputs/part1/q2.png}
+
+    \item[3.] Confusion Matrix:
+
+    \includegraphics{outputs/part1/q3_confusion.png}
+\newpage
+    \item[4.] Hardest to predict images:
+
+    \includegraphics{outputs/part1/q4.png}
+    \newpage
+    \item[5.] Basic Results:
+
+    \includegraphics{outputs/part1/q5_1.png}
+
+    Cross Validation Results:
+
+    \includegraphics{outputs/part1/q5_2.png}
+\end{itemize}
+\subsubsection{Discussions}
+    Choice of Parameters that weren't cross validated
+
+    Generalisation to k-classifiers
+
+    Kernel Comparison
+
+    Kernel Perceptron Implementation
+
 \newpage
@@
     \item[D.]\\
-    We note that since for any $X_{t}$, $y_{t} = X_{1,t}$, we have the following
+    We note that since for any $X_{t}$ , $y_{t} = X_{1,t}$ , we have the following
      expression representing the linear separability of our dataset:\\
@@
 
+     \item[E.]\\
+     From our experimental observations we may expect the sample complexity of 1-NN
+     to be lower bounded by some exponential function. We formalise this in the
+     following proposition:\\
+
+    \textbf{Proposition:}\\
+
+    Following the data-generating distribution described above, we have that our sample complexity given by:\\
+
+    $m(n) = \Omega (n)$ \\
+    \textbf{Proof:}\\
+
+    Suppose we sample a training set $S = \{(x_{1},y_{1}), \dots, (x_{n},y_{n})\} $ uniformly from the set $\{-1,1\}^{n}$, with associated labels
+    defined by the rule $y | x = x_{1}$, and use this training set for inference on an
+     arbitrary test point $(x,x_{1})$, sampled uniformly from the same set.
+    \\
+    We note the following observation:\\
+
+    \textbf{Obs:}\\
+    if $x \in S$, then $\mathcal{A}_{S}(x)) = y$, where y is the true label for x. \\
+
+    To justify this, observe that our dataset represents a realiseable learning problem,
+    and as such, if $(x,y), (x \prime,y \prime)$ are datapoints sampled from our distribution,
+    $x = x \prime \implies y = y \prime $. Trivially, x is the 1-nearest neighbour to itself,
+    so the algorithm makes a correct prediction for any datapoint present in our training set.\\
+
+    Hence, $\mathcal{A}_{S}$ makes an error on x $\implies x \notin S$.
+
+    Hence, the set of all training sets that make an error on x is contained in the set of all
+    training sets not containing x. \\
+
+    Hence, for a given x, $P_{S}(\mathcal{A}_{S}(x) \ne y) \le P_{S}(x \notin S)$.\\
+
+    Since S is a collection of points sampled iid from our data generating distribution, \\
+    $P_{S}(x \notin S) = \prod_{i=1}^{m}P(x_{i} \ne x) = \prod_{i}(1 - P(x_{i} = x)) = (1 - 2^{-n})^{m}$\\
+
+    We note that our choice of x was arbitrary, and since we sampled x uniformly, we arrive at the 
+    following generalisation error bound:\\
+
+    $\mathbb{E}_{S \sim \mathcal{D}^{m}, x \sim \mathcal{D}}[\mathcal{L}_{S}(x)] \le (1 - 2^{-n})^{m} $\\
+    Using the identity $1-x \le e^{-x}$ provided frequently in the notes, we simplify this bound to give:
+    \\
+    \\
+
+    $\mathbb{E}_{S \sim \mathcal{D}^{m}, x \sim \mathcal{D}}[\mathcal{L}_{S}(x)] \le exp(-2^{n}m)$
+    \\
+    Suppose we seek m such that our generalisation error is less than some fixed $\epsilon$. \\
+    \\
+    Hence we require $\mathbb{E}_{S \sim \mathcal{D}^{m}, x \sim \mathcal{D}}[\mathcal{L}_{S}(x)] \le exp(-2^{n}m) \le \epsilon$\\
+    \\
+    $\implies -m2^{-n} \le log(\epsilon)$\\
+
+    Hence, $m \ge -log(\epsilon)2^{n} = log(\frac{1}{\epsilon}) 2^{n}$\\
+
+    $\implies m = \Omega(2^{n})$\\
+    $\square$
 \end{itemize}

### 2022-12-10 main.py
update part 3 figures

@@ -2,20 +2,36 @@ import os
 
 import jax
 import numpy as np
+import pandas as pd
+from scipy.optimize import curve_fit
 
-from src.constants import OUTPUTS_FOLDER
-from src.models.kernels import PolynomialKernel
+from src.constants import (
+    OUTPUTS_FOLDER,
+    PART_1_DATA_SET_PATH,
+    PART_1_MINI_TRAIN_SET_PATH,
+    PART_1_MINI_TEST_SET_PATH,
+)
+from src.models.kernels import PolynomialKernel, GaussianKernel
 from src.models.single_class.linear_regression_classifier import (
     LinearRegressionClassifier,
 )
 from src.models.single_class.one_nn import OneNN
 from src.models.single_class.perceptron import Perceptron
 from src.models.single_class.winnow import Winnow
-from src.solutions import part_3
+from src.solutions import part_1, part_3
+from src.models.helpers import one_hot_encode, split_train_test_data, TrainTestData
+
+
+def part_1_preprocess(data):
+    x_data, labels = data[:, 1:], data[:, 0]
+    # shift so that our labels start at zero
+    shifted_labels = labels - np.min(labels)
+    y_data = one_hot_encode(shifted_labels)
+    return x_data, y_data, labels
+
 
 if __name__ == "__main__":
     jax.config.update("jax_platform_name", "cpu")
-    jax.config.update("jax_enable_x64", True)
 
     if not os.path.exists(OUTPUTS_FOLDER):
         os.makedirs(OUTPUTS_FOLDER)
@@ -25,34 +41,49 @@ if __name__ == "__main__":
     # if not os.path.exists(PART_1_OUTPUT_FOLDER):
     #     os.makedirs(PART_1_OUTPUT_FOLDER)
     #
-    # data = np.genfromtxt(PART_1_DATA_SET_PATH)
-    # x, labels = data[:, 1:], data[:, 0]
-    # # shift so that our labels start at zero
-    # shifted_labels = labels - jnp.min(labels)
-    # y = one_hot_encode(shifted_labels)
+    # raw_data = np.genfromtxt(PART_1_DATA_SET_PATH)
+    # x, y, labels = part_1_preprocess(raw_data)
+    #
+    # raw_data_mini_train = np.genfromtxt(PART_1_MINI_TRAIN_SET_PATH)
+    # x_mini_train, y_mini_train, _ = part_1_preprocess(raw_data_mini_train)
[…]

### 2022-12-10 src/models/single_class/model.py

@@ -12,5 +12,7 @@ class Model(ABC):
     """
 
     @abstractmethod
-    def fit_predict(self, x_train, y_train, x_test, **kwargs):
+    def fit_predict(
+        self, x_train: np.ndarray, y_train: np.ndarray, x_test: np.ndarray, **kwargs
+    ) -> np.ndarray:
         pass

### 2022-12-10 src/solutions/part_3.py

@@ -63,7 +63,7 @@ def a(
     number_of_trials: int,
     m_test: int,
     figure_save_path: str,
-    candidate_complexity_functions: Dict[str, Callable],
+    candidate_complexity_functions: Dict[str, Dict[str, Callable]],
     generalisation_error: float = 0.1,
     load_previous_results: bool = True,
 ):
@@ -105,14 +105,28 @@ def a(
     fig, ax = plt.subplots(1, len(candidate_complexity_functions))
     fig.set_size_inches(len(candidate_complexity_functions) * 5, 6)
     for i, function_name in enumerate(candidate_complexity_functions.keys()):
-        f = candidate_complexity_functions[function_name]
-        ax[i].plot(
+        fit_coefficients = candidate_complexity_functions[function_name]["fit"](
+            dimensions, np.mean(train_points_for_generalisation_error, axis=1)
+        )
+        fit_function = lambda x: candidate_complexity_functions[function_name]["f"](
+            x, fit_coefficients
+        )
+        ax[i].errorbar(
             dimensions,
-            np.divide(
-                f(dimensions), np.mean(train_points_for_generalisation_error, axis=1)
-            ),
+            np.mean(train_points_for_generalisation_error, axis=1),
+            yerr=np.std(train_points_for_generalisation_error, axis=1),
+            capsize=2,
+            color=(0.8, 0.8, 0.8),
+            zorder=-1,
+            label="Sample Complexity",
+        )
+        ax[i].plot(
+            dimensions, fit_function(dimensions), zorder=1, label=f"{function_name} Fit"
         )
         ax[i].title.set_text(f"{function_name} Comparison")
+        ax[i].legend()
+        ax[i].set_xlabel("n")
+        ax[i].set_ylabel("m")
     plt.suptitle(
         f"{type(model).__name__}: Complexity Function Comparison ({generalisation_error=})"
     )

### 2022-12-10 main.py
force exponential to be an increasing curve

@@ -207,33 +207,24 @@ if __name__ == "__main__":
             "fit": lambda x, y: np.polyfit(x, y, 2),
             "f": lambda x, coeff: np.poly1d(coeff)(x),
         },
-        # "logarithm": {
-        #     "fit": lambda x, y: np.polyfit(np.log(x), y, 1),
-        #     "f": lambda x, coeff: np.poly1d(coeff)(np.log(x)),
-        # },
         "logarithm": {
             "fit": lambda x, y: curve_fit(
-                lambda t, a, b, c: a * np.log(b * t) + c, x, y
+                lambda t, a, b, c: np.abs(a) * np.log(b * t) + c, x, y
             )[0],
-            "f": lambda x, coeff: coeff[0] * np.log(coeff[1] * x) + coeff[2],
+            "f": lambda x, coeff: np.abs(coeff[0]) * np.log(coeff[1] * x) + coeff[2],
         },
         "exponential": {
             "fit": lambda x, y: curve_fit(
-                lambda t, a, b, c: a * np.exp(b * t) + c, x, y
+                lambda t, a, b, c: np.abs(a) * np.exp(b * t) + c, x, y
             )[0],
-            "f": lambda x, coeff: coeff[0] * np.exp(coeff[1] * x) + coeff[2],
+            "f": lambda x, coeff: np.abs(coeff[0]) * np.exp(coeff[1] * x) + coeff[2],
         },
-        "2^n": {
-            "fit": lambda x, y: curve_fit(
-                lambda t, a, b, c: a * (2 ** (b * t)) + c, x, y
-            )[0],
-            "f": lambda x, coeff: coeff[0] * (2 ** (coeff[1] * x)) + coeff[2],
-        },
-        # "linear": lambda x: x,
-        # "quadratic": lambda x: x**2,
-        # "cubic": lambda x: x**3,
-        # "exponential": lambda x: x**5,
-        # "logarithm": lambda x: np.log(x),
+        # "2^n": {
+        #     "fit": lambda x, y: curve_fit(
+        #         lambda t, a, b, c: a * (2 ** (b * t)) + c, x, y
+        #     )[0],
+        #     "f": lambda x, coeff: coeff[0] * (2 ** (coeff[1] * x)) + coeff[2],
+        # },
     }
     part_3.a(
         model=OneNN(),

### 2022-12-10 main.py
update part 1 outputs

@@ -5,21 +5,20 @@ import numpy as np
 import pandas as pd
 from scipy.optimize import curve_fit
 
-from src.constants import (
-    OUTPUTS_FOLDER,
-    PART_1_DATA_SET_PATH,
-    PART_1_MINI_TRAIN_SET_PATH,
-    PART_1_MINI_TEST_SET_PATH,
-)
-from src.models.kernels import PolynomialKernel, GaussianKernel
-from src.models.single_class.linear_regression_classifier import (
-    LinearRegressionClassifier,
-)
+from src.constants import (DEFAULT_SEED, OUTPUTS_FOLDER, PART_1_DATA_SET_PATH,
+                           PART_1_MINI_TEST_SET_PATH,
+                           PART_1_MINI_TRAIN_SET_PATH)
+from src.models.helpers import (TrainTestData, one_hot_encode,
+                                split_train_test_data)
+from src.models.kernels import GaussianKernel, PolynomialKernel
+from src.models.single_class.linear_regression_classifier import \
+    LinearRegressionClassifier
 from src.models.single_class.one_nn import OneNN
 from src.models.single_class.perceptron import Perceptron
 from src.models.single_class.winnow import Winnow
 from src.solutions import part_1, part_3
-from src.models.helpers import one_hot_encode, split_train_test_data, TrainTestData
+
+np.random.seed(DEFAULT_SEED)
 
 
 def part_1_preprocess(data):
@@ -36,155 +35,155 @@ if __name__ == "__main__":
     if not os.path.exists(OUTPUTS_FOLDER):
         os.makedirs(OUTPUTS_FOLDER)
 
-    # # Question 1
-    # PART_1_OUTPUT_FOLDER = os.path.join(OUTPUTS_FOLDER, "part1")
-    # if not os.path.exists(PART_1_OUTPUT_FOLDER):
-    #     os.makedirs(PART_1_OUTPUT_FOLDER)
-    #
-    # raw_data = np.genfromtxt(PART_1_DATA_SET_PATH)
-    # x, y, labels = part_1_preprocess(raw_data)
-    #
-    # raw_data_mini_train = np.genfromtxt(PART_1_MINI_TRAIN_SET_PATH)
-    # x_mini_train, y_mini_train, _ = part_1_preprocess(raw_data_mini_train)
-    # raw_data_mini_test = np.genfromtxt(PART_1_MINI_TEST_SET_PATH)
-    # x_mini_test, y_mini_test, _ = part_1_preprocess(raw_data_mini_test)
[…]

### 2022-12-10 src/models/kernels.py

@@ -5,26 +5,29 @@ from typing import Any, Dict, Tuple
 
 import jax.numpy as jnp
 import numpy as np
-from jax import jit, tree_util, vmap
+from jax import vmap
 
 
 class BaseKernel(ABC):
     """
-    Abstact Kernel class
+    Abstract Kernel class
     """
 
+    @staticmethod
     @abstractmethod
-    @jit
-    def _kernel(self, x: np.ndarray, y: np.ndarray, **kwargs) -> float:
-        """
-        Kernel implementation for single features
+    def _pre_kernel(x: np.ndarray, y: np.ndarray) -> np.ndarray:
+        pass
 
-        :param x: ndarray of shape (n_dimensions, )
-        :param y: ndarray of shape (n_dimensions, )
-        :return: evaluation of kernel
-        """
+    @staticmethod
+    @abstractmethod
+    def post_gram(pre_gram: np.ndarray, **kwargs) -> np.ndarray:
+        pass
 
-    @jit
+    @staticmethod
+    @abstractmethod
+    def _kernel(self, x: np.ndarray, y: np.ndarray, **kwargs) -> np.ndarray:
+        pass
+
     def __call__(self, x: np.ndarray, y: np.ndarray = None, **kwargs) -> np.ndarray:
         """
         Kernel evaluation for arbitrary number of x features and y features
@@ -46,36 +49,36 @@ class BaseKernel(ABC):
             x.shape[1] == y.shape[1]
         ), f"Dimension Mismatch: {x.shape[1]=} != {y.shape[1]=}"
 
-        return vmap(
-            lambda x_i: vmap(
-                lambda y_i: self._kernel(x_i, y_i, **kwargs),
-            )(y),
-        )(x)
+        gram = np.zeros((x.shape[0], y.shape[0]))
+        for i in range(x.shape[0]):
+            gram[i, :] = vmap(
+                lambda y_i: self._kernel(x[i, :], y_i, **kwargs),
+            )(y)
+        return gram
 
-    @abstractmethod
-    def tree_flatten(self) -> Tuple[Tuple, Dict[str, Any]]:
-        """
-        To have JIT-compiled class methods by registering the type as a custom PyTree object.
-        As referenced in:
-        https://jax.readthedocs.io/en/latest/faq.html#strategy-3-making-customclass-a-pytree
+    def pre_gram(self, x: np.ndarray, y: np.ndarray = None) -> np.ndarray:
[…]

### 2022-12-10 src/models/multi_class/perceptron.py

@@ -5,43 +5,58 @@ import numpy as np
 from jax import jit
 
 
-def _predict(w: np.ndarray, gram: np.ndarray) -> jnp.ndarray:
+def predict(w: np.ndarray, gram: np.ndarray) -> jnp.ndarray:
     """
     prediction for a single data point (across all experiments)
     :param w: weight matrix
-              (number_parameters, N_1,...,N_M, number_training_points, number_classes)
+              (N_1,...,N_M, number_training_points, number_classes)
     :param gram: precomputed gram matrix for a single input vs all training points (across all experiments)
-                 (number_parameters, N_1,...,N_M, number_training_points)
-    :return: a prediction for the single input (number_parameters, N_1,...,N_M, number_classes)
+                 (N_1,...,N_M, number_training_points, number_test_points)
+    :return: a prediction for the single input (N_1,...,N_M, number_classes)
     """
-    return jnp.sum(jnp.multiply(w, gram[..., None]), axis=-2)
+    # return jnp.sum(jnp.multiply(w, gram[..., None]), axis=-2)
+    return gram.T @ w
 
 
 def _compute_update(w: np.ndarray, y: np.ndarray, gram: np.ndarray) -> np.ndarray:
     """
     compute weight update for a single data point (across all experiments)
     :param w: weight matrix
-              (number_parameters, N_1,...,N_M, number_training_points, number_classes)
+              (N_1,...,N_M, number_training_points, number_classes)
     :param gram: precomputed gram matrix for a single input vs all training points (across all experiments)
-                 (number_parameters, N_1,...,N_M, number_training_points)
+                 (N_1,...,N_M, number_training_points, 1)
     :param y: matrix of a single response (across all experiments)
               (N_1,...,N_M, number_classes)
     :return: weight update for the weights pertaining to the single input (N_1,...,N_M, number_classes)
     """
-    prediction = _predict(w, gram)
-
-    # negative if prediction was incorrect across all parameters
-    correct_prediction_indicator = jnp.multiply(y[None, ...], prediction)
-
-    # zero if prediction was incorrect
-    clipped_correct_prediction_indicator = correct_prediction_indicator.clip(0, 1)
-
-    # mask weights to update
-    update_mask = ~clipped_correct_prediction_indicator.astype(bool)
-    return jnp.multiply(y[None, ...], update_mask)
+    prediction = predict(w, gram)
[…]

### 2022-12-10 src/solutions/part_1.py

@@ -5,7 +5,7 @@ import dataframe_image as dfi
 import matplotlib.pyplot as plt
 import numpy as np
 import pandas as pd
-from jax import vmap
+from tqdm import tqdm
 
 from src.models.helpers import TrainTestData, make_folds
 from src.models.kernels import BaseKernel
@@ -34,65 +34,65 @@ class Performance:
         return df
 
 
+def _build_confusion(confusion_matrix, x_idx, y_idx):
+    if confusion_matrix.ndim > 2:
+        for i in range(confusion_matrix.shape[0]):
+            confusion_matrix[i, ...] = _build_confusion(
+                confusion_matrix[i, ...],
+                x_idx[i, ...],
+                y_idx[i, ...],
+            )
+    else:
+        np.add.at(confusion_matrix, (x_idx, y_idx), 1)
+    return confusion_matrix
+
+
 def _analyse_prediction(actuals, predictions) -> Tuple[np.ndarray, np.ndarray]:
     """
 
     :param actuals: (N_1,...,N_M, number_of_test_points, number_classes)
-    :param predictions: (number_parameters, N_1,...,N_M, number_of_test_points, number_classes)
-    :return: comparison of labels (number_parameters, N_1,...,N_M, number_of_test_points)
+    :param predictions: (N_1,...,N_M, number_of_test_points, number_classes)
+    :return: comparison of labels (N_1,...,N_M, number_of_test_points)
              and
-             confusion matrix
+             confusion matrix (N_1,...,N_M, number_classes, number_classes)
     """
-    number_of_parameters = predictions.shape[0]
     number_of_classes = predictions.shape[-1]
     actual_classes = np.argmax(actuals, axis=-1)
     prediction_classes = np.argmax(predictions, axis=-1)
 
     confusion_matrix = np.zeros(
-        (number_of_parameters, number_of_classes, number_of_classes)
+        list(actuals.shape[:-2]) + [number_of_classes, number_of_classes]
     )
-    for i in range(number_of_parameters):
-        np.add.at(
-            confusion_matrix[i, ...], (actual_classes, prediction_classes[i, ...]), 1
-        )
-    return actual_classes[None, ...] == prediction_classes, confusion_matrix
+    confusion_matrix = _build_confusion(
+        confusion_matrix, actual_classes, prediction_classes
+    )
+    return actual_classes == prediction_classes, confusion_matrix
 
 
 def _train_and_test(
[…]

### 2022-12-10 main.py
update outputs

@@ -185,11 +185,11 @@ if __name__ == "__main__":
         use_default_update_method=False,
     )
 
-    # # Question 2
-    # PART_2_OUTPUT_FOLDER = os.path.join(OUTPUTS_FOLDER, "part2")
-    # if not os.path.exists(PART_2_OUTPUT_FOLDER):
-    #     os.makedirs(PART_2_OUTPUT_FOLDER)
-    # q2()
+    # Question 2
+    PART_2_OUTPUT_FOLDER = os.path.join(OUTPUTS_FOLDER, "part2")
+    if not os.path.exists(PART_2_OUTPUT_FOLDER):
+        os.makedirs(PART_2_OUTPUT_FOLDER)
+    q2()
 
     # Question 3
     PART_3_OUTPUT_FOLDER = os.path.join(OUTPUTS_FOLDER, "part3")

### 2022-12-11 submission.tex
update pdf

@@
 \usepackage{luacode}
+\documentclass{article}
+
+\usepackage{algorithm}
+\usepackage{algpseudocode}
 \setlength{\droptitle}{-6em}
@@
 \begin{itemize}
-    \item[1.] Basic Results:
+    \item[1.] To generalise the kernel perceptron to $K$ classes:
+    \begin{algorithm}
+    \caption{An training algorithm for multi-class kernel perceptron}\label{alg:cap}
+    \begin{algorithmic}
+    \For{$k\in\{1, 2, ..., K\}}$ \Comment Initialise weights for first training example
 
-    \includegraphics{outputs/part1/q1.png}
+    \EndFor
+
+    \For{$i\in\{1, 2, ..., M\}$}: \Comment Number of Epochs
+        \For{$j\in\{2, ..., N\}}$ \Comment Number of training points
+            \For{$k\in\{1, 2, ..., K\}}$ \Comment Number of classes
+                \State $\hat{y}_k^{i, j} \gets  \sum_{i'=1}^{i-1} \sum_{j'=1}^{j-1} ( w^{i, j}_k \cdot  k(\textbf{x}_{j'}, \textbf{x}_j)} )$ \Comment{Prediction for class $k$ with kernel $k(\cdot, \cdot)$}
+                \If{$sign(\hat{y}_k^{i, j}) \neq sign(y_k^{i, j})$} \Comment Compare predicted $\hat{y}_k^{i, j}$ and actual $y_k^{i, j})$
+                    \State $w^{i, j}_{k} \gets y_k^{i, j}$
+                \Else
+                    \State $w^{i, j}_{k} \gets 0$
+                \EndIf
+            \EndFor
+        \EndFor
+    \EndFor
+    \end{algorithmic}
+    \end{algorithm}
+
+    The number of epochs was determined by training on the mini train data set until the performance of the mini test set no longer changed.
+    This was considered a reasonable number of epochs to use to train the actual data set.
+
+    For prediction, the $k$ with the maximum value of $\hat{y}_k$ (the argmax of $\hat{y}$) is considered the class prediction by the model.
+    \newpage
+
+    Basic Results:
+
+    \begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.5]{outputs/part1/q1.png}
+    \caption{20 Runs with a Polynomial Kernel}
+    \label{fig:1}
+    \end{figure}
 
@@
 
-    \includegraphics{outputs/part1/q2.png}
+    \begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.5]{outputs/part1/q2.png}
+    \caption{5-fold Cross-Validation for 20 Runs with a Polynomial Kernel}
+    \label{fig:2}
+    \end{figure}
+\newpage
 
@@
 
-    \includegraphics{outputs/part1/q3_confusion.png}
+    \begin{figure}[h]
+    \centering
+    \begin{minipage}{.5\textwidth}
+      \centering
+      \includegraphics[width=.8\linewidth]{outputs/part1/q3_confusion-imshow_mean.png}
+      \caption{Polynomial Kernel Mean}
+      \label{fig:3}
+    \end{minipage}%
+    \begin{minipage}{.5\textwidth}
+      \centering
+      \includegraphics[width=.8\linewidth]{outputs/part1/q3_confusion-imshow_stdev.png}
+      \caption{Polynomial Kernel St. Dev.}
+      \label{fig:4}
+    \end{minipage}
+    \end{figure}
+
+    \begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.5]{outputs/part1/q3_confusion.png}
+    \caption{Polynomial Kernel Confusion Matrix Error Rate Table}
+    \label{fig:5}
+    \end{figure}
+
+    \item[4.] The images with the most errors made by the 20 models trained with cross-validation were considered the hardest to predict and visualised.
+    It is not surprising that these are to predict. 
+    We can see that in all five cases in Figure~\ref{fig:6}, the images do not look like their labels, in fact, they mostly look vertical or horizontal bars.
+    Thus it would be unreasonable to expect that the model would be able to predict them correctly.
+
+    \begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.7]{outputs/part1/q4.png}
+    \caption{Images with the Most Errors from the Trained Models}
+    \label{fig:6}
+    \end{figure}
+
     \newpage
-    \item[4.] Hardest to predict images:
 
-    \includegraphics{outputs/part1/q4.png}
+    \item[5.] To select a good range of values for kernel width sigma for the Gaussian kernel, the mini training and test set was used to quickly gauge the test error for different hyper-parameters.
+    The hyper-parameter values above and below the best performing hyper-parameter (with respect to test set error) was chosen as the hyper-parameter range to define $S$, the set of values for cross-validation for repeating parts 1 and 2 with the Gaussian Kernel.
+    \begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.5]{outputs/part1/q5_1-mini.png}
+    \caption{Performance for mini data set (to narrow down a hyper-parameter range)}
+    \label{fig:7}
+    \end{figure}
     \newpage
-    \item[5.] Basic Results:
 
-    \includegraphics{outputs/part1/q5_1.png}
+    Basic Results:
+
+    \begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.5]{outputs/part1/q5_1.png}
+    \caption{20 Runs with a Gaussian Kernel}
+    \label{fig:8}
+    \end{figure}
 
@@
 
-    \includegraphics{outputs/part1/q5_2.png}
+    \begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.5]{outputs/part1/q5_2.png}
+    \caption{5-fold Cross-Validation for 20 Runs with a Gaussian Kernel}
+    \label{fig:9}
+    \end{figure}
+
+\newpage
+    \item[6.] An alternative method to generalise the kernel perceptron to $k$-classes:
+
+    \begin{algorithm}
+    \caption{Another training algorithm for multi-class kernel perceptron}\label{alg:cap}
+    \begin{algorithmic}
+    \For{$k\in\{1, 2, ..., K\}}$ \Comment Initialise weights for first training example
+        \State $w^{1, 1}_k \gets 0$
+    \EndFor
+
+    \For{$i\in\{1, 2, ..., M\}$}: \Comment Number of Epochs
+        \For{$j\in\{2, ..., N\}}$ \Comment Number of training points
+            \For{$k\in\{1, 2, ..., K\}}$ \Comment Number of classes
+                \State $\hat{y}_k^{i, j} \gets  \sum_{i'=1}^{i-1} \sum_{j'=1}^{j-1} ( w^{i, j}_k \cdot  k(\textbf{x}_{j'}, \textbf{x}_j)} )$ \Comment{Prediction for class $k$ with kernel $k(\cdot, \cdot)$}
+            \EndFor
+            \State $\hat{c} \gets argmax_k \hat{y}_k^{i, j}$ \Comment Predicted class
+            \State $c \gets argmax_k y_k^{i, j}$ \Comment Actual class
+            \If{$\hat{c} \neq c$} \Comment Compare predicted and actual class
+                \State $w^{i, j}_{c} \gets y_{c}^{i, j}$ \Comment Non-zero weights only for actual and predicted classes
+                \State $w^{i, j}_{\hat{c}} \gets y_{\hat{c}}^{i, j}$
+                \State $w^{i, j}_{k} \gets 0 \forall k\in\{1, 2, ..., K\}, k \neq c, k\neq \hat{c}$
+            \Else \Comment All zero weights if actual and predicted classes match
+                \State $w^{i, j}_{k} \gets 0 \forall k\in\{1, 2, ..., K\}$
+                \EndIf
+        \EndFor
+    \EndFor
+    \end{algorithmic}
+    \end{algorithm}
+\newpage
+
+    Basic Results:
+
+    \begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.5]{outputs/part1/q6.png}
+    \caption{}
+    \label{fig:10}
+    \end{figure}
+    Cross Validation Results:
+
+    \begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.5]{outputs/part1/q6_performance.png}
+    \caption{}
+    \label{fig:11}
+    \end{figure}
+
 \end{itemize}
+\newpage
 \subsubsection{Discussions}
@@
 \\
-
-\includegraphics{outputs/part2/laplacian_interpolation_report.png}
+    \begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.5]{outputs/part2/laplacian_interpolation_report.png}
+    \caption{}
+    \label{fig:12}
+    \end{figure}
 
@@
 And for the laplacian kernel method:
-
-\includegraphics{outputs/part2/laplacian_kernel_interpolation_report.png}
+    \begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.5]{outputs/part2/laplacian_kernel_interpolation_report.png}
+    \caption{}
+    \label{fig:13}
+    \end{figure}
 
@@
 \begin{itemize}
-    \item[a.]
-    \item[b.]
-    \item[c.]
-    \item[D.]\\
+    \item[a.] Sample complexity plots for the four algorithms: perceptron, winnow, least squares, and 1-nearest neighbours.
+
+    \begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.6]{outputs/part3/q1a_perceptron_sample_complexity.png}
+    \caption{Perceptron Sample Complexity}
+    \label{fig:14}
+    \end{figure}
+
+    \begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.6]{outputs/part3/q1a_winnow_sample_complexity.png}
+    \caption{Winnow Sample Complexity}
+    \label{fig:15}
+    \end{figure}
+\newpage
+`
+
+    \begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.6]{outputs/part3/q1a_lin_reg_sample_complexity.png}
+    \caption{Least Squares Sample Complexity}
+    \label{fig:16}
+    \end{figure}
+
+    \begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.6]{outputs/part3/q1a_one_nn_sample_complexity.png}
+    \caption{1-Nearest Neighbours Sample Complexity}
+    \label{fig:17}
+    \end{figure}
+
+\newpage
+
+    \item[b.] To estimate sample complexity,
+
+    Tradeoffs and biases of this method of sample complexity estimation include
+\newpage
+    \item[c.] To estimate how $m$ grows as a function of $n$ as $n \rightarrow \infty$ for each of the four algorithms, we first visualise lines of best fit of the sample complexities for different function classes (i.e.
+polynomial, exponential, logarithm):
+
+    \begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.35]{outputs/part3/q1a_perceptron_complexity_function_comparison.png}
+    \caption{Perceptron Sample Complexity vs Function Classes}
+    \label{fig:18}
+    \end{figure}
+
+    \begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.35]{outputs/part3/q1a_winnow_complexity_function_comparison.png}
+    \caption{Winnow Sample Complexity vs Function Classes}
+    \label{fig:19}
+    \end{figure}
+\newpage
+    \begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.35]{outputs/part3/q1a_lin_reg_complexity_function_comparison.png}
+    \caption{Least Squares Sample Complexity vs Function Classes}
+    \label{fig:21}
+    \end{figure}
+
+    \begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.35]{outputs/part3/q1a_one_nn_complexity_function_comparison.png}
+    \caption{1-Nearest Neighbours Sample Complexity vs Function Classes}
+    \label{fig:22}
+    \end{figure}
+
+    From these plots we can see
+
+    Comparing the performance of the four algorithms
+
+\newpage
+
+    \item[d.]\\
     We note that since for any $X_{t}$ , $y_{t} = X_{1,t}$ , we have the following
@@
 
-     \item[E.]\\
+\newpage
+
+     \item[e.]\\
      From our experimental observations we may expect the sample complexity of 1-NN

### 2022-12-11 main.py

@@ -5,14 +5,18 @@ import numpy as np
 import pandas as pd
 from scipy.optimize import curve_fit
 
-from src.constants import (DEFAULT_SEED, OUTPUTS_FOLDER, PART_1_DATA_SET_PATH,
-                           PART_1_MINI_TEST_SET_PATH,
-                           PART_1_MINI_TRAIN_SET_PATH)
-from src.models.helpers import (TrainTestData, one_hot_encode,
-                                split_train_test_data)
+from src.constants import (
+    DEFAULT_SEED,
+    OUTPUTS_FOLDER,
+    PART_1_DATA_SET_PATH,
+    PART_1_MINI_TEST_SET_PATH,
+    PART_1_MINI_TRAIN_SET_PATH,
+)
+from src.models.helpers import TrainTestData, one_hot_encode, split_train_test_data
 from src.models.kernels import GaussianKernel, PolynomialKernel
-from src.models.single_class.linear_regression_classifier import \
-    LinearRegressionClassifier
+from src.models.single_class.linear_regression_classifier import (
+    LinearRegressionClassifier,
+)
 from src.models.single_class.one_nn import OneNN
 from src.models.single_class.perceptron import Perceptron
 from src.models.single_class.winnow import Winnow

### 2022-12-11 src/models/multi_class/perceptron.py

@@ -14,7 +14,6 @@ def predict(w: np.ndarray, gram: np.ndarray) -> jnp.ndarray:
                  (N_1,...,N_M, number_training_points, number_test_points)
     :return: a prediction for the single input (N_1,...,N_M, number_classes)
     """
-    # return jnp.sum(jnp.multiply(w, gram[..., None]), axis=-2)
     return gram.T @ w
 
 

### 2022-12-12 submission.tex
update report with part 1 and 3

@@
     \For{$k\in\{1, 2, ..., K\}}$ \Comment Initialise weights for first training example
-
+        \State $w^{1, 1}_k \gets 0$
     \EndFor
@@
     \For{$i\in\{1, 2, ..., M\}$}: \Comment Number of Epochs
-        \For{$j\in\{2, ..., N\}}$ \Comment Number of training points
+        \For{$j\in\{2, ..., N\}}$ \Comment Number of training points (skipping the first point)
             \For{$k\in\{1, 2, ..., K\}}$ \Comment Number of classes
-                \State $\hat{y}_k^{i, j} \gets  \sum_{i'=1}^{i-1} \sum_{j'=1}^{j-1} ( w^{i, j}_k \cdot  k(\textbf{x}_{j'}, \textbf{x}_j)} )$ \Comment{Prediction for class $k$ with kernel $k(\cdot, \cdot)$}
+                \State $\hat{y}_k^{i, j} \gets  \sum_{i'=1}^{i-1} \sum_{j'=1}^{j-1} ( w^{i', j'}_k \cdot  k(\textbf{x}_{j'}, \textbf{x}_j)} )$ \Comment{Prediction for class $k$ with kernel $k(\cdot, \cdot)$}
                 \If{$sign(\hat{y}_k^{i, j}) \neq sign(y_k^{i, j})$} \Comment Compare predicted $\hat{y}_k^{i, j}$ and actual $y_k^{i, j})$
@@
 
-    The number of epochs was determined by training on the mini train data set until the performance of the mini test set no longer changed.
+    The number of epochs was determined by training on the mini training data set until the performance of the mini testing data set no longer changed.
     This was considered a reasonable number of epochs to use to train the actual data set.
 
-    For prediction, the $k$ with the maximum value of $\hat{y}_k$ (the argmax of $\hat{y}$) is considered the class prediction by the model.
+    For prediction, the $k$ with the maximum value of $\hat{y}_k$ (the argmax of $\hat{y}$) is considered the label prediction by the model.
     \newpage
@@
 
-    \item[4.] The images with the most errors made by the 20 models trained with cross-validation were considered the hardest to predict and visualised.
-    It is not surprising that these are to predict. 
-    We can see that in all five cases in Figure~\ref{fig:6}, the images do not look like their labels, in fact, they mostly look vertical or horizontal bars.
-    Thus it would be unreasonable to expect that the model would be able to predict them correctly.
+    \item[4.] The images with the most errors made by the 20 models trained in part 2 were considered the hardest to predict and visualised.
+    It is not surprising that these are hard to predict.
+    We can see that in all five cases, the images do not look like their labels, in fact, they mostly look like vertical or horizontal bars.
+    Thus it would be unreasonable to expect a model to predict them correctly.
 
@@
 
-    \item[5.] To select a good range of values for kernel width sigma for the Gaussian kernel, the mini training and test set was used to quickly gauge the test error for different hyper-parameters.
+    \item[5.] To select a good range of values for the kernel width sigma for the Gaussian kernel, the mini training and testing sets was used to quickly gauge the test error for different hyper-parameters.
     The hyper-parameter values above and below the best performing hyper-parameter (with respect to test set error) was chosen as the hyper-parameter range to define $S$, the set of values for cross-validation for repeating parts 1 and 2 with the Gaussian Kernel.
@@
             \For{$k\in\{1, 2, ..., K\}}$ \Comment Number of classes
-                \State $\hat{y}_k^{i, j} \gets  \sum_{i'=1}^{i-1} \sum_{j'=1}^{j-1} ( w^{i, j}_k \cdot  k(\textbf{x}_{j'}, \textbf{x}_j)} )$ \Comment{Prediction for class $k$ with kernel $k(\cdot, \cdot)$}
+                \State $\hat{y}_k^{i, j} \gets  \sum_{i'=1}^{i-1} \sum_{j'=1}^{j-1} ( w^{i', j}_k \cdot  k(\textbf{x}_{j'}, \textbf{x}_j)} )$ \Comment{Prediction for class $k$ with kernel $k(\cdot, \cdot)$}
             \EndFor
-            \State $\hat{c} \gets argmax_k \hat{y}_k^{i, j}$ \Comment Predicted class
-            \State $c \gets argmax_k y_k^{i, j}$ \Comment Actual class
-            \If{$\hat{c} \neq c$} \Comment Compare predicted and actual class
-                \State $w^{i, j}_{c} \gets y_{c}^{i, j}$ \Comment Non-zero weights only for actual and predicted classes
+            \State $\hat{c} \gets argmax_k \hat{y}_k^{i, j}$ \Comment Predicted label
+            \State $c \gets argmax_k y_k^{i, j}$ \Comment Actual label
+            \If{$\hat{c} \neq c$} \Comment Compare predicted and actual label
+                \State $w^{i, j}_{c} \gets y_{c}^{i, j}$ \Comment Non-zero weights only for actual and predicted label
                 \State $w^{i, j}_{\hat{c}} \gets y_{\hat{c}}^{i, j}$
                 \State $w^{i, j}_{k} \gets 0 \forall k\in\{1, 2, ..., K\}, k \neq c, k\neq \hat{c}$
-            \Else \Comment All zero weights if actual and predicted classes match
+            \Else \Comment All zero weights if actual and predicted labels match
                 \State $w^{i, j}_{k} \gets 0 \forall k\in\{1, 2, ..., K\}$
@@
     \includegraphics[scale=0.5]{outputs/part1/q6.png}
-    \caption{}
+    \caption{20 Runs with a Polynomial Kernel (Alternative Training Method)}
     \label{fig:10}
@@
     \includegraphics[scale=0.5]{outputs/part1/q6_performance.png}
-    \caption{}
+    \caption{5-fold Cross-Validation for 20 Runs with a Polynomial Kernel (Alternative Training Method)}
     \label{fig:11}
@@
 \subsubsection{Discussions}
-    Choice of Parameters that weren't cross validated
 
-    Generalisation to k-classifiers
+For these experiments, the number of folds, number of runs, and train/test split were parameters that were arbitrarily chosen, not chosen through cross-validation.
+Moreover, the kernel parameters were cross-validated to find optimal values, however the range for which cross validation was performed over (i.e.
+degree 1 to 7 for the polynomial kernel) was chosen relatively arbitrarily.
+For Gaussian kernels, this was done in a two step process, where a very wide range for sigma was initially used, although this wide range was still chosen arbitrarily.
+Increasing the number of folds would provide a better estimate of the out of sample performance (i.e.
+in the limit where we have N folds, each training on $N-1$ points and testing on the single excluded data point).
+However, this can be quite computationally heavy and a compromise must be drawn.
+This a similar situation for the number of runs.
+By increasing the number of runs, we gain a better understanding of average performance, however this is at a computational cost of performing more runs.
+The train/test split used for these experiments was 80\% training data and 20\% testing data.
+This follows general rule of thumb for train/test splits.
+Given a finite data set size, increasing the training percentage can provide inaccurate out of sample performance with the test set.
+Conversly, a smaller training percentage can poorly represent the model's performance due to limited training examples.
+Thus a balance must be drawn between the two.
+The range of hyper-parameters to search for cross validation requires past experience working with kernels and knowledge about the given data set.
+However these ranges can be quite general (as shown for the Gaussian kernel where we search a space from $1e-05$ to $1e+01$) and we can iteratively narrow our search space.
 
-    Kernel Comparison
+Comparing the two methodologies for generalising the perceptron to $k$-class classifiers, we can see that the main implementation difference is with the training process, where Algorithm 1 can update an arbitrary number of its weights to be non-zero while Algorithm 2 will update only two weights if the prediction is incorrect.
+In this sense, Algorithm 1 is like training $k$ independent binary classifiers, where updates are made for each sub-classifier independent of other the prediction of the others.
+Algorithm 2 introduces dependence between sub-classifiers during the training phase.
+This is because whether a sub-classifier is selected to be updated depends on if it is the label predicting classifier (i.e.
+the argmax) or the classifier for the actual label.
+Otherwise, it is not updated.
+In some sense, Algorithm 1 is able to pass "correction" signal to all of its classifiers at each step, while Algorithm 2 is constrained in its "speed" of training its classifiers to a maximum of two at a time.
+Comparing Figure~\ref{fig:2} and Figure~\ref{fig:11}, we can see that Algorithm 1 performs better than Algorithm 2 and this is likely due to this ability of Algorithm 1 to perform corrections for all its classifiers even if they are not the actual label or wrongly predicted label for a training example.
 
-    Kernel Perceptron Implementation
+Comparing Figure~\ref{fig:2} and Figure~\ref{fig:9}, we can see that the Gaussian Kernel performs better than the Polynomial Kernel.
+This is expected because the Gaussian Kernel provides a more expressive (infinite) feature space to model the data compared to a Polynomial kernel.
+
+These experiments were implemented by vectorising and simulating the training behaviour of this online algorithm for faster computation.
+However, the results exactly mimic the behaviour of the algorithms depicted.
+The vectorisation starts with initialising a zeros weight matrix $ \textbf{w} = \textbf{0} \in \mathbb{R}^{KxN}$.
+During the $j^{th}$ step of training, we only update the $j^{th}$ column of weights in $\textbf{w}$.
+Thus, during prediction for the $j^{th}$ training example, we know that all weights for training examples $\geq j$ will be zero and we will be simulating an online algorithm that only predicts using the $< j$ examples.
+Moreover during prediction, the operation $\sum_{i'=1}^{i-1} \sum_{j'=1}^{j-1} ( w^{i', j'}_k \cdot  k(\textbf{x}_{j'}, \textbf{x}_j)}$ can be factored as $ \sum_{j'=1}^{j-1} (\sum_{i'=1}^{i-1} w^{i', j'}_k ) \cdot   k(\textbf{x}_{j'}, \textbf{x}_j)}$.
+Thus, instead of storing a weight matrix of size $\mathbb{R}^{Kx(N \cdot M)}$, for $M$ epochs, we can sum the weights corresponding to the sample training example over multiple epochs and have a weight matrix of constant size $\mathbb{R}^{KxN}$.
+The kernel evaluations were also precomputed to simulate the online model and speed up computation.
+Precomputing the gram matrix for a kernel helps vectorise the operation.
+Thus during the simulated online model, the gram matrix is simply indexed at the appropriate training example to perform the weight updates.
+Additionally, across different hyper-parameters for a given kernels, a "pre-gram matrix" is pre-computed and used across the different hyper-parameters of a kernel.
+For example with a polynomial kernel, the gram matrix of inner products is computed as a "pre-gram matrix".
+Then for each polynomial experiment, the elements of the matrix is simply raised to the $d^{th}$ degree.
+This also significantly improves the speed of the experiments because a single "pre-gram matrix" can be shared across experiments during a hyper-parameter search.
+Although the perceptron training algorithm is sequential in nature (i.e.
+the new weight update depends on the weight updates of the previous step), each hyper-parameter and each run is independent.
+This invites the opportunity to run these in parallel, performing weight updates for multiple runs in parallel.
+However we ran into issues of memory constraints when trying to run this on our machine with the given data set, so our implementation did not take advantage of this.
 
@@
 Note that error variance decreases as a function of the number of known labels, but 
-has a muhc more significant impacgt for the vanilla interpolation method.
+has a much more significant impact for the vanilla interpolation method.
 
@@
 
-    \item[b.] To estimate sample complexity,
+    \item[b.] The following algorithm was used to estimate sample complexity:
 
-    Tradeoffs and biases of this method of sample complexity estimation include
+    \begin{algorithm}
+    \caption{Sample Complexity Estimation Algorithm}\label{alg:cap}
+    \begin{algorithmic}
+    \For{$n\in\{1, 2, ..., N\}$}: \Comment Number of dimensions
+        \State $\mathcal{M}_n \gets []$ \Comment Store $m$ values for each trial
+        \For {$t\in\{1, 2, ..., T\}$} \Comment Number of trials
+            \State $m \gets  0$ \Comment Number of training points
+            \State $\mathcal{D}_{train} \gets  \{\}$ \Comment Training set
+            \State $\mathcal{D}_{test} \gets  \{(x^1_{test}, y^1_{test}), ..., (x^{M'}_{test}, y^{M'}_{test})\}$ \Comment Fixed test set of size $M'$
+            \State $error \gets  1 \Comment initial test set error
+            \While{$error > 0.1$}
+                \State $m \gets  m+1$
+                \State $\mathcal{D}_{train} \gets  \mathcal{D}_{train} \cup \{(x^m_{train}, y^m_{train})\}$ \Comment Add a new training point
+                \State $error \gets model.train({D}_{train}).test({D}_{test})$ \Comment Train model and compute error
+            \EndWhile
+            \State $\mathcal{M}_n \gets \mathcal{M}_n + [m]$
+        \EndFor
+    \end{algorithmic}
+    \end{algorithm}
+    For each $\mathcal{M}_n$ the mean and standard deviation were calculated to produce the plots for each model.
+    Choosing different values for the number of trials $T$ and the test set size $M'$, is a tradeoff between limited computation resources and accuracy of our approximation.
+With larger number of trials, we improve our approximation, however this requires more computational resources.
+A larger test set size $M'$ provides a better approximation of $\{-1 ,1\}^n$ and therefore a better approximation of the generalisation error.
+Moreover, choosing $N$ puts a finite horizon on the number of points available for estimating the sample complexity function.
+For some algorithms such as one-nearest neighbours, we see that the number of training samples grows exponentially with $n$.
+Thus to have a plot up to 100 dimensions like with least squares, would require a lot more computational resources.
+As such, we limited our evaluation for one-NN to 20 dimensions.
+However, this can introduce biases in our estimation of the sample complexity.
+It is possible that our chosen finite horizon is inadequate for capturing the dynamics as $n \rightarrow \infty$.
+For example, a sample complexity that is actually exponential could seem linear if we do not choose an $N$ that is large enough to reveal this trend.
+
 \newpage
@@
 
-    From these plots we can see
-
-    Comparing the performance of the four algorithms
+    From these plots we can see that the perceptron sample complexity grows linearly ($m = \Theta(n)$), the Winnow sample complexity grows logarithmically ($m = \Theta(\log(n))$), the least squares sample complexity grows linearly ($m = \Theta(n)$), and the 1-nearest neighbours sample complexity grows exponentially ($m = \Theta(e^{n})$).
+These estimates can be qualitatively observed by attempting to fit different function curves to the experimental results and choosing the function with the best qualitative fit.
+This shows that winnow is a much more robust algorithm in high dimensions due to its logarithmic scaling of the number of training points with respect to the dimensionality to achieve the same error rate.
+On the other hand, one-nearest neighbours scales exponentially, suggesting that it is impractical to use in high dimensional data.
+This can be attributed to the curse of dimensionality.
+Both the perceptron and least squares scale linearly, thus performing worse than winnow but better than the one-NN algorithm.
 

### 2022-12-13 submission.tex
problem with latex file

@@
 
-Experimental report for the laplacian interpolation approach:
-\\
     \begin{figure}[h]
@@
     \includegraphics[scale=0.5]{outputs/part2/laplacian_interpolation_report.png}
-    \caption{}
+    \caption{Laplacian Interpolation}
     \label{fig:12}
@@
 
-\\
-
-And for the laplacian kernel method:
     \begin{figure}[h]
@@
     \includegraphics[scale=0.5]{outputs/part2/laplacian_kernel_interpolation_report.png}
-    \caption{}
+    \caption{Laplacian Kernel Interpolation}
     \label{fig:13}
@@
 
-Some observations to make here are:\\
+\end{}
+\subsubsection{Discussions}
+Both models exhibit high accuracy in all low-data settings. We see here that the vast majority of datapoints are connected only to points
+of the same labelling, and that the graph is highly separated into 2 clusters.
+Hence with minimal training information, both methods are able to predict with a
+high degree of accuracy. For the laplacian seminorm interpolation method, this may be observed 
+as its solution in the objective-minimisation form essentially describes a graph cut of minimal size, respecting
+the true labels. We should note that in both of our models, the only pints that will be classified incorrectly with a 
+reasonably high probability are these teal points in the diagram above.\\
 
-a) Both models seem to perform fairly well, even in the low-data setting.\\
+b) Increasing the number of labelled datapoints generally increases the accuracy in both models.\\
 
-b) Increating the number of known labels increases the accuracy and decreases
- the variance of the predictors.\\
+c) Increasing the total number of datapoints generally decreases the error variance in the seminorm interpolation
+model, but has a limited impact on the kernel interpolation model. \\
 
-c) Increasing the total number of datapoints generally increases both model accuracies,
-and decreases variance. \\
+d) The laplacian kernel method outperforms the vanilla inerpolation approach considerably, in accuracy, and less so
+for variance. \\
 
-d) The laplacian kernel method outperforms the vanilla inerpolation approach considerably,
-on both accuracy and variance. \\
-
-The main reason for the success of this algorithm is the high degree of
+The main reason for the success of these models is the high degree of
 cluster separation observed in the dataset.
@@
 
-For illustration, here is a diagram representing the graph adjacency matrix,
+For illustration, here is a diagram representing the graph adjacency matrix for 50 labels per class,
 with colours showing the labelling of an edge. Here blue edges are where both 
@@
 
-\includegraphics{outputs/part2/graph_label_diagram.png}#
-
-We see through this that the vast majority of datapoints are connected only to points
-of the same labelling, and that the graph is highly separated  into 2 clusters.
-Hence with minimal training information, both methods are able to predict with a
- high degree of accuracy.\\
+\includegraphics{outputs/part2/graph_label_diagram.png}
 
 Note that error variance decreases as a function of the number of known labels, but 
-has a much more significant impact for the vanilla interpolation method.
+has a more significant impact for the vanilla interpolation method. A reasonable explanation for this is that our
 
@@
 interpolation method. A reasonable explanation for this is that the laplacian
-interpolation approach utilises local information to 'diffuse' labels through the graph. 
-This means that only datapoints close to labelled data receive information from the 
+interpolation approach utilises local information to 'diffuse' label information through the graph. 
+This means that only datapoints close to labelled data receive direct information from the 
 labels themselves, and accuracy is likely reduced for datapoints far from the labels.
@@
 \begin{itemize}
-    \item[a.] Sample complexity plots for the four algorithms: perceptron, winnow, least squares, and 1-nearest neighbours.
-
-    \begin{figure}[h]
-    \centering
-    \includegraphics[scale=0.6]{outputs/part3/q1a_perceptron_sample_complexity.png}
-    \caption{Perceptron Sample Complexity}
-    \label{fig:14}
-    \end{figure}
-
-    \begin{figure}[h]
-    \centering
-    \includegraphics[scale=0.6]{outputs/part3/q1a_winnow_sample_complexity.png}
-    \caption{Winnow Sample Complexity}
-    \label{fig:15}
-    \end{figure}
-\newpage
-`
-
-    \begin{figure}[h]
-    \centering
-    \includegraphics[scale=0.6]{outputs/part3/q1a_lin_reg_sample_complexity.png}
-    \caption{Least Squares Sample Complexity}
-    \label{fig:16}
-    \end{figure}
-
-    \begin{figure}[h]
-    \centering
-    \includegraphics[scale=0.6]{outputs/part3/q1a_one_nn_sample_complexity.png}
-    \caption{1-Nearest Neighbours Sample Complexity}
-    \label{fig:17}
-    \end{figure}
-
-\newpage
-
-    \item[b.] The following algorithm was used to estimate sample complexity:
-
-    \begin{algorithm}
-    \caption{Sample Complexity Estimation Algorithm}\label{alg:cap}
-    \begin{algorithmic}
-    \For{$n\in\{1, 2, ..., N\}$}: \Comment Number of dimensions
-        \State $\mathcal{M}_n \gets []$ \Comment Store $m$ values for each trial
-        \For {$t\in\{1, 2, ..., T\}$} \Comment Number of trials
-            \State $m \gets  0$ \Comment Number of training points
-            \State $\mathcal{D}_{train} \gets  \{\}$ \Comment Training set
-            \State $\mathcal{D}_{test} \gets  \{(x^1_{test}, y^1_{test}), ..., (x^{M'}_{test}, y^{M'}_{test})\}$ \Comment Fixed test set of size $M'$
-            \State $error \gets  1 \Comment initial test set error
-            \While{$error > 0.1$}
-                \State $m \gets  m+1$
-                \State $\mathcal{D}_{train} \gets  \mathcal{D}_{train} \cup \{(x^m_{train}, y^m_{train})\}$ \Comment Add a new training point
-                \State $error \gets model.train({D}_{train}).test({D}_{test})$ \Comment Train model and compute error
-            \EndWhile
-            \State $\mathcal{M}_n \gets \mathcal{M}_n + [m]$
-        \EndFor
-    \end{algorithmic}
-    \end{algorithm}
-    For each $\mathcal{M}_n$ the mean and standard deviation were calculated to produce the plots for each model.
-    Choosing different values for the number of trials $T$ and the test set size $M'$, is a tradeoff between limited computation resources and accuracy of our approximation.
-With larger number of trials, we improve our approximation, however this requires more computational resources.
-A larger test set size $M'$ provides a better approximation of $\{-1 ,1\}^n$ and therefore a better approximation of the generalisation error.
-Moreover, choosing $N$ puts a finite horizon on the number of points available for estimating the sample complexity function.
-For some algorithms such as one-nearest neighbours, we see that the number of training samples grows exponentially with $n$.
-Thus to have a plot up to 100 dimensions like with least squares, would require a lot more computational resources.
-As such, we limited our evaluation for one-NN to 20 dimensions.
-However, this can introduce biases in our estimation of the sample complexity.
-It is possible that our chosen finite horizon is inadequate for capturing the dynamics as $n \rightarrow \infty$.
-For example, a sample complexity that is actually exponential could seem linear if we do not choose an $N$ that is large enough to reveal this trend.
-
-\newpage
-    \item[c.] To estimate how $m$ grows as a function of $n$ as $n \rightarrow \infty$ for each of the four algorithms, we first visualise lines of best fit of the sample complexities for different function classes (i.e.
-polynomial, exponential, logarithm):
-
-    \begin{figure}[h]
-    \centering
-    \includegraphics[scale=0.35]{outputs/part3/q1a_perceptron_complexity_function_comparison.png}
-    \caption{Perceptron Sample Complexity vs Function Classes}
-    \label{fig:18}
-    \end{figure}
-
-    \begin{figure}[h]
-    \centering
-    \includegraphics[scale=0.35]{outputs/part3/q1a_winnow_complexity_function_comparison.png}
-    \caption{Winnow Sample Complexity vs Function Classes}
-    \label{fig:19}
-    \end{figure}
-\newpage
-    \begin{figure}[h]
-    \centering
-    \includegraphics[scale=0.35]{outputs/part3/q1a_lin_reg_complexity_function_comparison.png}
-    \caption{Least Squares Sample Complexity vs Function Classes}
-    \label{fig:21}
-    \end{figure}
-
-    \begin{figure}[h]
-    \centering
-    \includegraphics[scale=0.35]{outputs/part3/q1a_one_nn_complexity_function_comparison.png}
-    \caption{1-Nearest Neighbours Sample Complexity vs Function Classes}
-    \label{fig:22}
-    \end{figure}
-
-    From these plots we can see that the perceptron sample complexity grows linearly ($m = \Theta(n)$), the Winnow sample complexity grows logarithmically ($m = \Theta(\log(n))$), the least squares sample complexity grows linearly ($m = \Theta(n)$), and the 1-nearest neighbours sample complexity grows exponentially ($m = \Theta(e^{n})$).
-These estimates can be qualitatively observed by attempting to fit different function curves to the experimental results and choosing the function with the best qualitative fit.
-This shows that winnow is a much more robust algorithm in high dimensions due to its logarithmic scaling of the number of training points with respect to the dimensionality to achieve the same error rate.
-On the other hand, one-nearest neighbours scales exponentially, suggesting that it is impractical to use in high dimensional data.
-This can be attributed to the curse of dimensionality.
-Both the perceptron and least squares scale linearly, thus performing worse than winnow but better than the one-NN algorithm.
-
-\newpage
-
-    \item[d.]\\
+    \item[a.]
+    \item[b.]
+    \item[c.]
+    \item[D.]\\
     We note that since for any $X_{t}$ , $y_{t} = X_{1,t}$ , we have the following
@@
     Hence, in our online mistake bound for the perceptron, we have that $\gamma =1$.
-    Further note that $\forall t$, $x_{t} \in {-1,1}^{n} \implies \|x_{t}\|^{2}
+    Further note that $\forall t$, $x_{t} \in \{-1,1\}^{n} \implies \|x_{t}\|^{2}
     = n$. This gives us that $R = max_{t} \|x_{t}\| = \sqrt{n}$.
@@
 
-\newpage
-
-     \item[e.]\\
+     \item[E.]\\
      From our experimental observations we may expect the sample complexity of 1-NN
@@
 
-    $m(n) = \Omega (n)$ \\
+    $m(n) = \Omega (2^{n})$ \\
     \textbf{Proof:}\\
 
-    Suppose we sample a training set $S = \{(x_{1},y_{1}), \dots, (x_{n},y_{n})\} $ uniformly from the set $\{-1,1\}^{n}$, with associated labels
+    We note the following result on generalisation error. 
+    \\
+
+    $L_{D}(1-NN) = \mathbf{E}_{(x,y) \sim \mathcal{D}, S \sim \mathcal{D}^{m}}(\mathbf{1}_{[\mathcal{A}_{S}(x) \ne y]})$
+
+    Note that since $\mathbf{1}_{[\mathcal{A}_{S}(x) \ne f(x)]}$ is a bernoulli variable, its expectation is given by:\\
+    $ P_{x \sim \mathcal{D}, S \sim \mathcal{D}^{m}}(\mathcal{A}_{S}(x) \ne y)$, which is our new expression for the generalisation error.\\
+
+    Suppose we sample a training set $S = \{(x_{1},y_{1}), \dots, (x_{n},y_{n})\} $, x sampled uniformly from the set $\{-1,1\}^{n}$, with associated labels
     defined by the rule $y | x = x_{1}$, and use this training set for inference on an
-     arbitrary test point $(x,x_{1})$, sampled uniformly from the same set.
+     arbitrary test point $(x,x_{1})$, sampled uniformly from the same data generating distribution.
     \\
@@
 
-    Hence, the set of all training sets that make an error on x is contained in the set of all
-    training sets not containing x. \\
+    Hence, $ \{S \subseteq \{-1,1\}^{n} : \mathcal{A}_{S}(x) \ne y \} \subseteq \{S \subseteq \{-1,1\}^{n} : x \notin S \} \\
 
@@
 
-    $\mathbb{E}_{S \sim \mathcal{D}^{m}, x \sim \mathcal{D}}[\mathcal{L}_{S}(x)] \le exp(-2^{n}m)$
-    \\
+    $\mathbb{E}_{S \sim \mathcal{D}^{m}, x \sim \mathcal{D}}[\mathcal{L}_{S}(x)] \le exp(-2^{-n}m)$\\
     Suppose we seek m such that our generalisation error is less than some fixed $\epsilon$. \\
     \\
-    Hence we require $\mathbb{E}_{S \sim \mathcal{D}^{m}, x \sim \mathcal{D}}[\mathcal{L}_{S}(x)] \le exp(-2^{n}m) \le \epsilon$\\
+    Hence we require $\mathbb{E}_{S \sim \mathcal{D}^{m}, x \sim \mathcal{D}}[\mathcal{L}_{S}(x)] \le exp(-2^{-n}m) \le \epsilon$\\
     \\

### 2022-12-13 main.py

@@ -20,7 +20,7 @@ from src.models.single_class.linear_regression_classifier import (
 from src.models.single_class.one_nn import OneNN
 from src.models.single_class.perceptron import Perceptron
 from src.models.single_class.winnow import Winnow
-from src.solutions import part_1, part_3
+from src.solutions import part_1, part_2, part_3
 
 np.random.seed(DEFAULT_SEED)
 
@@ -96,172 +96,172 @@ if __name__ == "__main__":
 
     # GAUSSIAN KERNEL
     # find best parameters
-    part_1.q1(
-        data_mini=data_mini,
-        data=[
-            split_train_test_data(x_mini, y_mini, percent_split)
-            for _ in range(number_of_runs)
-        ],
-        kernel_class=GaussianKernel(),
-        kernel_parameters=np.logspace(-5, 1, 20),
-        kernel_parameter_name="sigma",
-        test_error_convergence_rate=test_error_convergence_rate,
-        df_performance_path=os.path.join(PART_1_OUTPUT_FOLDER, "q5_1-mini"),
-    )
-    df_gaussian_kernel_performance = pd.read_csv(
-        os.path.join(PART_1_OUTPUT_FOLDER, "q5_1-mini.csv")
-    )
-    best_parameter_idx = np.argmin(df_gaussian_kernel_performance["Test Error"])
-    best_gaussian_kernel_params = list(
-        df_gaussian_kernel_performance.iloc[
-            best_parameter_idx - 1 : best_parameter_idx + 2, 0
-        ]
-    )
-    best_gaussian_kernel_params = [
-        float(x.split("=")[1])
-        for x in [best_gaussian_kernel_params[0], best_gaussian_kernel_params[-1]]
-    ]
+    # part_1.q1(
+    #     data_mini=data_mini,
+    #     data=[
+    #         split_train_test_data(x_mini, y_mini, percent_split)
+    #         for _ in range(number_of_runs)
+    #     ],
+    #     kernel_class=GaussianKernel(),
+    #     kernel_parameters=np.logspace(-5, 1, 20),
+    #     kernel_parameter_name="sigma",
+    #     test_error_convergence_rate=test_error_convergence_rate,
+    #     df_performance_path=os.path.join(PART_1_OUTPUT_FOLDER, "q5_1-mini"),
+    # )
+    # df_gaussian_kernel_performance = pd.read_csv(
[…]

### 2022-12-13 src/models/laplacian_interpolation.py

@@ -16,9 +16,9 @@ class LaplacianInterpolation:
         :return: y_hat: predicted labels for y_{l+1}, ... , y_{n}
         """
         s = y.shape[0]
-        diagonal = np.diag(w.sum(0))
+        degree_matrix = np.diag(w.sum(0))
         return np.sign(
-            np.linalg.lstsq(diagonal[s:, s:] - w[s:, s:], w[s:, :s] @ y, rcond=None)[0]
+            np.linalg.lstsq(degree_matrix[s:, s:] - w[s:, s:], w[s:, :s] @ y, rcond=None)[0]
         )
 
 

### 2022-12-13 src/solutions/part_2.py

@@ -29,7 +29,7 @@ def experimental_report(
     number_iterations,
 ):
     sample_range = [1, 2, 4, 8, 16]
-    accuracy = np.zeros((4, 5, number_iterations))
+    loss = np.zeros((4, 5, number_iterations))
 
     for iteration in range(number_iterations):
         for i, dataset in enumerate(datasets):
@@ -41,12 +41,12 @@ def experimental_report(
                     y[sample[: 2 * sample_size]],
                     y[sample[2 * sample_size :]],
                 )
-                accuracy[i, j, iteration] = np.mean(
-                    model.predict(w[sample, :][:, sample], y_train) == y_test
+                loss[i, j, iteration] = np.mean(
+                    model.predict(w[sample, :][:, sample], y_train) != y_test
                 )
                 if i == 0:
                     graph_edge_label_diagram(w, y, GRAPH_LABEL_DIAGRAM_PATH)
-    return accuracy.mean(-1), accuracy.std(-1)
+    return loss.mean(-1), loss.std(-1)
 
 
 def write_report_to_csv(means, stds, outpath):
@@ -57,7 +57,7 @@ def write_report_to_csv(means, stds, outpath):
     report.index = [50, 100, 200, 400]
     report = pd.concat(
         [pd.concat([report], keys=["# of known labels (per class)"], axis=1)],
-        keys=["accuracy"],
+        keys=["# of datapoints per label"],
     )
     dfi.export(report, outpath)
 

### 2022-12-13 submission.tex
remove end
revert last 2 commits

--- 2022-12-12 submission.tex
@@
 
-Some observations to make here are:\\
+\subsubsection{Discussions}
+Both models exhibit high accuracy in all low-data settings. We see here that the vast majority of datapoints are connected only to points
+of the same labelling, and that the graph is highly separated into 2 clusters.
+Hence with minimal training information, both methods are able to predict with a
+high degree of accuracy. For the laplacian seminorm interpolation method, this may be observed 
+as its solution in the objective-minimisation form essentially describes a graph cut of minimal size, respecting
+the true labels. We should note that in both of our models, the only pints that will be classified incorrectly with a 
+reasonably high probability are these teal points in the diagram above.\\
 
-a) Both models seem to perform fairly well, even in the low-data setting.\\
+b) Increasing the number of labelled datapoints generally increases the accuracy in both models.\\
 
-b) Increating the number of known labels increases the accuracy and decreases
- the variance of the predictors.\\
+c) Increasing the total number of datapoints generally decreases the error variance in the seminorm interpolation
+model, but has a limited impact on the kernel interpolation model. \\
 
-c) Increasing the total number of datapoints generally increases both model accuracies,
-and decreases variance. \\
-
-d) The laplacian kernel method outperforms the vanilla inerpolation approach considerably,
-on both accuracy and variance. \\
+d) The laplacian kernel method outperforms the vanilla inerpolation approach considerably, in accuracy, and less so
+for variance. \\
 

### 2022-12-13 main.py

@@ -20,7 +20,7 @@ from src.models.single_class.linear_regression_classifier import (
 from src.models.single_class.one_nn import OneNN
 from src.models.single_class.perceptron import Perceptron
 from src.models.single_class.winnow import Winnow
-from src.solutions import part_1, part_2, part_3
+from src.solutions import part_1, part_3
 
 np.random.seed(DEFAULT_SEED)
 
@@ -96,172 +96,172 @@ if __name__ == "__main__":
 
     # GAUSSIAN KERNEL
     # find best parameters
-    # part_1.q1(
-    #     data_mini=data_mini,
-    #     data=[
-    #         split_train_test_data(x_mini, y_mini, percent_split)
-    #         for _ in range(number_of_runs)
-    #     ],
-    #     kernel_class=GaussianKernel(),
-    #     kernel_parameters=np.logspace(-5, 1, 20),
-    #     kernel_parameter_name="sigma",
-    #     test_error_convergence_rate=test_error_convergence_rate,
-    #     df_performance_path=os.path.join(PART_1_OUTPUT_FOLDER, "q5_1-mini"),
-    # )
-    # df_gaussian_kernel_performance = pd.read_csv(
-    #     os.path.join(PART_1_OUTPUT_FOLDER, "q5_1-mini.csv")
-    # )
-    # best_parameter_idx = np.argmin(df_gaussian_kernel_performance["Test Error"])
-    # best_gaussian_kernel_params = list(
-    #     df_gaussian_kernel_performance.iloc[
-    #         best_parameter_idx - 1 : best_parameter_idx + 2, 0
-    #     ]
-    # )
-    # best_gaussian_kernel_params = [
-    #     float(x.split("=")[1])
-    #     for x in [best_gaussian_kernel_params[0], best_gaussian_kernel_params[-1]]
-    # ]
+    part_1.q1(
+        data_mini=data_mini,
+        data=[
+            split_train_test_data(x_mini, y_mini, percent_split)
+            for _ in range(number_of_runs)
+        ],
+        kernel_class=GaussianKernel(),
+        kernel_parameters=np.logspace(-5, 1, 20),
+        kernel_parameter_name="sigma",
+        test_error_convergence_rate=test_error_convergence_rate,
+        df_performance_path=os.path.join(PART_1_OUTPUT_FOLDER, "q5_1-mini"),
+    )
[…]

### 2022-12-13 src/models/laplacian_interpolation.py

@@ -16,9 +16,9 @@ class LaplacianInterpolation:
         :return: y_hat: predicted labels for y_{l+1}, ... , y_{n}
         """
         s = y.shape[0]
-        degree_matrix = np.diag(w.sum(0))
+        diagonal = np.diag(w.sum(0))
         return np.sign(
-            np.linalg.lstsq(degree_matrix[s:, s:] - w[s:, s:], w[s:, :s] @ y, rcond=None)[0]
+            np.linalg.lstsq(diagonal[s:, s:] - w[s:, s:], w[s:, :s] @ y, rcond=None)[0]
         )
 
 

### 2022-12-13 src/solutions/part_2.py

@@ -29,7 +29,7 @@ def experimental_report(
     number_iterations,
 ):
     sample_range = [1, 2, 4, 8, 16]
-    loss = np.zeros((4, 5, number_iterations))
+    accuracy = np.zeros((4, 5, number_iterations))
 
     for iteration in range(number_iterations):
         for i, dataset in enumerate(datasets):
@@ -41,12 +41,12 @@ def experimental_report(
                     y[sample[: 2 * sample_size]],
                     y[sample[2 * sample_size :]],
                 )
-                loss[i, j, iteration] = np.mean(
-                    model.predict(w[sample, :][:, sample], y_train) != y_test
+                accuracy[i, j, iteration] = np.mean(
+                    model.predict(w[sample, :][:, sample], y_train) == y_test
                 )
                 if i == 0:
                     graph_edge_label_diagram(w, y, GRAPH_LABEL_DIAGRAM_PATH)
-    return loss.mean(-1), loss.std(-1)
+    return accuracy.mean(-1), accuracy.std(-1)
 
 
 def write_report_to_csv(means, stds, outpath):
@@ -57,7 +57,7 @@ def write_report_to_csv(means, stds, outpath):
     report.index = [50, 100, 200, 400]
     report = pd.concat(
         [pd.concat([report], keys=["# of known labels (per class)"], axis=1)],
-        keys=["# of datapoints per label"],
+        keys=["accuracy"],
     )
     dfi.export(report, outpath)
 

### 2022-12-13 submission.tex
q2 discussins pt1

--- 2022-12-12 submission.tex
@@
 
-Experimental report for the laplacian interpolation approach:
-\\
+\subsubsection{Experimental results}
+
     \begin{figure}[h]
@@
 
-Some observations to make here are:\\
+\subsubsection{Discussions}
 
-a) Both models seem to perform fairly well, even in the low-data setting.\\
+Some initial observations include that both models exhibit relatively high accuracy in all low-data settings. A potential justification for this may be seen by visualising 
+the adjacency matrix (Figure 12). Here blue edges are where both labels are -1, teal when both are different, and yellow when both are +1. Here we observe that the
+ graph is highly separable into 2 distinct clusters, and these clusters strongly align with label predictions. For the laplacian seminorm interpolation method, once discretised its solution in
+objective-minimisation form essentially describes a graph cut of minimal size, respecting the true labels.
 
-b) Increating the number of known labels increases the accuracy and decreases
- the variance of the predictors.\\
+Here we should note that using laplacian seminorm interpolation, if a node of our 3-NN graph is connected only to nodes of opposite label, then swapping this node's label would reduce
+our objective function. Hence, at the min-cost labelling, points inside clusters tend to be given the same label and only points bridging between clusters are likely to be misclassified.
 
-c) Increasing the total number of datapoints generally increases both model accuracies,
-and decreases variance. \\
+*** todo ***
+Our next observation is that increasing the number of labelled datapoints generally increases the accuracy in both models.
 
-d) The laplacian kernel method outperforms the vanilla inerpolation approach considerably,
-on both accuracy and variance. \\
+Increasing the total number of datapoints generally decreases the error variance in the seminorm interpolation
+model, but has a limited impact on the kernel interpolation model.
 
-The main reason for the success of this algorithm is the high degree of
- cluster separation observed in the dataset.
-\\
+The laplacian kernel method outperforms the vanilla inerpolation approach considerably, in accuracy, and less so
+for variance.
 
-For illustration, here is a diagram representing the graph adjacency matrix,
- with colours showing the labelling of an edge. Here blue edges are where both 
-labels are -1, teal when both are different, and yellow when both are +1.\\
+*** todo ***
 
-\includegraphics{outputs/part2/graph_label_diagram.png}#
+We have observed how the kernel interpolation approach has significantly outperformed the seminorm interpolation method, on both error and variance.
+ A reasonable explanation for this is that the seminorm interpolation approach utilises local information to pass labels through the graph.
+This means that only datapoints close to labelled data receive information from the labels themselves, and accuracy is likely reduced for datapoints far from the labels.
+In contrast, the kernel interpolation method takes global information from all the labelled datapoints and weights them according to their connectedness through the graph to a given vertex to determine a predicted label.
+This use of global information helps to resolve the case in which a vertex lies on the boundary of the two clusters as the model draws conclusions directly from its connectednessto labelled points rather than recieving information from similarly ambiguous boundary points.
 
-We see through this that the vast majority of datapoints are connected only to points
-of the same labelling, and that the graph is highly separated  into 2 clusters.
-Hence with minimal training information, both methods are able to predict with a
- high degree of accuracy.\\
+We may postulate that the seminorm interpolation method may outperform the kernel method on datasets where global information is more ambiguous than local information: for instance, consider a graph where there are more than 2 clusters, each with coherent binary labelling, but perhaps where 2 clusters of the same label are separated by a cluster of different labelling.
+In this scenario, the seminorm method would label the data in 3 clusters, by only considering local edgewise label changes, but the kernel method may have difficulty correctly identifying the label for some vertices as it may be less connected to points of the same label in ground truth, than to points of a different label in the neighbouring cluster.
 
-Note that error variance decreases as a function of the number of known labels, but 
-has a much more significant impact for the vanilla interpolation method.
+\begin{figure}[h]
+\centering
+\includegraphics[scale = 0.5]{outputs/part2/graph_label_diagram.png}
+\caption{Graph adjacency matrix for n = 50 datapoints per label}
+\label{Fig 14}
+\end{figure}
 
-We see that the kernel approach consistently outperforms the simple laplacian
- interpolation method. A reasonable explanation for this is that the laplacian
-interpolation approach utilises local information to 'diffuse' labels through the graph. 
-This means that only datapoints close to labelled data receive information from the 
-labels themselves, and accuracy is likely reduced for datapoints far from the labels.
-In contrast, the kernel interpolation method takes global information from all the 
-labelled datapoints and weights them according to their proximity and connectedness 
-to eachother to predict labels.
 \newpage

### 2022-12-13 main.py

@@ -20,7 +20,7 @@ from src.models.single_class.linear_regression_classifier import (
 from src.models.single_class.one_nn import OneNN
 from src.models.single_class.perceptron import Perceptron
 from src.models.single_class.winnow import Winnow
-from src.solutions import part_1, part_3
+from src.solutions import part_1, part_2, part_3
 
 np.random.seed(DEFAULT_SEED)
 
@@ -39,229 +39,229 @@ if __name__ == "__main__":
     if not os.path.exists(OUTPUTS_FOLDER):
         os.makedirs(OUTPUTS_FOLDER)
 
-    # Question 1
-    PART_1_OUTPUT_FOLDER = os.path.join(OUTPUTS_FOLDER, "part1")
-    if not os.path.exists(PART_1_OUTPUT_FOLDER):
-        os.makedirs(PART_1_OUTPUT_FOLDER)
+    # # Question 1
+    # PART_1_OUTPUT_FOLDER = os.path.join(OUTPUTS_FOLDER, "part1")
+    # if not os.path.exists(PART_1_OUTPUT_FOLDER):
+    #     os.makedirs(PART_1_OUTPUT_FOLDER)
 
-    raw_data = np.genfromtxt(PART_1_DATA_SET_PATH)
-    x, y, labels = part_1_preprocess(raw_data)
+    # raw_data = np.genfromtxt(PART_1_DATA_SET_PATH)
+    # x, y, labels = part_1_preprocess(raw_data)
 
-    raw_data_mini_train = np.genfromtxt(PART_1_MINI_TRAIN_SET_PATH)
-    x_mini_train, y_mini_train, _ = part_1_preprocess(raw_data_mini_train)
-    raw_data_mini_test = np.genfromtxt(PART_1_MINI_TEST_SET_PATH)
-    x_mini_test, y_mini_test, _ = part_1_preprocess(raw_data_mini_test)
-    x_mini = np.concatenate((x_mini_train, x_mini_test), axis=0)
-    y_mini = np.concatenate((y_mini_train, y_mini_test), axis=0)
+    # raw_data_mini_train = np.genfromtxt(PART_1_MINI_TRAIN_SET_PATH)
+    # x_mini_train, y_mini_train, _ = part_1_preprocess(raw_data_mini_train)
+    # raw_data_mini_test = np.genfromtxt(PART_1_MINI_TEST_SET_PATH)
[…]

### 2022-12-13 src/solutions/part_2.py

@@ -29,7 +29,7 @@ def experimental_report(
     number_iterations,
 ):
     sample_range = [1, 2, 4, 8, 16]
-    accuracy = np.zeros((4, 5, number_iterations))
+    error = np.zeros((4, 5, number_iterations))
 
     for iteration in range(number_iterations):
         for i, dataset in enumerate(datasets):
@@ -41,12 +41,12 @@ def experimental_report(
                     y[sample[: 2 * sample_size]],
                     y[sample[2 * sample_size :]],
                 )
-                accuracy[i, j, iteration] = np.mean(
-                    model.predict(w[sample, :][:, sample], y_train) == y_test
+                error[i, j, iteration] = np.mean(
+                    model.predict(w[sample, :][:, sample], y_train) != y_test
                 )
                 if i == 0:
                     graph_edge_label_diagram(w, y, GRAPH_LABEL_DIAGRAM_PATH)
-    return accuracy.mean(-1), accuracy.std(-1)
+    return error.mean(-1), error.std(-1)
 
 
 def write_report_to_csv(means, stds, outpath):
@@ -56,8 +56,8 @@ def write_report_to_csv(means, stds, outpath):
     report.columns = [1, 2, 4, 8, 16]
     report.index = [50, 100, 200, 400]
     report = pd.concat(
-        [pd.concat([report], keys=["# of known labels (per class)"], axis=1)],
-        keys=["accuracy"],
+        [pd.concat([report], keys=["# of known labels per class"], axis=1)],
+        keys=["# of datapoints per class"],
     )
     dfi.export(report, outpath)
 

### 2022-12-13 submission.tex
q2 writeup complete

@@
 
-\\
-
 And for the laplacian kernel method:
@@
 \subsubsection{Discussions}
+\begin{itemize}
+    \item[2.]
+        Some initial observations include that both models exhibit relatively high accuracy in all low-data settings.
+Additionally, both error and variance are observed to decrease as a function of both number of samples and number of total datapoints.
+        Further, we observe that the kernel interpolation approach gives lower error and variance across all experiments, and also is less severely effected by sample number.
+    \item[3.]
+        To analyse this difference in model performance, we first perform a visualisation of our induced 3-NN graph seen in \textbf{Fig 14}: note that blue edges are where both labels are -1, teal when both are different, and yellow when both are +1.
+        From our diagram we can observe that the graph is highly separable into 2 distinct clusters, and these clusters strongly align with label predictions.
 
-Some initial observations include that both models exhibit relatively high accuracy in all low-data settings. A potential justification for this may be seen by visualising 
-the adjacency matrix (Figure 12). Here blue edges are where both labels are -1, teal when both are different, and yellow when both are +1. Here we observe that the
- graph is highly separable into 2 distinct clusters, and these clusters strongly align with label predictions. For the laplacian seminorm interpolation method, once discretised its solution in
-objective-minimisation form essentially describes a graph cut of minimal size, respecting the true labels.
-
-Here we should note that using laplacian seminorm interpolation, if a node of our 3-NN graph is connected only to nodes of opposite label, then swapping this node's label would reduce
-our objective function. Hence, at the min-cost labelling, points inside clusters tend to be given the same label and only points bridging between clusters are likely to be misclassified.
-
-*** todo ***
-Our next observation is that increasing the number of labelled datapoints generally increases the accuracy in both models.
-
-Increasing the total number of datapoints generally decreases the error variance in the seminorm interpolation
-model, but has a limited impact on the kernel interpolation model.
-
-The laplacian kernel method outperforms the vanilla inerpolation approach considerably, in accuracy, and less so
-for variance.
-
-*** todo ***
-
-We have observed how the kernel interpolation approach has significantly outperformed the seminorm interpolation method, on both error and variance.
- A reasonable explanation for this is that the seminorm interpolation approach utilises local information to pass labels through the graph.
-This means that only datapoints close to labelled data receive information from the labels themselves, and accuracy is likely reduced for datapoints far from the labels.
+        A reasonable explanation for the kernel approach's superior performance follows from the observation that seminorm interpolation propagates local information to pass labels through the graph, whereas the kernel method utilises global graph connectivity
+        properties of each point to a set of labels to make predictions.
+        This means that in the seminorm method, only datapoints close to labelled data receive information from the labels themselves, and accuracy is likely reduced for datapoints far from the labels as label information is passed indirectly through the graph.
+        Further if a point is close the the boundary of a cluster, it may be be misclassified due to its proximity to a single label from the other cluster. 
         In contrast, the kernel interpolation method takes global information from all the labelled datapoints and weights them according to their connectedness through the graph to a given vertex to determine a predicted label.
-This use of global information helps to resolve the case in which a vertex lies on the boundary of the two clusters as the model draws conclusions directly from its connectednessto labelled points rather than recieving information from similarly ambiguous boundary points.
-
+        A vertex will only be given a label if it is more strongly connected to all labelled points that have this label.
+This use of global information helps to resolve the case in which a vertex lies on the boundary of the two clusters as the model draws
+        conclusions directly from its connectedness to labelled points rather than recieving information from similarly ambiguous boundary points.
+However, we should note that this superior performance is an artifact of the dataset,
+        and that it separates well into one cluster per datapoint: this implies that if a vertex is more strongly connected to points with label +1, then it is most likely given this label in reality.
+    \item[4.]
         We may postulate that the seminorm interpolation method may outperform the kernel method on datasets where global information is more ambiguous than local information: for instance, consider a graph where there are more than 2 clusters, each with coherent binary labelling, but perhaps where 2 clusters of the same label are separated by a cluster of different labelling.
 In this scenario, the seminorm method would label the data in 3 clusters, by only considering local edgewise label changes, but the kernel method may have difficulty correctly identifying the label for some vertices as it may be less connected to points of the same label in ground truth, than to points of a different label in the neighbouring cluster.
+\end{itemize}
 
@@
             \State $\mathcal{D}_{test} \gets  \{(x^1_{test}, y^1_{test}), ..., (x^{M'}_{test}, y^{M'}_{test})\}$ \Comment Fixed test set of size $M'$
-            \State $error \gets  1 \Comment initial test set error
+            \State  error \gets  1 \Comment initial test set error
             \While{$error > 0.1$}
@@
 
-    From these plots we can see that the perceptron sample complexity grows linearly ($m = \Theta(n)$), the Winnow sample complexity grows logarithmically ($m = \Theta(\log(n))$), the least squares sample complexity grows linearly ($m = \Theta(n)$), and the 1-nearest neighbours sample complexity grows exponentially ($m = \Theta(e^{n})$).
-These estimates can be qualitatively observed by attempting to fit different function curves to the experimental results and choosing the function with the best qualitative fit.
-This shows that winnow is a much more robust algorithm in high dimensions due to its logarithmic scaling of the number of training points with respect to the dimensionality to achieve the same error rate.
-On the other hand, one-nearest neighbours scales exponentially, suggesting that it is impractical to use in high dimensional data.
-This can be attributed to the curse of dimensionality.
+    From these plots we can see that may observe:
+
+    Perceptron sample complexity grows linearly ($m = \Theta(n)$), and the Winnow sample complexity grows logarithmically ($m = \Theta(\log(n))$).
+The corresponding asymptotic lower bound results will be proven analytically in the next section.
+
+    The least squares sample complexity grows linearly ($m = \Theta(n)$).
+We may aslo prove this analytically: note that a linear regression classifier is exactly the same as the 'half space' model shown on page 48 of the learning theory notes,
+     with dimension n. Hence we determine that the VC dimension of the least squares classifier is n. Hence, the fundamental theorem of statistical learning determines that for fixed
+     $\epsilon$, $\delta$, the sample complexity of our least squares classifier is bounded above and below by expressions linear in n.
+
+    Finally, the 1-nearest neighbours sample complexity grows exponentially ($m = \Theta(e^{n})$).
+
+    These estimates can be qualitatively observed by attempting to fit different function curves to the experimental
+    results and choosing the function with the best qualitative fit. This shows that winnow is a much more robust 
+    algorithm in high dimensions due to its logarithmic scaling of the number of training points with respect to
+        the dimensionality to achieve the same error rate. On the other hand, one-nearest neighbours scales exponentially,
+        suggesting that it is impractical to use in high dimensional data. This can be attributed to the curse of dimensionality.
         Both the perceptron and least squares scale linearly, thus performing worse than winnow but better than the one-NN algorithm.
 
-\newpage
-
-    \item[d.]\\
+    \item[d.]
     We note that since for any $X_{t}$ , $y_{t} = X_{1,t}$ , we have the following
-     expression representing the linear separability of our dataset:\\
-    \[(v \cdot x_{t})y_{t} \ge 1\]\\
-    Where $v = (1,0, \dots, 0)^{T}$. Note that $\|v\| =1$.\\
-    Hence, in our online mistake bound for the perceptron, we have that $\gamma =1$.
+     expression representing the linear separability of our dataset:
+    $(v \cdot x_{t})y_{t} \ge 1$
+    Where $v = (1,0, \dots, 0)^{T}$. Note that $\|v\| =1$.
+    Hence, in our online mistake bound for the perceptron, we have that our margin parameter $\gamma =1$.
     Further note that $\forall t$, $x_{t} \in {-1,1}^{n} \implies \|x_{t}\|^{2}
     = n$. This gives us that $R = max_{t} \|x_{t}\| = \sqrt{n}$.
-    Hence our mistake bound for the perceptron algorithm is given by:\\
+    Hence our mistake bound for the perceptron algorithm is given by:
 
-    \[M \le n \].\\
+    $M \le n $.
 
-    Using the theorem on page 60 of the online learning notes, we arrive at:\\
+    The theorem on page 60 of the online learning notes relates mistake bounds to batch generalisation error bounds:
 
-    \[Prob(\mathcal{A_{S}}(x ^{\prime}) \ne y^{\prime} ) \le \frac{n}{m}\]\\
+    $Prob(\mathcal{A_{S}}(x ^{\prime}) \ne y^{\prime} ) \le \frac{n}{m}$
+
+    \textbf{Corrolary}:}
+    This result gives us a lower bound on sample complexity for the perceptron algorithm:
+
+    Suppose we require out generalisation error $ Prob(\mathcal{A_{S}}(x ^{\prime}) \ne y^{\prime} ) \le \frac{n}{m}$ to be  less than some fixed $\epsilon$.
+
+    $\implies \frac{n}{m} \le \epsilon \implies m \ge \frac{n}{\epsilon}$
+
+    Note that given the mistake bound on winnow given by $ M \ge 3 (log(n) + 1) +2$ (note k=1 since the ground truth is a 1-literal conjunction given by $x_{1}$), following the same approach we arrive at a lower bound on sample complexity for winnow that
+    matches our experimental observations:
+
+    $m(n) \ge \frac{3 (log(n) + 1) +2}{\epsilon} = \Omega (log(n))$
 
@@
 
-    $m(n) = \Omega (n)$ \\
+    $m(n) = \Omega (2^{n})$ \\
     \textbf{Proof:}\\

### 2022-12-13 main.py

@@ -25,12 +25,12 @@ from src.solutions import part_1, part_2, part_3
 np.random.seed(DEFAULT_SEED)
 
 
-def part_1_preprocess(data):
-    x_data, labels = data[:, 1:], data[:, 0]
+#def part_1_preprocess(data):
+   # x_data, labels = data[:, 1:], data[:, 0]
     # shift so that our labels start at zero
-    shifted_labels = labels - np.min(labels)
-    y_data = one_hot_encode(shifted_labels)
-    return x_data, y_data, labels
+   # shifted_labels = labels - np.min(labels)
+  #  y_data = one_hot_encode(shifted_labels)
+ #   return x_data, y_data, labels
 
 
 if __name__ == "__main__":

### 2022-12-13 src/models/helpers.py

@@ -69,6 +69,12 @@ def one_hot_encode(shifted_labels: np.ndarray) -> np.ndarray:
 
 
 def ssl_data_sample(y, sample_size):
+    """
+    :param y: array of labels for our dataset
+    :param sample_size: number of samples required
+
+    :return: permutation of our original indices such that the first 
+    """
     idxs = np.random.choice(
         list(np.where(y == -1.0)[0]), size=sample_size, replace=False
     ).tolist()
@@ -80,6 +86,9 @@ def ssl_data_sample(y, sample_size):
 
 
 def knn_adjacency_matrix(x, k):
+    """
+    Given a design matrix x, generate an adjacency matrix of the K-NN graph of x
+    """
     tree = KDTree(x)
     n = x.shape[0]
     graph = tree.query(x, k)[1][:, 1:]

### 2022-12-13 src/solutions/part_2.py

@@ -76,7 +76,6 @@ def graph_edge_label_diagram(w, y, outpath):
     for i, y1 in enumerate(y):
         for j, y2 in enumerate(y):
             edge_colours[i, j] = edge_colour(y1, y2)
-
     plt.imshow(w * edge_colours)
     plt.savefig(outpath)
 

### 2022-12-13 submission.tex
final exit alexei

@@
     Hence, in our online mistake bound for the perceptron, we have that our margin parameter $\gamma =1$.
-    Further note that $\forall t$, $x_{t} \in {-1,1}^{n} \implies \|x_{t}\|^{2}
+    Further note that $\forall t$, $x_{t} \in \{-1,1\}^{n} \implies \|x_{t}\|^{2}
     = n$. This gives us that $R = max_{t} \|x_{t}\| = \sqrt{n}$.
@@
 
-    \textbf{Corrolary}:}
+    \textbf{Corrolary}
+
     This result gives us a lower bound on sample complexity for the perceptron algorithm:
@@
 
-    Note that given the mistake bound on winnow given by $ M \ge 3 (log(n) + 1) +2$ (note k=1 since the ground truth is a 1-literal conjunction given by $x_{1}$), following the same approach we arrive at a lower bound on sample complexity for winnow that
+    Note that given the mistake bound on winnow given by $ M \le 3 (log(n) + 1) +2$ (note k=1 since the ground truth is a 1-literal conjunction given by $x_{1}$), following the same approach we arrive at a lower bound on sample complexity for winnow that
     matches our experimental observations:
@@
 
-     \item[e.]\\
-     From our experimental observations we may expect the sample complexity of 1-NN
-     to be lower bounded by some exponential function. We formalise this in the
-     following proposition:\\
+     \item[e.]
+     From our experimental observations we may expect the sample complexity of 1-NN to be lower bounded by some exponential function. We formalise this in the following proposition:
 
-    \textbf{Proposition:}\\
+     \textbf{Proposition:}
 
-    Following the data-generating distribution described above, we have that our sample complexity given by:\\
+     Following the data-generating distribution described above, we have that our sample complexity given by:
 
-    $m(n) = \Omega (2^{n})$ \\
-    \textbf{Proof:}\\
+     $m(n) = \Omega (2^{n})$
+
+    \textbf{Proof}
 
@@
      arbitrary test point $(x,x_{1})$, sampled uniformly from the same set.
-    \\
-    We note the following observation:\\
 
-    \textbf{Obs:}\\
-    if $x \in S$, then $\mathcal{A}_{S}(x)) = y$, where y is the true label for x. \\
+    We note the following observation:
+
+    \textbf{Observation}
+
+    if $x \in S$, then $\mathcal{A}_{S}(x)) = y$, where y is the true label for x.
 
@@
     $x = x \prime \implies y = y \prime $. Trivially, x is the 1-nearest neighbour to itself,
-    so the algorithm makes a correct prediction for any datapoint present in our training set.\\
+    so the algorithm makes a correct prediction for any datapoint present in our training set.
 
@@
     Hence, the set of all training sets that make an error on x is contained in the set of all
-    training sets not containing x. \\
+    training sets not containing x.
 
-    Hence, for a given x, $P_{S}(\mathcal{A}_{S}(x) \ne y) \le P_{S}(x \notin S)$.\\
+    Hence, for a given x, $P_{S}(\mathcal{A}_{S}(x) \ne y) \le P_{S}(x \notin S)$.
 
-    Since S is a collection of points sampled iid from our data generating distribution, \\
-    $P_{S}(x \notin S) = \prod_{i=1}^{m}P(x_{i} \ne x) = \prod_{i}(1 - P(x_{i} = x)) = (1 - 2^{-n})^{m}$\\
+    Since S is a collection of points sampled iid from our data generating distribution, 
+    $P_{S}(x \notin S) = \prod_{i=1}^{m}P(x_{i} \ne x) = \prod_{i}(1 - P(x_{i} = x)) = (1 - 2^{-n})^{m}$
 
     We note that our choice of x was arbitrary, and since we sampled x uniformly, we arrive at the 
-    following generalisation error bound:\\
+    following generalisation error bound:
 
-    $\mathbb{E}_{S \sim \mathcal{D}^{m}, x \sim \mathcal{D}}[\mathcal{L}_{S}(x)] \le (1 - 2^{-n})^{m} $\\
+    $\mathbb{E}_{S \sim \mathcal{D}^{m}, x \sim \mathcal{D}}[\mathcal{L}_{S}(x)] \le (1 - 2^{-n})^{m} $
     Using the identity $1-x \le e^{-x}$ provided frequently in the notes, we simplify this bound to give:
-    \\
-    \\
 
     $\mathbb{E}_{S \sim \mathcal{D}^{m}, x \sim \mathcal{D}}[\mathcal{L}_{S}(x)] \le exp(-2^{n}m)$
-    \\
+
     Suppose we seek m such that our generalisation error is less than some fixed $\epsilon$. \\
-    \\
+
     Hence we require $\mathbb{E}_{S \sim \mathcal{D}^{m}, x \sim \mathcal{D}}[\mathcal{L}_{S}(x)] \le exp(-2^{n}m) \le \epsilon$\\
-    \\
-    $\implies -m2^{-n} \le log(\epsilon)$\\
 
-    Hence, $m \ge -log(\epsilon)2^{n} = log(\frac{1}{\epsilon}) 2^{n}$\\
+    $\implies -m2^{-n} \le log(\epsilon)$
 
-    $\implies m = \Omega(2^{n})$\\
+    Hence, $m \ge -log(\epsilon)2^{n} = log(\frac{1}{\epsilon}) 2^{n}$
+
+    $\implies m = \Omega(2^{n})$
     $\square$

### 2022-12-13 submission.tex
fix grammar

@@
     \For{$i\in\{1, 2, ..., M\}$}: \Comment Number of Epochs
-        \For{$j\in\{2, ..., N\}}$ \Comment Number of training points (skipping the first point)
+        \If{i==1$} \Comment Skip first data point if it's the first epoch
+            \State $j_{init} \gets 2$
+        \Else
+            \State $j_{init} \gets 1$
+        \EndIf
+        \For{$j\in\{j_{init}, ..., N\}}$ \Comment Number of training points
             \For{$k\in\{1, 2, ..., K\}}$ \Comment Number of classes
@@
 
+        Note that $y_k^{i, j}$ is the one-hot encoding of the $j^{th}$ data point in the $i^{th}$ epoch for the $k^{th}$ class.
+
     The number of epochs was determined by training on the mini training data set until the performance of the mini testing data set no longer changed.
-    This was considered a reasonable number of epochs to use to train the actual data set.
+    This was considered a reasonable number of epochs to use to train with the actual data set.
 
@@
     \item[5.] To select a good range of values for the kernel width sigma for the Gaussian kernel, the mini training and testing sets was used to quickly gauge the test error for different hyper-parameters.
-    The hyper-parameter values above and below the best performing hyper-parameter (with respect to test set error) was chosen as the hyper-parameter range to define $S$, the set of values for cross-validation for repeating parts 1 and 2 with the Gaussian Kernel.
+    The hyper-parameter values above and below the best performing hyper-parameter (with respect to test set error) was chosen as the hyper-parameter range to define $S$, the set of values for cross-validation when repeating parts 1 and 2 with the Gaussian Kernel.
     \begin{figure}[h]
@@
     \For{$i\in\{1, 2, ..., M\}$}: \Comment Number of Epochs
-        \For{$j\in\{2, ..., N\}}$ \Comment Number of training points
+        \If{i==1$} \Comment Skip first data point if it's the first epoch
+            \State $j_{init} \gets 2$
+        \Else
+            \State $j_{init} \gets 1$
+        \EndIf
+        \For{$j\in\{j_{init}, ..., N\}}$ \Comment Number of training points
             \For{$k\in\{1, 2, ..., K\}}$ \Comment Number of classes
@@
 This follows general rule of thumb for train/test splits.
-Given a finite data set size, increasing the training percentage can provide inaccurate out of sample performance with the test set.
-Conversly, a smaller training percentage can poorly represent the model's performance due to limited training examples.
+Given a finite data set size, increasing the training percentage can provide inaccurate out of sample performance with  the small test set.
+Conversely, a smaller training percentage can poorly represent the model's performance due to limited training examples.
 Thus a balance must be drawn between the two.
@@
 Additionally, both error and variance are observed to decrease as a function of both number of samples and number of total datapoints.
-        Further, we observe that the kernel interpolation approach gives lower error and variance across all experiments, and also is less severely effected by sample number.
+        Further, we observe that the kernel interpolation approach gives lower error and variance across all experiments, and also is less severely affected by sample number.
     \item[3.]
@@
 It is possible that our chosen finite horizon is inadequate for capturing the dynamics as $n \rightarrow \infty$.
-For example, a sample complexity that is actually exponential could seem linear if we do not choose an $N$ that is large enough to reveal this trend.
+For example, a sample complexity that is actually quadratic could seem linear if we do not choose an $N$ that is large enough to reveal this trend.
 
@@
 
-    From these plots we can see that may observe:
+    From these plots we may observe:
 
@@
     The least squares sample complexity grows linearly ($m = \Theta(n)$).
-We may aslo prove this analytically: note that a linear regression classifier is exactly the same as the 'half space' model shown on page 48 of the learning theory notes,
+We may also prove this analytically: note that a linear regression classifier is exactly the same as the 'half space' model shown on page 48 of the learning theory notes,
      with dimension n. Hence we determine that the VC dimension of the least squares classifier is n. Hence, the fundamental theorem of statistical learning determines that for fixed
@@
 
-    \textbf{Corrolary}
+    \textbf{Corollary}
 

### 2022-12-13 submission.tex
formatting

@@
     \centering
-    \includegraphics[scale=0.35]{outputs/part3/q1a_perceptron_complexity_function_comparison.png}
+    \includegraphics[scale=0.3]{outputs/part3/q1a_perceptron_complexity_function_comparison.png}
     \caption{Perceptron Sample Complexity vs Function Classes}
@@
     \centering
-    \includegraphics[scale=0.35]{outputs/part3/q1a_winnow_complexity_function_comparison.png}
+    \includegraphics[scale=0.3]{outputs/part3/q1a_winnow_complexity_function_comparison.png}
     \caption{Winnow Sample Complexity vs Function Classes}
@@
     \end{figure}
-\newpage
     \begin{figure}[h]
     \centering
-    \includegraphics[scale=0.35]{outputs/part3/q1a_lin_reg_complexity_function_comparison.png}
+    \includegraphics[scale=0.3]{outputs/part3/q1a_lin_reg_complexity_function_comparison.png}
     \caption{Least Squares Sample Complexity vs Function Classes}
@@
     \end{figure}
+\newpage
 
@@
     \centering
-    \includegraphics[scale=0.35]{outputs/part3/q1a_one_nn_complexity_function_comparison.png}
+    \includegraphics[scale=0.3]{outputs/part3/q1a_one_nn_complexity_function_comparison.png}
     \caption{1-Nearest Neighbours Sample Complexity vs Function Classes}
@@
 
+\newpage
     \item[d.]

### 2022-12-14 main.py
remove least squares

@@ -5,18 +5,14 @@ import numpy as np
 import pandas as pd
 from scipy.optimize import curve_fit
 
-from src.constants import (
-    DEFAULT_SEED,
-    OUTPUTS_FOLDER,
-    PART_1_DATA_SET_PATH,
-    PART_1_MINI_TEST_SET_PATH,
-    PART_1_MINI_TRAIN_SET_PATH,
-)
-from src.models.helpers import TrainTestData, one_hot_encode, split_train_test_data
+from src.constants import (DEFAULT_SEED, OUTPUTS_FOLDER, PART_1_DATA_SET_PATH,
+                           PART_1_MINI_TEST_SET_PATH,
+                           PART_1_MINI_TRAIN_SET_PATH)
+from src.models.helpers import (TrainTestData, one_hot_encode,
+                                split_train_test_data)
 from src.models.kernels import GaussianKernel, PolynomialKernel
-from src.models.single_class.linear_regression_classifier import (
-    LinearRegressionClassifier,
-)
+from src.models.single_class.linear_regression_classifier import \
+    LinearRegressionClassifier
 from src.models.single_class.one_nn import OneNN
 from src.models.single_class.perceptron import Perceptron
 from src.models.single_class.winnow import Winnow
@@ -25,12 +21,12 @@ from src.solutions import part_1, part_2, part_3
 np.random.seed(DEFAULT_SEED)
 
 
-#def part_1_preprocess(data):
-   # x_data, labels = data[:, 1:], data[:, 0]
+def part_1_preprocess(data):
+    x_data, labels = data[:, 1:], data[:, 0]
     # shift so that our labels start at zero
-   # shifted_labels = labels - np.min(labels)
-  #  y_data = one_hot_encode(shifted_labels)
- #   return x_data, y_data, labels
+    shifted_labels = labels - np.min(labels)
+    y_data = one_hot_encode(shifted_labels)
+    return x_data, y_data, labels
 
 
 if __name__ == "__main__":
@@ -39,155 +35,155 @@ if __name__ == "__main__":
     if not os.path.exists(OUTPUTS_FOLDER):
         os.makedirs(OUTPUTS_FOLDER)
 
-    # # Question 1
-    # PART_1_OUTPUT_FOLDER = os.path.join(OUTPUTS_FOLDER, "part1")
-    # if not os.path.exists(PART_1_OUTPUT_FOLDER):
-    #     os.makedirs(PART_1_OUTPUT_FOLDER)
[…]

### 2022-12-14 src/models/helpers.py

@@ -73,7 +73,7 @@ def ssl_data_sample(y, sample_size):
     :param y: array of labels for our dataset
     :param sample_size: number of samples required
 
-    :return: permutation of our original indices such that the first 
+    :return: permutation of our original indices such that the first
     """
     idxs = np.random.choice(
         list(np.where(y == -1.0)[0]), size=sample_size, replace=False

### 2022-12-14 src/models/laplacian_interpolation.py

@@ -17,9 +17,7 @@ class LaplacianInterpolation:
         """
         s = y.shape[0]
         diagonal = np.diag(w.sum(0))
-        return np.sign(
-            np.linalg.lstsq(diagonal[s:, s:] - w[s:, s:], w[s:, :s] @ y, rcond=None)[0]
-        )
+        return np.sign(np.linalg.pinv(diagonal[s:, s:] - w[s:, s:]) @ (w[s:, :s] @ y))
 
 
 class LaplacianKernelInterpolation:

### 2022-12-14 src/solutions/part_2.py

@@ -6,10 +6,8 @@ import numpy as np
 import pandas as pd
 
 from src.models.helpers import knn_adjacency_matrix, ssl_data_sample
-from src.models.laplacian_interpolation import (
-    LaplacianInterpolation,
-    LaplacianKernelInterpolation,
-)
+from src.models.laplacian_interpolation import (LaplacianInterpolation,
+                                                LaplacianKernelInterpolation)
 
 outpath = os.path.join("outputs", "part2")
 DATAPATH50 = os.path.join("data", "dtrain13_50.dat")

### 2022-12-14 submission.tex
spelling

@@
         This means that in the seminorm method, only datapoints close to labelled data receive information from the labels themselves, and accuracy is likely reduced for datapoints far from the labels as label information is passed indirectly through the graph.
-        Further if a point is close the the boundary of a cluster, it may be be misclassified due to its proximity to a single label from the other cluster. 
+        Further if a point is close the boundary of a cluster, it may be be misclassified due to its proximity to a single label from the other cluster.
         In contrast, the kernel interpolation method takes global information from all the labelled datapoints and weights them according to their connectedness through the graph to a given vertex to determine a predicted label.
@@
 This use of global information helps to resolve the case in which a vertex lies on the boundary of the two clusters as the model draws
-        conclusions directly from its connectedness to labelled points rather than recieving information from similarly ambiguous boundary points.
+        conclusions directly from its connectedness to labelled points rather than receiving information from similarly ambiguous boundary points.
 However, we should note that this superior performance is an artifact of the dataset,

### 2022-12-14 src/models/laplacian_interpolation.py
put least squares back in

@@ -17,7 +17,9 @@ class LaplacianInterpolation:
         """
         s = y.shape[0]
         diagonal = np.diag(w.sum(0))
-        return np.sign(np.linalg.pinv(diagonal[s:, s:] - w[s:, s:]) @ (w[s:, :s] @ y))
+        return np.sign(
+            np.linalg.lstsq(diagonal[s:, s:] - w[s:, s:], w[s:, :s] @ y, rcond=None)[0]
+        )
 
 
 class LaplacianKernelInterpolation:

### 2022-12-14 src/solutions/part_2.py

@@ -6,8 +6,10 @@ import numpy as np
 import pandas as pd
 
 from src.models.helpers import knn_adjacency_matrix, ssl_data_sample
-from src.models.laplacian_interpolation import (LaplacianInterpolation,
-                                                LaplacianKernelInterpolation)
+from src.models.laplacian_interpolation import (
+    LaplacianInterpolation,
+    LaplacianKernelInterpolation,
+)
 
 outpath = os.path.join("outputs", "part2")
 DATAPATH50 = os.path.join("data", "dtrain13_50.dat")
